### 2024-08-17 hello_world/rugsafe/paper/paper.tex
checkpoint with paper

\documentclass{article}
\usepackage{amsmath}

\title{Rugsafe: A Protocol for Protecting Digital Assets from Rug Pulls}
\author{info@Rugsafe.org}
\date{v0.0.1 August 1, 2024}

\begin{document}

\maketitle

\begin{abstract}
Rugsafe introduces a novel protocol designed to mitigate the risks associated with rug pulls in decentralized finance (DeFi). By leveraging cryptographic primitives and economic incentives, Rugsafe provides a framework that ensures the security and recoverability of assets when fraudulent activities are detected. The protocol is built around the concept of vaults for rugged tokens, issuance of anticoin tokens, and an incentive mechanism that penalizes and rewards users based on their interaction with the system. Rugsafe integrates seamlessly with existing DeFi platforms, offering an additional layer of security without compromising the decentralization principles.
\end{abstract}

%\clearpage

%\tableofcontents

%\twocolumn
\section{Overview}

The Rugsafe protocol enables users who hold rugged tokens, denoted as $C_r$, to deposit these tokens into a specialized vault $V_c$ and receive an equal amount of anticoin tokens, $C_a$, which are pegged to the inverse price movement of $C_r$.

\subsection{Vault Creation and Anticoin Issuance}
When a vault $V_c$ is created for a rugged token $C_r$, users can deposit $C_r$ into this vault. Upon deposit, the protocol mints an equal amount of $C_a$, which is credited to the user's balance.

\begin{equation}
C_a = C_r
\end{equation}

The vaults are held in a central vault registry, ensuring that all interactions with rugged tokens are tracked and managed within the system.

\subsection{Withdrawal Penalty Mechanism}
If a user decides to withdraw their original rugged tokens $C_r$ by depositing back their $C_a$, a penalty is incurred. A portion of the $C_a$ tokens are deducted from the user's balance, and these penalized tokens are distributed among the remaining $C_a$ holders.

\begin{equation}
C_{r,\text{withdrawn}} = C_{r,\text{deposited}} - P(C_a)
\end{equation}

Where $P(C_a)$ represents the penalty, which scales according to the amount of $C_r$ originally deposited. The penalty mechanism incentivizes holding $C_a$ longer, as the remaining holders benefit from these penalties.

\subsection{Anticoin Pricing and Pegging Mechanism}
At the time of vault creation, the protocol records the current price of the underlying rugged token $C_r$. This price is used as a reference for all future transactions involving $C_a$.

\begin{equation}
\text{Price}_{C_a} \propto \frac{1}{\text{Price}_{C_r}}
\end{equation}

As the price of $C_r$ fluctuates, the value of $C_a$ adjusts inversely, similar to an algorithmic stablecoin mechanism. This ensures that $C_a$ holders are protected against the devaluation of $C_r$.

\subsection{User Commitment and Signal to the Ecosystem}
Depositing $C_r$ into a vault $V_c$ and receiving $C_a$ signals the user's belief that $C_r$ is a rugged token. To further reinforce this belief, users can burn their $C_a$ tokens, effectively removing them from circulation and indicating their strong commitment to the protocol's mission.

\begin{equation}
\text{Signal} = \text{Burn}(C_a)
\end{equation}

This burning mechanism enhances the credibility of the user's claim that $C_r$ is a rugged token and provides additional confidence to other participants in the ecosystem.

\subsection{Opportunities for New Developments}
The Rugsafe protocol's structure opens up opportunities for developers to build applications that cater to the needs of rug pull victims. By establishing a market for anticoin tokens $C_a$, new financial products and services can be developed to support users who have suffered losses from rug pulls.

\subsection{Whale Penalty Mechanism}
To prevent large holders (whales) from gaming the system, the penalty for withdrawing $C_r$ scales with the amount of $C_a$ held. Inspired by quadratic voting schemes, the penalty increases progressively as the whale's holdings increase, ensuring fairness and preventing manipulation.

\begin{equation}
P(C_a) \propto \left(\text{Holdings}\right)^\lambda
\end{equation}

Where $\lambda > 1$ is a scaling factor that ensures the penalty increases non-linearly with the amount of $C_a$ held. This scaling penalty ensures that the system remains equitable and prevents disproportionate influence by large holders.

\section{Conclusion}
Rugsafe presents a robust mathematical framework designed to protect against rug pulls in the DeFi space. By combining vault mechanisms, anticoin issuance, and incentive structures, it ensures a secure environment for digital asset management. The protocol's design not only protects users but also opens up new avenues for development and innovation in the DeFi ecosystem.

\end{document}

### 2024-08-17 hello_world/src/instruction.rs

@@ -1,6 +1,6 @@
 use borsh::{BorshDeserialize, BorshSerialize};
+use solana_program::msg;
 use solana_program::program_error::ProgramError;
-
 #[repr(C)]
 #[derive(Clone, Debug, PartialEq, BorshSerialize, BorshDeserialize)]
 pub enum VaultInstruction {
@@ -13,13 +13,19 @@ pub enum VaultInstruction {
 
 impl VaultInstruction {
     pub fn unpack(input: &[u8]) -> Result<Self, ProgramError> {
+        msg!("input: {:?}", hex::encode(input));
+
         let (&tag, rest) = input
             .split_first()
             .ok_or(ProgramError::InvalidInstructionData)?;
+        msg!("tag: {}", tag);
+        msg!("Rest: {:?}", hex::encode(rest));
+
         Ok(match tag {
             0 => Self::CreateVault,
             1 => {
                 let amount = Self::unpack_amount(rest)?;
+                msg!("amount from inside unpack 1: {}", &amount.to_string());
                 Self::Deposit { amount }
             }
             2 => {
@@ -32,6 +38,7 @@ impl VaultInstruction {
             }
             4 => {
                 let amount = Self::unpack_amount(rest)?;
+                msg!("amount from inside unpack 2: {}", &amount.to_string());
                 Self::Faucet { amount }
             }
             _ => return Err(ProgramError::InvalidInstructionData),
@@ -44,6 +51,7 @@ impl VaultInstruction {
             .and_then(|slice| slice.try_into().ok())
             .map(u64::from_le_bytes)
             .ok_or(ProgramError::InvalidInstructionData)?;
+        msg!("amount from inside unpack_amount: {}", amount);
         Ok(amount)
     }
 }

### 2024-08-17 hello_world/src/processor.rs

@@ -119,45 +119,47 @@ impl Processor {
         let required_lamports = rent.minimum_balance(Mint::LEN);
         msg!("required_lamports: {}", required_lamports);
 
-        msg!("create mint accct");
-        invoke(
-            &solana_program::system_instruction::create_account(
-                payer_account.key,
-                mint_account.key,
-                required_lamports,
-                Mint::LEN as u64,
-                spl_account.key,
-            ),
-            &[
-                payer_account.clone(),
-                mint_account.clone(),
-                system_program.clone(),
-            ],
-        )?;
-        // }
+        if mint_account.data_is_empty() {
+            msg!("create mint accct");
+            invoke(
+                &solana_program::system_instruction::create_account(
+                    payer_account.key,
+                    mint_account.key,
+                    required_lamports,
+                    Mint::LEN as u64,
+                    spl_account.key,
+                ),
+                &[
+                    payer_account.clone(),
+                    mint_account.clone(),
+                    system_program.clone(),
+                ],
+            )?;
+            // }
 
-        msg!("after create mint accct, now init mint");
-        // Initialize the mint account
-        match invoke(
-            &initialize_mint(
-                &spl_token::id(),
-                &mint_account.key,
-                &payer_account.key,
-                Some(&payer_account.key),
-                0,
-            )?,
-            &[
-                mint_account.clone(),
-                rent_account.clone(),
-                payer_account.clone(),
-            ],
-        ) {
-            Ok(_) => msg!("Mint account initialized successfully"),
-            Err(e) => {
-                msg!("Failed to initialize mint account: {:?}", e);
-                return Err(e);
-            }
-        };
+            msg!("after create mint accct, now init mint");
+            // Initialize the mint account
+            match invoke(
+                &initialize_mint(
+                    &spl_token::id(),
+                    &mint_account.key,
+                    &payer_account.key,
+                    Some(&payer_account.key),
+                    0,
+                )?,
+                &[
+                    mint_account.clone(),
+                    rent_account.clone(),
+                    payer_account.clone(),
+                ],
+            ) {
+                Ok(_) => msg!("Mint account initialized successfully"),
+                Err(e) => {
+                    msg!("Failed to initialize mint account: {:?}", e);
+                    return Err(e);
+                }
+            };
+        }
 
         msg!("after init mint, now lets create vault");
 
@@ -712,22 +714,26 @@ impl Processor {
[…]

### 2024-08-17 hello_world/tests/test.rs

@@ -891,6 +891,7 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
         .get_rent()
         .await?
         .minimum_balance(TokenAccount::LEN);
+
     let create_token_account_ix = system_instruction::create_account(
         &payer.pubkey(),
         &user_token_keypair.pubkey(),
@@ -922,17 +923,48 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
 
     // Create the faucet instruction
     println!("Creating faucet instruction...");
-    let faucet_ix = Instruction::new_with_borsh(
+    // let faucet_ix = Instruction::new_with_borsh(
+    //     program_id,
+    //     &VaultInstruction::Faucet { amount: 1000 },
+    //     vec![
+    //         AccountMeta::new(payer.pubkey(), true),
+    //         AccountMeta::new(user_token_keypair.pubkey(), true),
+    //         AccountMeta::new(mint_keypair.pubkey(), true),
+    //         AccountMeta::new_readonly(spl_token::id(), false),
+    //         AccountMeta::new_readonly(rent_key, false),
+    //         AccountMeta::new_readonly(solana_program::system_program::id(), false),
+    //     ],
+    // );
+
+    // let faucet_ix = Instruction {
+    //     program_id,
+    //     accounts: vec![
+    //         AccountMeta::new(payer.pubkey(), true),
+    //         AccountMeta::new(user_token_keypair.pubkey(), true),
+    //         AccountMeta::new(mint_keypair.pubkey(), true),
+    //         AccountMeta::new_readonly(spl_token::id(), false),
+    //         AccountMeta::new_readonly(rent_key, false),
+    //         AccountMeta::new_readonly(solana_program::system_program::id(), false),
+    //     ],
+    //     data: vec![4, 100], // Instruction ID for "Deposit"
+    // };
+
+    let amount: u64 = 1000;
+    let mut data = vec![4]; // Instruction ID
+    data.extend_from_slice(&amount.to_le_bytes()); // Append the amount as an 8-byte little-endian value
+
+    let faucet_ix = Instruction {
         program_id,
-        &VaultInstruction::Faucet { amount: 1000 },
-        vec![
+        accounts: vec![
             AccountMeta::new(payer.pubkey(), true),
             AccountMeta::new(user_token_keypair.pubkey(), true),
             AccountMeta::new(mint_keypair.pubkey(), true),
             AccountMeta::new_readonly(spl_token::id(), false),
[…]

### 2024-08-17 hello_world/src/processor.rs
working faucet

@@ -710,8 +710,6 @@ impl Processor {
         Ok(())
     }
 
-    /////////////////////// TEST faucet
-    /// fn process_faucet(
     fn process_faucet(program_id: &Pubkey, accounts: &[AccountInfo], amount: u64) -> ProgramResult {
         let account_info_iter = &mut accounts.iter();
 
@@ -720,22 +718,32 @@ impl Processor {
         let mint_account = next_account_info(account_info_iter)?;
         let spl_account = next_account_info(account_info_iter)?;
         let rent_account = next_account_info(account_info_iter)?;
-        let system_program = next_account_info(account_info_iter)?; // Add this line to include the system program
+        let system_program = next_account_info(account_info_iter)?;
+
+        // Derive the PDA for the mint account
+        let (expected_mint_pubkey, bump_seed) =
+            Pubkey::find_program_address(&[b"mint"], program_id);
+
+        msg!("expected_mint_pubkey: {}", expected_mint_pubkey);
+        msg!("comparing it to: {}", mint_account.key);
+        // Ensure the derived mint address matches the passed mint account
+        if *mint_account.key != expected_mint_pubkey {
+            msg!("Error: Invalid mint account passed");
+            return Err(ProgramError::InvalidArgument);
+        }
 
         // Ensure the payer is a signer
         msg!("payer_account.is_signer: {}", payer_account.is_signer);
-        // if !payer_account.is_signer {
-        //     return Err(ProgramError::MissingRequiredSignature);
-        // }
 
         // Check if the mint account needs to be created and initialized
         if mint_account.data_is_empty() {
             let rent = Rent::get()?;
             let required_lamports = rent.minimum_balance(Mint::LEN);
 
-            msg!("1");
             // Create the mint account
-            invoke(
+            msg!("1");
+
+            invoke_signed(
                 &solana_program::system_instruction::create_account(
                     payer_account.key,
                     mint_account.key,
@@ -746,24 +754,27 @@ impl Processor {
                 &[
                     payer_account.clone(),
                     mint_account.clone(),
-                    // spl_account.clone(),
-                    system_program.clone(), // Include system program in the invoke call
+                    system_program.clone(),
                 ],
+                // &[&[b"vault_registry", &[bump_seed]]],
+                &[&[b"mint".as_ref(), &[bump_seed]]],
             )?;
 
-            msg!("2");
-            // Initialize the mint account
+            // msg!("2");
+
+            // // Initialize the mint account
             invoke(
[…]

### 2024-08-17 hello_world/tests/test.rs

@@ -847,9 +847,6 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
     println!("Starting test_faucet");
 
     let program_id = Pubkey::new_unique();
-    // let mint_authority = Keypair::new();
-    // let user_account = Keypair::new();
-
     let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(Processor::process));
 
     // Add SPL Token program
@@ -862,93 +859,17 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
     println!("Starting program test context...");
     let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
 
-    // Create mint account
-    println!("Creating mint account...");
-    let mint_keypair = Keypair::new();
-    let rent_key = solana_program::sysvar::rent::ID;
+    ///////////////////////////////
+    // Derive mint PDA as expected by the backend
+    let (mint_pubkey, _bump_seed) = Pubkey::find_program_address(&[b"mint"], &program_id);
+    // let mint_keypair = Keypair::new(); // Mint account
+    // let mint_pubkey = mint_keypair.pubkey();
 
-    let mint_rent = banks_client.get_rent().await?.minimum_balance(Mint::LEN);
-    let create_mint_ix = system_instruction::create_account(
-        &payer.pubkey(),
-        &mint_keypair.pubkey(),
-        mint_rent,
-        Mint::LEN as u64,
-        &spl_token::id(),
-    );
-    let initialize_mint_ix = spl_token::instruction::initialize_mint(
-        &spl_token::id(),
-        &mint_keypair.pubkey(),
-        &payer.pubkey(),
-        None,
-        0,
-    )
-    .map_err(|e| Box::new(e) as Box<dyn std::error::Error>)?;
-
-    // Create user token account
-    println!("Creating user token account...");
+    //////////////////////////////
+    // Create user token account keypair
     let user_token_keypair = Keypair::new();
-    let token_account_rent = banks_client
-        .get_rent()
-        .await?
-        .minimum_balance(TokenAccount::LEN);
 
-    let create_token_account_ix = system_instruction::create_account(
-        &payer.pubkey(),
-        &user_token_keypair.pubkey(),
-        token_account_rent,
-        TokenAccount::LEN as u64,
-        &spl_token::id(),
-    );
-    let initialize_token_account_ix = spl_token::instruction::initialize_account(
[…]

### 2024-08-17 hello_world/tests/test.rs
working faucet

@@ -867,7 +867,7 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
 
     //////////////////////////////
     // Create user token account keypair
-    let user_token_keypair = Keypair::new();
+    let user_token_keypair: Keypair = Keypair::new();
 
     // Prepare the faucet instruction
     let amount: u64 = 1000;

### 2024-08-18 hello_world/src/processor.rs
saved

@@ -12,6 +12,7 @@ use solana_program::{
     sysvar,
     sysvar::rent::Rent,
 };
+use spl_associated_token_account::get_associated_token_address;
 
 // use solana_sdk::program::invoke_signed;
 
@@ -63,11 +64,14 @@ impl Processor {
     @description Handles the creation of a new vault, including initializing the mint and vault accounts, and setting up the state account for the vault registry.
     @param program_id - The ID of the currently executing program.
     @param accounts - The accounts involved in the transaction.
+    @ note - creates a MINT, a VAULT, and a STATE account is they arent already made
     */
     fn process_create_vault(program_id: &Pubkey, accounts: &[AccountInfo]) -> ProgramResult {
         let account_info_iter = &mut accounts.iter();
         let payer_account = next_account_info(account_info_iter)?;
+        // mint for anticoins
         let mint_account = next_account_info(account_info_iter)?;
+        // the account that will hold Token A
         let vault_account = next_account_info(account_info_iter)?;
         let rent_account = next_account_info(account_info_iter)?;
         let spl_account = next_account_info(account_info_iter)?;
@@ -163,39 +167,86 @@ impl Processor {
 
         msg!("after init mint, now lets create vault");
 
+        //////////// NOTE DO WE MAKE A NEW VAULT ACCOUNT? or use an account
         let vault_required_lamports = rent.minimum_balance(spl_token::state::Account::LEN);
         msg!("Creating vault account");
-        invoke(
-            &solana_program::system_instruction::create_account(
-                payer_account.key,
-                vault_account.key,
-                vault_required_lamports,
-                spl_token::state::Account::LEN as u64,
-                spl_account.key,
-            ),
-            &[
-                payer_account.clone(),
-                vault_account.clone(),
-                system_program.clone(),
-            ],
-        )?;
-        msg!("after create vault, now lets init vault");
-        // Initialize the vault account (assuming it's a token account)
-        invoke(
-            &spl_token::instruction::initialize_account(
-                &spl_token::id(),
-                vault_account.key,
-                mint_account.key,
-                payer_account.key,
-            )?,
-            &[
-                vault_account.clone(),
-                mint_account.clone(),
-                rent_account.clone(),
-                payer_account.clone(),
-                spl_account.clone(),
-            ],
-        )?;
+        if vault_account.data_is_empty() {
+            //old
+            // invoke(
+            //     &solana_program::system_instruction::create_account(
+            //         payer_account.key,
+            //         vault_account.key,
+            //         vault_required_lamports,
[…]

### 2024-08-18 hello_world/src/processor.rs
iençworkign test with vault using associated token address instead of new

@@ -70,11 +70,14 @@ impl Processor {
         let account_info_iter = &mut accounts.iter();
         let payer_account = next_account_info(account_info_iter)?;
         // mint for anticoins
-        let mint_account = next_account_info(account_info_iter)?;
+        // let mint_account = next_account_info(account_info_iter)?;
+        let mint_account_token_a = next_account_info(account_info_iter)?;
+        let mint_account_a_token_a = next_account_info(account_info_iter)?;
         // the account that will hold Token A
         let vault_account = next_account_info(account_info_iter)?;
         let rent_account = next_account_info(account_info_iter)?;
         let spl_account = next_account_info(account_info_iter)?;
+
         let system_program = next_account_info(account_info_iter)?;
         // let state_account = next_account_info(account_info_iter)?; // Add this line
 
@@ -89,18 +92,40 @@ impl Processor {
             return Err(ProgramError::InvalidAccountData);
         }
 
+        let associated_token_program = next_account_info(account_info_iter)?;
+
         msg!("Creating vault...");
         msg!("payer account key: {:?}", payer_account.key);
-        msg!("Mint account key: {:?}", mint_account.key);
+        msg!("Mint account Token A key: {:?}", mint_account_token_a.key);
+        msg!(
+            "Mint account AToken A key: {:?}",
+            mint_account_a_token_a.key
+        );
         msg!("Vault account key: {:?}", vault_account.key);
         msg!("Rent account key: {:?}", rent_account.key);
         msg!("State account key: {:?}", state_account.key);
         msg!("SPL: {}", spl_token::id());
-        msg!("Mint account balance: {:?}", mint_account.lamports());
+
+        // NOTE: two mint types
+        // msg!("Mint account balance: {:?}", mint_account.lamports());
+        msg!(
+            "Mint Token Aaccount balance: {:?}",
+            mint_account_token_a.lamports()
+        );
+        msg!(
+            "Mint AToken A account balance: {:?}",
+            mint_account_a_token_a.lamports()
+        );
+
         msg!("Vault account balance: {:?}", vault_account.lamports());
         msg!("Rent account balance: {:?}", rent_account.lamports());
         msg!("Payer account balance: {:?}", payer_account.lamports());
         msg!("spl account balance: {:?}", spl_account.lamports());
+        msg!(
+            "associated token account balance: {:?}",
+            associated_token_program.lamports()
+        );
+
[…]

### 2024-08-18 hello_world/src/state.rs

@@ -2,7 +2,9 @@ use solana_program::pubkey::Pubkey;
 
 #[derive(Debug, PartialEq)]
 pub struct Vault {
+    // NOTE: Is a token Account associated with Token A's mint
     pub vault_account: Pubkey,
+    // NOTE: Is a mint for minting ATokenA
     pub mint_account: Pubkey,
     pub owner: Pubkey,
 }

### 2024-08-18 hello_world/tests/test.rs

@@ -5,6 +5,7 @@ use rugsafe::instruction::VaultInstruction;
 use rugsafe::process_instruction;
 use rugsafe::processor::Processor;
 use rugsafe::state::{Vault, VaultRegistry};
+use solana_program::hash::Hash;
 use solana_program::program_pack::Pack;
 use solana_program::rent::Rent;
 use solana_program::system_instruction;
@@ -23,6 +24,7 @@ use solana_sdk::{
     transaction::Transaction,
     transport::TransportError,
 };
+use spl_associated_token_account::get_associated_token_address;
 use spl_token::instruction::initialize_mint;
 use spl_token::state::Account as TokenAccount;
 use spl_token::state::Mint;
@@ -74,12 +76,11 @@ async fn test_create_vault() -> Result<(), TransportError> {
     // Setup keys and program
     let program_id = Pubkey::new_unique();
     let mint_keypair = Keypair::new(); // Mint account
-    let mint_key = mint_keypair.pubkey();
-    let vault_keypair = Keypair::new(); // Vault account
-    let vault_key = vault_keypair.pubkey();
+    let mint_atokena_key = mint_keypair.pubkey();
 
     let rent_key = solana_program::sysvar::rent::ID;
     let spl_key = spl_token::id();
+    let associated_token_program = spl_associated_token_account::id();
 
     // let state_keypair = Keypair::new(); // State account
 
@@ -106,14 +107,26 @@ async fn test_create_vault() -> Result<(), TransportError> {
     let rent_account = banks_client.get_account(rent_key).await?;
     assert!(rent_account.is_some(), "Rent account not found");
 
+    // Create token mint
+    let mint_tokena_keypair =
+        create_token_mint(banks_client, &payer, recent_blockhash, &payer.pubkey()).await?;
+    let mint_tokena_key = mint_tokena_keypair.pubkey();
+
+    // NOTE vault key should be associated token account for token a's mint
+    // let vault_keypair = Keypair::new(); // Vault account
+    // let vault_key = vault_keypair.pubkey();
+    let vault_key: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key);
+
     // Call the function to create the vault instruction
     println!("Creating vault instruction...");
     let create_vault_instruction = create_vault_instruction(
         &program_id,
         &vault_key,
-        &mint_key,
+        &mint_tokena_key,
+        &mint_atokena_key,
         &payer.pubkey(),
         &state_key,
+        &associated_token_program,
[…]

### 2024-08-19 hello_world/src/processor.rs
working with associated accounts

@@ -13,6 +13,7 @@ use solana_program::{
     sysvar::rent::Rent,
 };
 use spl_associated_token_account::get_associated_token_address;
+use spl_associated_token_account::{self, instruction};
 
 // use solana_sdk::program::invoke_signed;
 
@@ -201,7 +202,7 @@ impl Processor {
         msg!("after init mint, now lets create vault");
 
         //////////// NOTE DO WE MAKE A NEW VAULT ACCOUNT? or use an account
-        let vault_required_lamports = rent.minimum_balance(spl_token::state::Account::LEN);
+        // let vault_required_lamports = rent.minimum_balance(spl_token::state::Account::LEN);
         msg!("Creating vault account");
         if vault_account.data_is_empty() {
             // associated attempt
@@ -212,7 +213,9 @@ impl Processor {
                     payer_account.key,
                     payer_account.key,
                     mint_account_token_a.key, // the mint this associated account should be for is the token a mint
-                    &spl_token::id(),         // SPL Token program ID is needed here
+                    // NOTE:
+                    &spl_token::id(), // SPL Token program ID is needed here
+                                      // associated_token_program.key,
                 ),
                 &[
                     payer_account.clone(),        // Funding account
@@ -220,8 +223,9 @@ impl Processor {
                     payer_account.clone(),        // Wallet address
                     mint_account_token_a.clone(), // Token mint address
                     system_program.clone(),       // System program
-                    spl_account.clone(),          // SPL Token program
-                                                  // associated_token_program.clone(),
+                    // NOTE: spl or associated
+                    spl_account.clone(), // SPL Token program
+                                         // associated_token_program.clone(), // associated_token_program.clone(),
                 ],
             )?;
         } else {
@@ -452,9 +456,9 @@ impl Processor {
         );
 
         let user_token_account_info = TokenAccount::unpack(&user_token_a_account.data.borrow())?;
-        let vault_account_info = TokenAccount::unpack(&vault_account.data.borrow())?;
+        // let vault_account_info = TokenAccount::unpack(&vault_account.data.borrow())?;
 
-        msg!("Vault account mint: {}", vault_account_info.mint);
+        // msg!("Vault account mint: {}", vault_account_info.mint);
 
         // if user_token_account_info.mint != *mint_account.key {
         //     msg!("Error: The mint associated with the user's TokenA account does not match the expected mint.");
@@ -478,134 +482,136 @@ impl Processor {
[…]

### 2024-08-19 hello_world/tests/test.rs

@@ -75,8 +75,8 @@ async fn test_process_instruction() -> Result<(), TransportError> {
 async fn test_create_vault() -> Result<(), TransportError> {
     // Setup keys and program
     let program_id = Pubkey::new_unique();
-    let mint_keypair = Keypair::new(); // Mint account
-    let mint_atokena_key = mint_keypair.pubkey();
+    let mint_atokena_keypair = Keypair::new(); // Mint account
+    let mint_atokena_key = mint_atokena_keypair.pubkey();
 
     let rent_key = solana_program::sysvar::rent::ID;
     let spl_key = spl_token::id();
@@ -147,7 +147,7 @@ async fn test_create_vault() -> Result<(), TransportError> {
     transaction.sign(
         // &[&payer, &mint_keypair, &vault_keypair, &state_keypair],
         // &[&payer, &mint_keypair, &vault_keypair],
-        &[&payer, &mint_keypair],
+        &[&payer, &mint_tokena_keypair, &mint_atokena_keypair],
         recent_blockhash,
     );
 
@@ -173,100 +173,100 @@ async fn test_create_vault() -> Result<(), TransportError> {
     println!("Test completed successfully.");
     Ok(())
 }
-#[tokio::test]
-async fn test_create_two_vaults() -> Result<(), TransportError> {
-    // Setup keys and program
-    let program_id = Pubkey::new_unique();
+// #[tokio::test]
+// async fn test_create_two_vaults() -> Result<(), TransportError> {
+//     // Setup keys and program
+//     let program_id = Pubkey::new_unique();
 
-    let rent_key = solana_program::sysvar::rent::ID;
-    let spl_key = spl_token::id();
-    let associated_token_program = spl_associated_token_account::id();
+//     let rent_key = solana_program::sysvar::rent::ID;
+//     let spl_key = spl_token::id();
+//     let associated_token_program = spl_associated_token_account::id();
 
-    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(process_instruction));
+//     let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(process_instruction));
 
-    // Derive the state account PDA
-    let (state_account_pda, _bump_seed) =
-        Pubkey::find_program_address(&[b"vault_registry"], &program_id);
+//     // Derive the state account PDA
+//     let (state_account_pda, _bump_seed) =
+//         Pubkey::find_program_address(&[b"vault_registry"], &program_id);
 
-    // Add SPL Token program
-    program_test.add_program(
[…]

### 2024-08-19 hello_world/tests/test.rs
update

@@ -173,100 +173,101 @@ async fn test_create_vault() -> Result<(), TransportError> {
     println!("Test completed successfully.");
     Ok(())
 }
-// #[tokio::test]
-// async fn test_create_two_vaults() -> Result<(), TransportError> {
-//     // Setup keys and program
-//     let program_id = Pubkey::new_unique();
 
-//     let rent_key = solana_program::sysvar::rent::ID;
-//     let spl_key = spl_token::id();
-//     let associated_token_program = spl_associated_token_account::id();
+#[tokio::test]
+async fn test_create_two_vaults() -> Result<(), TransportError> {
+    // Setup keys and program
+    let program_id = Pubkey::new_unique();
 
-//     let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(process_instruction));
+    let rent_key = solana_program::sysvar::rent::ID;
+    let spl_key = spl_token::id();
+    let associated_token_program = spl_associated_token_account::id();
 
-//     // Derive the state account PDA
-//     let (state_account_pda, _bump_seed) =
-//         Pubkey::find_program_address(&[b"vault_registry"], &program_id);
+    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(process_instruction));
 
-//     // Add SPL Token program
-//     program_test.add_program(
-//         "spl_token",
-//         spl_key,
-//         processor!(spl_token::processor::Processor::process),
-//     );
+    // Derive the state account PDA
+    let (state_account_pda, _bump_seed) =
+        Pubkey::find_program_address(&[b"vault_registry"], &program_id);
 
-//     // Start the context
-//     let mut context = program_test.start_with_context().await;
-//     let banks_client = &mut context.banks_client;
-//     let payer = &context.payer;
-//     let recent_blockhash = banks_client.get_latest_blockhash().await?;
+    // Add SPL Token program
+    program_test.add_program(
+        "spl_token",
+        spl_key,
+        processor!(spl_token::processor::Processor::process),
+    );
 
-//     // Retrieve rent details
-//     println!("Retrieving rent details...");
-//     let rent_account = banks_client.get_account(rent_key).await?;
-//     assert!(rent_account.is_some(), "Rent account not found");
+    // Start the context
+    let mut context = program_test.start_with_context().await;
+    let banks_client = &mut context.banks_client;
+    let payer = &context.payer;
[…]

### 2024-08-22 hello_world/rugsafe/paper/paper.tex
saved

@@
 \usepackage{amsmath}
+\usepackage{graphicx} % Add this line
+\usepackage{xcolor}
+\pagecolor{black}
+\color{white}
 
 \title{Rugsafe: A Protocol for Protecting Digital Assets from Rug Pulls}
-\author{info@Rugsafe.org}
+\author{info@rugsafe.org}
 \date{v0.0.1 August 1, 2024}
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\textwidth]{images/2.png}
+\caption{The inverse logarithmic relationship between the price of the underlying rugged token $C_r$ and the amount of minted anticoins $C_a$.
+As the price of $C_r$ decreases, the amount of minted $C_a$ increases, providing stability and protection for holders.}
+\label{fig:minted_anticoins}
+\end{figure}
+
 \subsection{User Commitment and Signal to the Ecosystem}
@@
 
-\section{Conclusion}
+\section{Closing Remarks}
 Rugsafe presents a robust mathematical framework designed to protect against rug pulls in the DeFi space.

### 2024-08-22 hello_world/src/processor.rs

@@ -95,7 +95,7 @@ impl Processor {
 
         let associated_token_program = next_account_info(account_info_iter)?;
 
-        msg!("Creating vault...");
+        // msg!("Creating vault...");
         msg!("payer account key: {:?}", payer_account.key);
         msg!("Mint account Token A key: {:?}", mint_account_token_a.key);
         msg!(
@@ -151,10 +151,10 @@ impl Processor {
         msg!("required_lamports: {}", required_lamports);
 
         //NOTE: ensure Token A mint is not empty
-        if mint_account_token_a.data_is_empty() {
-            msg!("ERROR: mint_account_token_a should not be empty at vault creation time");
-            return Err(ProgramError::Custom(99));
-        }
+        // if mint_account_token_a.data_is_empty() {
+        //     msg!("ERROR: mint_account_token_a should not be empty at vault creation time");
+        //     return Err(ProgramError::Custom(99));
+        // }
 
         // NOTE: check if ATokenA mint is empty, since we need to mint atokens
         if mint_account_a_token_a.data_is_empty() {
@@ -199,7 +199,7 @@ impl Processor {
             };
         }
 
-        msg!("after init mint, now lets create vault");
+        // msg!("after init mint, now lets create vault");
 
         //////////// NOTE DO WE MAKE A NEW VAULT ACCOUNT? or use an account
         // let vault_required_lamports = rent.minimum_balance(spl_token::state::Account::LEN);
@@ -460,10 +460,10 @@ impl Processor {
 
         // msg!("Vault account mint: {}", vault_account_info.mint);
 
-        // if user_token_account_info.mint != *mint_account.key {
-        //     msg!("Error: The mint associated with the user's TokenA account does not match the expected mint.");
-        //     return Err(ProgramError::InvalidAccountData);
-        // }
+        if user_token_account_info.mint != *mint_token_a_account.key {
+            msg!("Error: The mint associated with the user's TokenA account does not match the expected mint.");
+            return Err(ProgramError::InvalidAccountData);
+        }
 
         if user_token_account_info.owner != *payer_account.key {
             msg!("Error: Payer account does not own the user TokenA account.");
@@ -472,6 +472,17 @@ impl Processor {
 
         let user_atoken_account = next_account_info(account_info_iter)?; // User's aTokenA account
         msg!("User aTokenA account: {}", user_atoken_account.key);
+
+        // msg!("user_atoken_account.data: {}", user_atoken_account.data);
[…]

### 2024-08-22 hello_world/tests/test.rs

@@ -75,8 +75,6 @@ async fn test_process_instruction() -> Result<(), TransportError> {
 async fn test_create_vault() -> Result<(), TransportError> {
     // Setup keys and program
     let program_id = Pubkey::new_unique();
-    let mint_atokena_keypair = Keypair::new(); // Mint account
-    let mint_atokena_key = mint_atokena_keypair.pubkey();
 
     let rent_key = solana_program::sysvar::rent::ID;
     let spl_key = spl_token::id();
@@ -107,10 +105,17 @@ async fn test_create_vault() -> Result<(), TransportError> {
     let rent_account = banks_client.get_account(rent_key).await?;
     assert!(rent_account.is_some(), "Rent account not found");
 
+    ////////////////////////
+    /// ///////////////// TODO
+    /// /////////////////////
     // Create token mint
     let mint_tokena_keypair =
         create_token_mint(banks_client, &payer, recent_blockhash, &payer.pubkey()).await?;
     let mint_tokena_key = mint_tokena_keypair.pubkey();
+
+    // NOTE: SHOULD THE A TOKEN MINT BE A NEW KEYPAIR?
+    let mint_atokena_keypair = Keypair::new(); // Mint account
+    let mint_atokena_key = mint_atokena_keypair.pubkey();
 
     // NOTE vault key should be associated token account for token a's mint
     // let vault_keypair = Keypair::new(); // Vault account
@@ -151,7 +156,7 @@ async fn test_create_vault() -> Result<(), TransportError> {
         recent_blockhash,
     );
 
-    println!("after sign");
+    // println!("after sign");
 
     // Process CreateVault transaction
     println!("Processing CreateVault transaction...");
@@ -388,22 +393,8 @@ async fn test_deposit() -> Result<(), BanksClientError> {
     println!("Creating associated token account for ATokenA...");
     let user_atoken_a_account = get_associated_token_address(&payer.pubkey(), &mint_atokena_key);
     println!("user_atoken_a_account: {}", user_atoken_a_account);
-    // let create_user_atoken_a_account_ix =
-    //     &spl_associated_token_account::instruction::create_associated_token_account(
-    //         &payer.pubkey(),   // Payer
-    //         &payer.pubkey(),   // Owner of the associated account
-    //         &mint_atokena_key, // Mint for ATokenA
-    //         &spl_token::id(),
-    //     );
 
-    // let transaction = Transaction::new_signed_with_payer(
[…]

### 2024-08-24 hello_world/rugsafe/paper/paper.tex
updated paper

@@
 
+%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{Vault Creation and Anticoin Issuance}
@@
 The vaults are held in a central vault registry, ensuring that all interactions with rugged tokens are tracked and managed within the system.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 The penalty mechanism incentivizes holding $C_a$ longer, as the remaining holders benefit from these penalties.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-This burning mechanism enhances the credibility of the user's claim that $C_r$ is a rugged token and provides additional confidence to other participants in the ecosystem.
+This burning mechanism not only signals the user's conviction but also impacts the market by reducing the circulating supply of $C_a$.
+As $C_a$ tokens are burned, the inverse relationship between the price of $C_a$ and $C_r$ continues to hold, but with a nuanced adjustment reflecting the decreased supply of $C_a$.
 
-\subsection{Opportunities for New Developments}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.8\textwidth]{images/3.png}
+\caption{The adjusted inverse logarithmic relationship between the price of the underlying rugged token $C_r$ and the amount of burned anticoins $C_a$.
+As the price of $C_r$ decreases, the amount of burned $C_a$ decreases, further solidifying the protective mechanism for holders.}
+\label{fig:burned_anticoins}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Opportunities for New Ecosystems}
 The Rugsafe protocol's structure opens up opportunities for developers to build applications that cater to the needs of rug pull victims.
 By establishing a market for anticoin tokens $C_a$, new financial products and services can be developed to support users who have suffered losses from rug pulls.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2024-08-25 hello_world/tests/test.rs
saved

@@ -152,7 +152,8 @@ async fn test_create_vault() -> Result<(), TransportError> {
     transaction.sign(
         // &[&payer, &mint_keypair, &vault_keypair, &state_keypair],
         // &[&payer, &mint_keypair, &vault_keypair],
-        &[&payer, &mint_tokena_keypair, &mint_atokena_keypair],
+        // &[&payer, &mint_tokena_keypair, &mint_atokena_keypair],
+        &[&payer, &mint_atokena_keypair],
         recent_blockhash,
     );
 
@@ -217,6 +218,10 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
         create_token_mint(banks_client, &payer, recent_blockhash, &payer.pubkey()).await?;
     let mint_tokena_key1 = mint_tokena_keypair1.pubkey();
 
+    // Create a new keypair for AToken A
+    let mint_atokena_keypair1 = Keypair::new();
+    let mint_atokena_key1 = mint_atokena_keypair1.pubkey();
+
     // Derive the associated token account for the first vault
     let vault_key1: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key1);
 
@@ -225,8 +230,8 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
     let create_vault_instruction1 = create_vault_instruction(
         &program_id,
         &vault_key1,
-        &mint_tokena_key1, // Token A mint
-        &mint_tokena_key1, // AToken A mint
+        &mint_tokena_key1,  // Token A mint
+        &mint_atokena_key1, // AToken A mint
         &payer.pubkey(),
         &state_account_pda,
         &associated_token_program,
@@ -234,7 +239,7 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
 
     let mut transaction1 =
         Transaction::new_with_payer(&[create_vault_instruction1], Some(&payer.pubkey()));
-    transaction1.sign(&[&payer, &mint_tokena_keypair1], recent_blockhash);
+    transaction1.sign(&[&payer, &mint_atokena_keypair1], recent_blockhash);
     banks_client.process_transaction(transaction1).await?;
 
     // Verify first vault creation
@@ -246,6 +251,10 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
         create_token_mint(banks_client, &payer, recent_blockhash, &payer.pubkey()).await?;
     let mint_tokena_key2 = mint_tokena_keypair2.pubkey();
 
[…]

### 2024-08-25 site2/src/script.js

@@ -1,0 +1,37 @@
+// init
+const camera = new THREE.PerspectiveCamera(70, window.innerWidth / window.innerHeight, 0.01, 10);
+camera.position.z = 3;
+
+const scene = new THREE.Scene();
+
+// lighting
+const light = new THREE.DirectionalLight(0xffffff, 1);
+light.position.set(1, 1, 1).normalize();
+scene.add(light);
+
+// load fbx model
+const loader = new THREE.FBXLoader();
+// loader.load('https://threejs.org/examples/models/fbx/Samba%20Dancing.fbx', function (object) {
+loader.load('http://localhost:4000/src/1.fbx', function (object) {
+  // scale the model if necessary
+  object.scale.set(0.01, 0.01, 0.01); // Adjust the scale based on your model's size
+
+  scene.add(object);
+}, undefined, function (error) {
+  console.error('An error happened while loading the FBX model:', error);
+});
+
+// renderer
+const renderer = new THREE.WebGLRenderer({ antialias: true });
+renderer.setSize(window.innerWidth, window.innerHeight);
+document.body.appendChild(renderer.domElement);
+
+// animation loop
+function animation(time) {
+  // Optional: rotate the scene or specific objects
+  scene.rotation.y += 0.01;
+
+  renderer.render(scene, camera);
+}
+
+renderer.setAnimationLoop(animation);

### 2024-08-25 hello_world/src/processor.rs
deposit works from UI, hardcoded both token balance addresses

@@ -203,10 +203,9 @@ impl Processor {
 
         //////////// NOTE DO WE MAKE A NEW VAULT ACCOUNT? or use an account
         // let vault_required_lamports = rent.minimum_balance(spl_token::state::Account::LEN);
-        msg!("Creating vault account");
         if vault_account.data_is_empty() {
             // associated attempt
-            msg!("Actually Creating Associated Token vault account");
+            // msg!("Actually Creating Associated Token vault account");
 
             invoke(
                 &spl_associated_token_account::instruction::create_associated_token_account(
@@ -242,7 +241,7 @@ impl Processor {
             let state_account_required_lamports = rent.minimum_balance(state_account_size);
 
             // Create the state account
-            msg!("about to create state cuz its empty");
+            // msg!("about to create state cuz its empty");
 
             // invoke(
             invoke_signed(
@@ -265,9 +264,10 @@ impl Processor {
             // Initialize VaultRegistry and serialize it into the state account's data
             let mut vault_registry = VaultRegistry { vaults: Vec::new() };
 
-            let new_vault: Vault = Vault {
+            let new_vault = Vault {
                 vault_account: *vault_account.key,
-                mint_account: *mint_account_a_token_a.key,
+                mint_token_a: *mint_account_token_a.key,
+                mint_a_token_a: *mint_account_a_token_a.key,
                 owner: *payer_account.key,
             };
 
@@ -342,7 +342,7 @@ impl Processor {
                 return Err(ProgramError::Custom(2));
             }
 
-            msg!("State account initialized successfully");
+            // msg!("State account initialized successfully");
         } else {
             msg!("State account is already initialized");
 
@@ -359,7 +359,8 @@ impl Processor {
             // Step 2: Add the new vault to the registry
             let new_vault = Vault {
                 vault_account: *vault_account.key,
-                mint_account: *mint_account_a_token_a.key,
+                mint_token_a: *mint_account_token_a.key,
+                mint_a_token_a: *mint_account_a_token_a.key,
                 owner: *payer_account.key,
             };
 
@@ -387,7 +388,7 @@ impl Processor {
                 &state_data[..64]
             );
 
-            msg!("VaultRegistry updated successfully");
+            // msg!("VaultRegistry updated successfully");
 
             // Log the number of vaults in the registry after the update
             let vault_count = vault_registry.vault_count();
@@ -460,6 +461,7 @@ impl Processor {
 
[…]

### 2024-08-25 hello_world/src/state.rs

@@ -2,10 +2,12 @@ use solana_program::pubkey::Pubkey;
 
 #[derive(Debug, PartialEq)]
 pub struct Vault {
-    // NOTE: Is a token Account associated with Token A's mint
+    // The token account associated with Token A's mint
     pub vault_account: Pubkey,
-    // NOTE: Is a mint for minting ATokenA
-    pub mint_account: Pubkey,
+    // The mint for minting ATokenA
+    pub mint_token_a: Pubkey,
+    // The mint for Token A
+    pub mint_a_token_a: Pubkey,
     pub owner: Pubkey,
 }
 
@@ -15,7 +17,7 @@ pub struct VaultRegistry {
 }
 
 impl Vault {
-    pub const LEN: usize = 32 * 3; // 5 Pubkeys, each 32 bytes
+    pub const LEN: usize = 32 * 4; // 5 Pubkeys, each 32 bytes
 
     /*
     @name serialize
@@ -25,7 +27,8 @@ impl Vault {
     pub fn serialize(&self) -> Vec<u8> {
         let mut data = Vec::with_capacity(Self::LEN);
         data.extend_from_slice(self.vault_account.as_ref());
-        data.extend_from_slice(self.mint_account.as_ref());
+        data.extend_from_slice(self.mint_token_a.as_ref());
+        data.extend_from_slice(self.mint_a_token_a.as_ref());
         data.extend_from_slice(self.owner.as_ref());
         data
     }
@@ -37,12 +40,14 @@ impl Vault {
     */
     pub fn deserialize(input: &[u8]) -> Self {
         let vault_account = Pubkey::new_from_array(input[0..32].try_into().unwrap());
-        let mint_account = Pubkey::new_from_array(input[32..64].try_into().unwrap());
-        let owner = Pubkey::new_from_array(input[64..96].try_into().unwrap());
+        let mint_token_a = Pubkey::new_from_array(input[32..64].try_into().unwrap());
+        let mint_a_token_a = Pubkey::new_from_array(input[64..96].try_into().unwrap());
+        let owner = Pubkey::new_from_array(input[96..128].try_into().unwrap());
 
         Vault {
             vault_account,
-            mint_account,
+            mint_token_a,
+            mint_a_token_a,
             owner,
         }
     }

### 2024-08-25 hello_world/tests/test.rs

@@ -279,6 +279,64 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
     let vault_account2 = banks_client.get_account(vault_key2).await?;
     assert!(vault_account2.is_some(), "Second vault account not created");
 
+    //assertions
+
+    // Fetch and verify the state account (VaultRegistry)
+    let state_account = banks_client.get_account(state_account_pda).await?;
+    assert!(state_account.is_some(), "State account not found");
+    let state_data = state_account.unwrap().data;
+
+    // Deserialize the VaultRegistry
+    let vault_registry =
+        VaultRegistry::deserialize(&state_data).expect("Failed to deserialize VaultRegistry");
+
+    // Ensure the vault registry contains two vaults
+    assert_eq!(
+        vault_registry.vaults.len(),
+        2,
+        "Vault registry should contain exactly two vaults"
+    );
+
+    // Verify the first vault's details
+    let first_vault = &vault_registry.vaults[0];
+    assert_eq!(
+        first_vault.vault_account, vault_key1,
+        "First vault account mismatch"
+    );
+    assert_eq!(
+        first_vault.mint_token_a, mint_tokena_key1,
+        "First mint_token_a mismatch"
+    );
+    assert_eq!(
+        first_vault.mint_a_token_a, mint_atokena_key1,
+        "First mint_a_token_a mismatch"
+    );
+    assert_eq!(
+        first_vault.owner,
+        payer.pubkey(),
+        "First vault owner mismatch"
+    );
+
+    // Verify the second vault's details
+    let second_vault = &vault_registry.vaults[1];
+    assert_eq!(
+        second_vault.vault_account, vault_key2,
+        "Second vault account mismatch"
+    );
+    assert_eq!(
+        second_vault.mint_token_a, mint_tokena_key2,
+        "Second mint_token_a mismatch"
+    );
+    assert_eq!(
+        second_vault.mint_a_token_a, mint_atokena_key2,
+        "Second mint_a_token_a mismatch"
+    );
+    assert_eq!(
+        second_vault.owner,
+        payer.pubkey(),
+        "Second vault owner mismatch"
+    );
+
     println!("Both vaults created successfully.");
     Ok(())
 }
@@ -497,6 +555,7 @@ fn create_vault_instruction(
         data: vec![0], // Add any additional data if needed
     }
 }
+
[…]

### 2024-08-25 hello_world/src/processor.rs
made vault registry dynamically sized

@@ -237,7 +237,8 @@ impl Processor {
         // Check if state account is empty and initialize it
         if state_account.data_is_empty() {
             // Correctly calculate the required size of the state account
-            let state_account_size = VaultRegistry::LEN;
+            let mut vault_registry = VaultRegistry::new();
+            let state_account_size = vault_registry.len();
             let state_account_required_lamports = rent.minimum_balance(state_account_size);
 
             // Create the state account
@@ -262,7 +263,7 @@ impl Processor {
             )?;
 
             // Initialize VaultRegistry and serialize it into the state account's data
-            let mut vault_registry = VaultRegistry { vaults: Vec::new() };
+            // let mut vault_registry = VaultRegistry { vaults: Vec::new() };
 
             let new_vault = Vault {
                 vault_account: *vault_account.key,
@@ -282,17 +283,17 @@ impl Processor {
             msg!("Number of vaults after addition: {}", number_of_vaults);
 
             // Debug: Print the vault registry state before serialization
-            msg!("VaultRegistry before serialization: {:?}", vault_registry);
+            // msg!("VaultRegistry before serialization: {:?}", vault_registry);
 
             let mut state_data = state_account.data.borrow_mut();
 
             // Perform serialization with error handling
             let serialized_data = vault_registry.serialize();
 
-            if serialized_data.len() != VaultRegistry::LEN {
+            if serialized_data.len() != vault_registry.len() {
                 msg!(
                     "Serialized length mismatch: expected {}, got {}",
-                    VaultRegistry::LEN,
+                    vault_registry.len(),
                     serialized_data.len()
                 );
                 return Err(ProgramError::Custom(1));
@@ -300,7 +301,7 @@ impl Processor {
 
             // Verify length of serialized data
             let serialized_length = state_data.len();
-            let expected_length = VaultRegistry::LEN;
+            let expected_length = vault_registry.len();
 
             // Log the serialized and expected length
 
@@ -309,10 +310,10 @@ impl Processor {
             msg!("Expected length: {}", expected_length);
             msg!("actual_serialized_length: {}", actual_serialized_length);
 
-            if serialized_data.len() != VaultRegistry::LEN {
+            if serialized_data.len() != vault_registry.len() {
                 msg!(
                     "Serialized length mismatch: expected {}, got {}",
-                    VaultRegistry::LEN,
+                    vault_registry.len(),
                     serialized_data.len()
                 );
[…]

### 2024-08-25 hello_world/src/state.rs

@@ -2,11 +2,8 @@ use solana_program::pubkey::Pubkey;
 
 #[derive(Debug, PartialEq)]
 pub struct Vault {
-    // The token account associated with Token A's mint
     pub vault_account: Pubkey,
-    // The mint for minting ATokenA
     pub mint_token_a: Pubkey,
-    // The mint for Token A
     pub mint_a_token_a: Pubkey,
     pub owner: Pubkey,
 }
@@ -14,16 +11,12 @@ pub struct Vault {
 #[derive(Debug, PartialEq)]
 pub struct VaultRegistry {
     pub vaults: Vec<Vault>,
+    pub capacity: usize,
 }
 
 impl Vault {
-    pub const LEN: usize = 32 * 4; // 5 Pubkeys, each 32 bytes
+    pub const LEN: usize = 32 * 4; // 4 Pubkeys, each 32 bytes
 
-    /*
-    @name serialize
-    @description Serializes a `Vault` instance into a vector of bytes, converting the internal Pubkey fields into a byte representation.
-    @param &self - A reference to the `Vault` instance being serialized.
-    */
     pub fn serialize(&self) -> Vec<u8> {
         let mut data = Vec::with_capacity(Self::LEN);
         data.extend_from_slice(self.vault_account.as_ref());
@@ -33,11 +26,6 @@ impl Vault {
         data
     }
 
-    /*
-    @name deserialize
-    @description Deserializes a slice of bytes into a `Vault` instance, reconstructing the internal Pubkey fields from their byte representation.
-    @param input - A byte slice representing the serialized `Vault` data.
-    */
     pub fn deserialize(input: &[u8]) -> Self {
         let vault_account = Pubkey::new_from_array(input[0..32].try_into().unwrap());
         let mint_token_a = Pubkey::new_from_array(input[32..64].try_into().unwrap());
@@ -54,41 +42,48 @@ impl Vault {
 }
 
 impl VaultRegistry {
-    pub const MAX_VAULTS: usize = 10;
-    pub const LEN: usize = 4 + (Vault::LEN * Self::MAX_VAULTS); // 4 bytes for vec length
+    pub const INITIAL_CAPACITY: usize = 10;
 
-    /*
-    @name serialize
-    @description Serializes a `VaultRegistry` instance into a vector of bytes, converting the internal vault list into a byte representation.
-    @param &self - A reference to the `VaultRegistry` instance being serialized.
-    */
+    pub fn new() -> Self {
[…]

### 2024-08-25 hello_world/tests/test.rs

@@ -827,10 +827,10 @@ async fn test_fetch_vault_with_data_from_registry() -> Result<(), TransportError
     println!("State account data length: {}", state_data.len());
     println!("First 32 bytes of state data: {:?}", &state_data[..32]);
 
-    println!(
-        "Expected size of VaultRegistry struct: {}",
-        VaultRegistry::LEN
-    );
+    // println!(
+    //     "Expected size of VaultRegistry struct: {}",
+    //     VaultRegistry::LEN
+    // );
     println!(
         "Actual size of data to be deserialized: {}",
         state_data.len()

### 2024-08-26 hello_world/tests/test.rs
fixed offet isssue for custom serialization of vault registry

@@ -176,6 +176,41 @@ async fn test_create_vault() -> Result<(), TransportError> {
     let vault_account = banks_client.get_account(vault_key).await?;
     assert!(vault_account.is_some(), "Vault account not created");
 
+    // assertions
+    let state_account = banks_client.get_account(state_key).await?;
+    assert!(state_account.is_some(), "State account not found");
+    let state_data = state_account.unwrap().data;
+
+    // Deserialize the VaultRegistry
+    let vault_registry =
+        VaultRegistry::deserialize(&state_data).expect("Failed to deserialize VaultRegistry");
+
+    // Ensure the vault registry contains two vaults
+    assert_eq!(
+        vault_registry.vaults.len(),
+        1,
+        "Vault registry should contain exactly one vault"
+    );
+
+    let first_vault = &vault_registry.vaults[0];
+    assert_eq!(
+        first_vault.vault_account, vault_key,
+        "First vault account mismatch"
+    );
+    assert_eq!(
+        first_vault.mint_token_a, mint_tokena_key,
+        "First mint_token_a mismatch"
+    );
+    assert_eq!(
+        first_vault.mint_a_token_a, mint_atokena_key,
+        "First mint_a_token_a mismatch"
+    );
+    assert_eq!(
+        first_vault.owner,
+        payer.pubkey(),
+        "First vault owner mismatch"
+    );
+
     println!("Test completed successfully.");
     Ok(())
 }

### 2024-08-31 hello_world/rugsafe/paper/paper.tex
saved
updated paper

--- 2024-08-22 hello_world/rugsafe/paper/paper.tex
@@
 \color{white}
+
+\definecolor{lightpurple}{rgb}{0.85, 0.85, 1} % Light purple background color
+\definecolor{white}{rgb}{1, 1, 1} % White text color
+
+%\pagecolor{lightpurple}
+%\color{black}
 
@@
 
+%\begin{abstract}
+%Rugsafe introduces a novel protocol designed to mitigate the risks associated with rug pulls in decentralized finance (DeFi).
+By leveraging cryptographic primitives and economic incentives, Rugsafe provides a framework that ensures the security and recoverability of assets when fraudulent activities are detected.
+The protocol is built around the concept of vaults for rugged tokens, issuance of anticoin tokens, and an incentive mechanism that penalizes and rewards users based on their interaction with the system.
+Rugsafe integrates seamlessly with existing DeFi platforms, offering an additional layer of security without compromising the decentralization principles.
+%\end{abstract}
+
 \begin{abstract}
@@
 By leveraging cryptographic primitives and economic incentives, Rugsafe provides a framework that ensures the security and recoverability of assets when fraudulent activities are detected.
-The protocol is built around the concept of vaults for rugged tokens, issuance of anticoin tokens, and an incentive mechanism that penalizes and rewards users based on their interaction with the system.
+The protocol revolves around the concept of vaults for rugged tokens, issuance of anticoin tokens as receipts, and a mechanism that regulates the supply of the native Rugsafe token in response to the volume of rugged tokens.
 Rugsafe integrates seamlessly with existing DeFi platforms, offering an additional layer of security without compromising the decentralization principles.
@@
 %\twocolumn
+
 \section{Overview}
 
-The Rugsafe protocol enables users who hold rugged tokens, denoted as $C_r$, to deposit these tokens into a specialized vault $V_c$ and receive an equal amount of anticoin tokens, $C_a$, which are pegged to the inverse price movement of $C_r$.
+The Rugsafe protocol enables users who hold rugged tokens, denoted as $C_r$, to deposit these tokens into a specialized vault $V_c$ and receive anticoin tokens, $C_a$,  which serve as receipts, \(\mathcal{R} \).
+The supply of Rugsafe's native token, $R$, is regulated based on the total value of rugged tokens in existence.
+
+%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Definition of a Rug Pull}
+
+A rug pull is a deceptive practice in the cryptocurrency and decentralized finance (DeFi) space, where the creators of a token, referred to as the "rug token," exploit the trust of users to siphon off liquidity and leave the victims holding worthless tokens.
+
+\subsection{Mechanism of a Rug Pull}
+
+1.
+\textbf{Creation of the Rug Token}: The token creator mints a large supply of a new token, the "rug token." The creator initially provides liquidity by pairing this rug token with another, more liquid token (e.g., ETH, USDC) and deposits both into a liquidity pool.
+
+2.
+\textbf{Attracting Liquidity}: As users begin to deposit their liquid tokens into the liquidity pool, believing in the legitimacy of the rug token, the pool's liquidity increases.
+Users typically deposit into the pool to earn trading fees or staking rewards.
+
+3.
+\textbf{Exploitation}: The token creator, who retains a significant portion of the rug token supply, waits until sufficient liquidity has been added by users.
+The creator then uses their large supply of rug tokens to swap out all the liquid tokens from the pool.
+
+\[
+\text{Rug Creator's Swap} = \text{Large Supply of Rug Token} \rightarrow \text{Withdrawal of All Liquid Tokens}
+\]
+
+4.
+\textbf{Outcome for Victims}: After the swap, the liquidity pool is drained of its valuable liquid tokens, leaving the victims holding a large number of rug tokens that are now worthless.
+The victims are left with an illiquid and devalued asset, while the creator absconds with the liquid tokens.
+
+\[
+\text{Victim's Holding} = \text{Rug Token (Now Worthless)}
+\]
+
+\subsection{Impact and Prevention}
+
+The practice of rug pulling is highly damaging to the victims, as it results in the loss of their liquid tokens in exchange for a worthless asset.
+The Rugsafe protocol is designed to prevent such scenarios by introducing mechanisms that ensure tokens minted on the Rugsafe chain are rugproof by default.
+
+Through mechanisms like bonding, claim processes, and community-driven challenge periods, the Rugsafe protocol provides a robust framework to protect users from potential rug pulls.
+By requiring issuers to post a bond at token issuance and allowing the community to challenge suspected rug pulls, the protocol empowers users to take proactive steps in safeguarding their investments.
+
+By defining and understanding the mechanics of a rug pull, the importance of the Rugsafe protocol's protective measures becomes clear.
+The protocol not only mitigates the risk of rug pulls but also creates a safer environment for the development and trading of new tokens within the ecosystem.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{Vault Creation and Anticoin Issuance}
-When a vault $V_c$ is created for a rugged token $C_r$, users can deposit $C_r$ into this vault. Upon deposit, the protocol mints an equal amount of $C_a$, which is credited to the user's balance.
+When a vault $V_c$ is created for a rugged token $C_r$, users can deposit $C_r$ into this vault.
+Upon deposit, the protocol mints an equal amount of $C_a$ tokens, which are credited to the user's balance.
+These $C_a$ tokens serve as a new, clean fungible token for the rugged victim, issued 1:1 with the underlying rugged token.
 
@@
 
+In addition to the 1:1 $C_a$ tokens, the user may also receive a receipt, \(\mathcal{R} \) , in the form of a non-fungible token (NFT) or a refungible token (RFT).
+The 1:1 $C_a$ token acts as a standard fungible token, fully transferable and tradable.
+However, the receipt could also be issued as an NFT, representing a unique claim on the deposited rugged tokens.
+Alternatively, the receipt can be an RFT, where an NFT representing the deposit is held by a contract.
+The contract then distributes shares of the NFT by issuing a fungible token that serves as representative shares of the underlying NFT.
+
+The type of asset used as the receipt, whether fungible, non-fungible, or refungible, is parameterized at the time of vault creation, with the relationship expressed as:
+
+\[
+\mathcal{R} = f(C_r, \tau)
+\]
+
+where $\text{type}$ determines whether the receipt is a fungible token, an NFT, or an RFT.
+This provides flexibility depending on the specific use case or preferences of the depositor.
 The vaults are held in a central vault registry, ensuring that all interactions with rugged tokens are tracked and managed within the system.
+Regardless of the type of receipt issued, depositors always receive the 1:1 $C_a$ tokens as a clean representation of their original rugged tokens.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{equation}
-C_{r,\text{withdrawn}} = C_{r,\text{deposited}} - P(C_a)
+C_{r,w} = C_{r,d} - P(C_a)
 \end{equation}
 
-Where $P(C_a)$ represents the penalty, which scales according to the amount of $C_r$ originally deposited.
+Where $P(C_a)$ represents the penalty, which scales according to the amount of $C_r$ originally deposited, \(d\).
 The penalty mechanism incentivizes holding $C_a$ longer, as the remaining holders benefit from these penalties.
 
-\subsection{Anticoin Pricing and Pegging Mechanism}
-At the time of vault creation, the protocol records the current price of the underlying rugged token $C_r$. This price is used as a reference for all future transactions involving $C_a$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Supply Regulation Mechanism}
+The protocol regulates the supply of the native Rugsafe token $R$ based on the total value of all rugged tokens $C_r$ in existence.
+The supply of the Rugsafe token is inversely related to the sum of the values of these rugged tokens, adjusted logarithmically:
 
 \begin{equation}
-\text{Price}_{C_a} \propto \frac{1}{\text{Price}_{C_r}}
+R_\text{supply}  \propto \frac{1}{\log\left(\sum C_r\right)}
 \end{equation}
 
-As the price of $C_r$ fluctuates, the value of $C_a$ adjusts inversely, similar to an algorithmic stablecoin mechanism. This ensures that $C_a$ holders are protected against the devaluation of $C_r$.
+This mechanism ensures that as more tokens are rugged, the supply of $R$ becomes increasingly scarce, potentially enhancing its value and stability within the ecosystem.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{images/2.png}
-\caption{The inverse logarithmic relationship between the price of the underlying rugged token $C_r$ and the amount of minted anticoins $C_a$.
-As the price of $C_r$ decreases, the amount of minted $C_a$ increases, providing stability and protection for holders.}
+\includegraphics[width=\textwidth]{images/5.png}
+\caption{The logarithmic relationship between the theoretical supply of Rugsafe tokens $R$ and the sum of rugged token values $\sum C_r$.
+This relationship underscores how the supply of $R$ is regulated based on the value of rugged tokens in existence, ensuring stability and scarcity.}
 \label{fig:minted_anticoins}
@@
 
+In addition to this scarcity mechanism, the native chain introduces emissions of Rugsafe tokens $R$ per block produced, as it operates on the Cosmos SDK framework.
+This implies that the total supply of $R$ is influenced by two opposing forces: the burning of tokens $R_\beta$ and the minting of new tokens $R_\texttt{mint}$ through block emissions.
+
+The rate of token burning is governed by the inverse relationship with the total value of rugged tokens $C_r$ in existence:
+
+\[
+R_{\beta} \propto \frac{1}{\log\left(\sum R_{C_v}\right)}
+\]
+
+Simultaneously, the protocol continuously mints new tokens at a rate proportional to the number of blocks produced:
+
+\[
+R_{\texttt{mint}} = \epsilon \times b
+\]
+
+where $\text{emission\_rate}$ is a parameter that determines the number of Rugsafe tokens emitted per block.
+
+The net change in the supply of Rugsafe tokens $R_\text{net}$ over time is the difference between the tokens minted and burned:
+
+\[
+R_{\text{net}} = R_{\epsilon} - R_{\beta}
+\]
+
+Both the burn rate $R_{\beta}$ and the emission rate per block $R_\epsilon$ are parameterized and can be adjusted through community governance:
+
+\[
+R_\beta = f\left(\frac{1}{\log\left(\sum R_{C_v}\right)}, \beta_{\texttt{burn}}\right)
+\]
+
+and to calculate the amount minted, we can take the emission rate per block, multiplied by the amount of blocks considered,
+
+\[
+R_{\beta} = g(\epsilon, \text{blocks})
+\]
+
+This flexibility allows the community to respond to changing market conditions and fine-tune the protocol to achieve the desired balance between token scarcity and availability.
+By giving the community control over these parameters, the protocol ensures that it can adapt over time, maintaining the health and stability of the Rugsafe ecosystem.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Anticoin Role and Market Interaction}
+At the time of vault creation, the protocol mints $C_a$ tokens in a 1:1 ratio with the deposited rugged tokens $C_r$.
+These $C_a$ tokens serve as a clean, fungible representation of the rugged tokens, providing users with a new asset that can be freely traded or held.
+The value of $C_a$ tokens is determined entirely by market forces, \(m_f\), allowing the broader ecosystem to establish their worth relative to other assets.
+
+The $C_a$ tokens function purely as receipts for the deposited rugged tokens and do not undergo any price adjustments or pegging mechanisms.
+This approach ensures that the protocol remains simple and transparent, with the market dictating the value of $C_a$ based on supply and demand dynamics.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%
+
+\subsection{User Interaction and Ecosystem Signaling}
+When users deposit rugged tokens $C_r$ into a vault $V_c$, they receive $C_a$ tokens as a direct and clean representation of their deposited rugged tokens.
+The relationship between the deposited tokens and the minted $C_a$ tokens is given by:
+
+\[
+C_a = C_r
+\]
+
+These $C_a$ tokens function as receipts, representing the ownership and claim on the underlying rugged tokens.
+The $C_a$ tokens are fungible and can be freely used within the ecosystem, whether for trading, holding, or as collateral in other DeFi applications.
+The presence of $C_a$ tokens within the market serves as a signal that the user has deposited rugged tokens into the protocol, effectively transforming $C_r$ into a new, market-driven asset.
+
+The market value of $C_a$ tokens is influenced by several factors, including:
+
+1. \textbf{Market Supply and Demand}: The value of $C_a$ tokens, $P_{C_a}$, is determined by the market, where supply and demand dynamics play a crucial role:
+
+\[
+P_{C_a} = f(S_{C_a}, D_{C_a})
+\]
+
+As the demand for $C_a$ tokens increases relative to their supply, the market value $P_{C_a}$ will rise, and vice versa.
+
+2.
+\textbf{Underlying Value of Rugged Tokens}: The value of $C_a$ tokens is also indirectly linked to the perceived value of the underlying rugged tokens $C_r$.
+If the market expects that the rugged tokens $C_r$ might regain value in the future, the value of $C_a$ could increase accordingly:
+
+\[
+P_{C_a} \propto E(P_{C_r})
+\]
+
+where $E(P_{C_r})$ is the expected future value of the rugged tokens.
+
+3.
+\textbf{Liquidity and Utility}: The utility of $C_a$ tokens within the ecosystem—such as their use as collateral, in trading pairs, or in yield farming—contributes to their liquidity and market value.
+The more integrated and useful $C_a$ tokens are within the DeFi space, the higher their market value:
+
+\[
+P_{C_a} = g(U_{C_a}, L_{C_a})
+\]
+
+The protocol does not enforce any actions related to burning or altering the supply of $C_a$ tokens.
+Instead, the focus is on providing a straightforward receipt mechanism that empowers users to manage their assets independently within the ecosystem.
+This means that $C_a$ tokens remain purely market-driven assets, with their value being dictated by market conditions and the broader DeFi ecosystem.
+
+Users may choose to hold $C_a$ tokens, anticipating a rise in value due to market demand or the recovery of the underlying rugged tokens.
+Alternatively, they might trade or leverage $C_a$ in other DeFi applications, thereby influencing its liquidity and market presence.
+
+This design choice simplifies the user experience while maintaining the integrity and transparency of the protocol.
+The absence of enforced mechanisms like burning or minting ensures that the value of $C_a$ tokens is wholly determined by the market, reflecting real-time supply and demand conditions within the ecosystem.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Opportunities for New Ecosystems}
+The Rugsafe protocol's structure introduces significant opportunities for developers and communities associated with rugged tokens $C_r$.
+Each rugged token $C_r$ represents an ecosystem that anticipated a specific offering or vision to materialize within the market.
+The issuance of $C_a$ tokens as a clean, fungible representation of $C_r$ provides these communities with a renewed opportunity to realize their original goals.
+
+By depositing rugged tokens $C_r$ into a vault $V_c$, the protocol mints $C_a$ tokens in a 1:1 ratio:
+
+\[
+C_a = C_r
+\]
+
+These $C_a$ tokens, backed by provable deposits of the original underlying rugged tokens, allow communities to reintroduce their vision to the market under new terms.
+The $C_a$ tokens can be traded, utilized as collateral, or integrated into new decentralized finance (DeFi) applications, thereby reviving the ecosystem that was initially disrupted.
+
+The presence of $C_a$ tokens in the market not only provides a second chance for these communities but also creates new financial products and services tailored to support the specific needs of rug pull victims.
+Developers can leverage this mechanism to build applications that cater to these communities, effectively transforming $C_r$ from a symbol of loss into a foundation for new economic activity.
+
+Quantifying the impact, if $N$ is the total number of rugged tokens and $M$ represents the market value of each token, the introduction of $C_a$ creates a new market potential:
+
+\[
+\text{Market Potential} = \sum_{i=1}^{N} M_i \cdot C_{a,i}
+\]
+
+This market potential signifies the total value that can be recaptured or reintroduced into the ecosystem through $C_a$ tokens, providing a substantial incentive for developers and communities to participate in the Rugsafe protocol.
+The resulting ecosystem could not only restore lost value but also innovate new financial instruments and services, revitalizing the original vision of the rugged projects.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{User Commitment and Signal to the Ecosystem}
-Depositing $C_r$ into a vault $V_c$ and receiving $C_a$ signals the user's belief that $C_r$ is a rugged token.
-To further reinforce this belief, users can burn their $C_a$ tokens, effectively removing them from circulation and indicating their strong commitment to the protocol's mission.
 
-\begin{equation}
-\text{Signal} = \text{Burn}(C_a)
-\end{equation}
+Depositing $C_r$ into a vault $V_c$ and receiving $C_a$ tokens signals the user's belief that $C_r$ is a rugged token.
+This action converts the rugged tokens into a new, clean representation within the ecosystem.
+To demonstrate a stronger commitment to the protocol, users can choose to burn their $C_a$ tokens, effectively removing them from circulation.
+This act of burning is a significant signal within the ecosystem.
 
-This burning mechanism enhances the credibility of the user's claim that $C_r$ is a rugged token and provides additional confidence to other participants in the ecosystem.
+The burning process can be represented as:
 
-\subsection{Opportunities for New Developments}
-The Rugsafe protocol's structure opens up opportunities for developers to build applications that cater to the needs of rug pull victims.
-By establishing a market for anticoin tokens $C_a$, new financial products and services can be developed to support users who have suffered losses from rug pulls.
+\[
+\text{Signal} = \texttt{Burn}(C_a)
+\]
+
+Mathematically, the burning mechanism reduces the circulating supply of $C_a$ tokens, which can be expressed as:
+
+\[
+C_a' = C_a - B_{C_a}
+\]
+
+where \(C_a'\) is the circulating supply of $C_a$ after the burn, and \(B_{C_a}\) is the quantity of $C_a$ tokens burned.
+
+This reduction in supply impacts the overall market dynamics and is reflected in the inverse relationship between the value of the Rugsafe token $R$ and the volume of rugged tokens $C_r$:
+
+\[
+R_\text{supply}  \propto \frac{1}{\log\left(\sum C_r \right)}
+\]
+
+The act of burning $C_a$ tokens strengthens this relationship by increasing the scarcity of $C_a$ and consequently affecting the value of $R$.
+The more $C_a$ is burned, the greater the signal of commitment to the protocol, potentially leading to a stronger inverse correlation between the value of $R$ and the total rugged tokens $C_r$.
+
+\[
+\frac{\partial R}{\partial C_a} < 0
+\]
+
+This partial derivative indicates that as the circulating supply of $C_a$ decreases (through burning), the value of $R$ is expected to increase, further solidifying the protocol's stability and the commitment of its participants.
+
+%% could be problematic
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Rugsafe Vaults as Oracles}
+Rugsafe vaults act as decentralized oracles, providing reliable data on the existence and volume of rugged tokens.
+This oracle functionality enables the protocol to adjust the supply of $R$ accurately and in real-time, based on the real-world data collected from the vaults.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%
 
 \subsection{Whale Penalty Mechanism}
-To prevent large holders (whales) from gaming the system, the penalty for withdrawing $C_r$ scales with the amount of $C_a$ held.
-Inspired by quadratic voting schemes, the penalty increases progressively as the whale's holdings increase, ensuring fairness and preventing manipulation.
+To prevent large holders (whales) from gaming the system, the penalty for withdrawing rugged tokens $C_r$ scales with the amount of $C_a$ held.
+This mechanism is inspired by quadratic voting schemes, where the penalty increases progressively as the holder's balance of $C_a$ tokens grows, ensuring fairness and preventing manipulation.
 
-\begin{equation}
-P(C_a) \propto \left(\text{Holdings}\right)^\lambda
-\end{equation}
+The penalty $P(C_a)$ for withdrawing rugged tokens is mathematically represented as:
 
-Where $\lambda > 1$ is a scaling factor that ensures the penalty increases non-linearly with the amount of $C_a$ held.
-This scaling penalty ensures that the system remains equitable and prevents disproportionate influence by large holders.
+\[
+P(C_a) \propto \left(H_{C_a}\right)^\lambda
+\]
+
+where $\lambda > 1$ is a scaling factor that ensures the penalty increases non-linearly with the amount of $C_a$ held.
+
+\subsubsection{Impact on Regular Users vs. Whales}
+
+For regular users, who typically hold smaller amounts of $C_a$, the penalty remains relatively low, as the function’s exponent $\lambda$ ensures that the penalty grows slowly with their holdings:
+
+\[
+P_{\text{regular}}(C_a) = k \cdot \left(H_{C_a}\right)^\lambda \quad \text{with} \quad \lambda > 1 \quad \text{and} \quad H_{C_a} \text{ small}
+\]
+
+where $k$ is a proportionality constant.
+For these users, the impact of the penalty is minimal, allowing them to interact with the protocol without significant costs, thus promoting fairness and inclusivity.
+
+For whales, however, the penalty increases significantly due to their large holdings of $C_a$. As the amount of $C_a$ held by a whale increases, the penalty grows more steeply:
+
+\[
+P_{\text{whale}}(C_a) = k \cdot \left(H_{C_a}\right)^\lambda \quad \text{with} \quad \lambda > 1 \quad \text{and} \quad H_{C_a} \text{ large}
+\]
+
+This non-linear increase in penalty serves two purposes.
+First, it deters whales from attempting to manipulate the system by accumulating and withdrawing large amounts of $C_r$.
+Second, it ensures that whales, who may also be regular users of the protocol, are subject to the same rules but with penalties that reflect their larger influence on the system.
+
+\subsubsection{Equitable System Design}
+
+By scaling the penalty non-linearly with the amount of $C_a$ held, as in figure \ref{fig:whale_penalty}, the system remains equitable for all users, regardless of their holdings.
+Regular users are protected from disproportionate penalties, while whales, whose actions could have a more significant impact on the system, face penalties commensurate with their holdings.
+This design discourages potential manipulation by large holders and promotes a more balanced and fair ecosystem for all participants.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/6.png}
+\caption{The impact of the whale penalty mechanism based on varying scaling factors $\lambda$.
+As $\lambda$ increases, the penalty for holding larger amounts of $C_a$ grows exponentially, particularly affecting whales with significant holdings.}
+\label{fig:whale_penalty}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Rugsafe Token Emissions and Parameterized Rewards Mechanism}
+
+The Rugsafe protocol introduces a mechanism that incentivizes users to deposit rugged tokens $C_r$ into vaults $V_c$ by providing rewards in the form of Rugsafe tokens $R$.
+These vaults, serving as oracles, verify the deposits of specific rugged tokens and trigger emissions of Rugsafe tokens on the main chain.
+
+In addition to receiving $C_a$, the user is rewarded with an airdrop of Rugsafe tokens $R$ on the main chain.
+The reward amount, $R_{\omega}$, for depositing rugged tokens is parameterized at the time of vault creation and is expressed as a function of the value of the deposit:
+
+\[
+R_{\omega} = f(C_r, \omega)
+\]
+
+where $\omega$ is a parameter set during vault creation that determines the emission rate tied to the value of the deposited tokens.
+
+Furthermore, the protocol introduces a greater incentive for users who choose to burn their $C_a$ tokens, thereby signaling that they do not intend to redeem their underlying rugged tokens.
+The reward amount for burning, $R_{\texttt{burn}}$, is also parameterized at vault creation and is given by:
+
+\[
+R_{\texttt{burn}} = g(C_a, \theta) \quad \text{with} \quad g(C_a, \theta) > f(C_r, \omega)
+\]
+
+where $\theta$ is a parameter that sets a higher emission rate for burning $C_a$, indicating a permanent withdrawal of the rugged tokens from circulation.
+
+Both the deposit and burn reward rates are flexible and can be tailored to the specific needs of the vault or community at the time of creation.
+This parameterization allows for customization of the incentives to align with the objectives of the protocol and the specific rugged token ecosystem.
+
+This mechanism ensures that users are rewarded for contributing to the stability and security of the Rugsafe ecosystem.
+By depositing $C_r$ into vaults and potentially burning $C_a$, users receive Rugsafe tokens, fostering further participation and engagement in the protocol.
+The difference in reward levels between depositing and burning reflects the varying degrees of commitment to the ecosystem, with greater rewards for those who choose to fully transition away from their rugged tokens.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Rugproof Mechanism}
+
+The Rugsafe chain introduces a novel mechanism that allows users to mint new assets directly on the chain, with the assurance that these assets are rugproof by default.
+This mechanism is designed to protect users from potential rug pulls by leveraging a bonding system and a community-driven challenge process.
+
+\subsubsection{Token Issuance and Bonding Mechanism}
+
+At the time of token issuance, the issuer is required to put up a nontrivial percentage \(x\%\) of the total issued tokens as a bond:
+
+\[
+\beta_{\text{issuer}} = x\% \times T_I
+\]
+
+This bond acts as collateral, ensuring that the issuer has a stake in the integrity of the project. The bond is held in escrow and serves as a safeguard against potential rug pulls.
+
+\subsubsection{Claim and Challenge Process}
+
+At any point in time, any user can submit a claim against the token issuer, asserting that the project is being rugged.
+To submit a claim, the user must also put up a bond, \(\beta_{\text{claim}}\), as a guarantee of their claim:
+
+\[
+\beta_{\text{claim}} = y\% \times T_I
+\]
+
+where \(y\%\) is a parameter that may vary depending on the perceived risk or the specifics of the token.
+
+Upon submitting a claim, a challenge period begins, during which other users can vote on whether the project is indeed rugging.
+Each vote requires a deposit, \(\delta_{\text{vote}}\), which can be chosen by the voter, though it may be smaller than the claim bond:
+
+\[
+\delta_{\text{vote}} \geq z
+\]
+
+where \(z\) is a minimum deposit amount set by the protocol.
+
+\subsubsection{Outcome of the Challenge Period}
+
+At the conclusion of the challenge period, the following outcomes are possible:
+
+1.
+\textbf{Project Found to Be Rugging}: If the project is found to be rugging, the issuer's bond is slashed by a parameterized percentage, \(\alpha\%\), and distributed among all token holders, excluding the issuer:
+
+\[
+\beta_{\text{slashed}} = \alpha\% \times \beta_{\text{issuer}}
+\]
+
+The user who successfully claimed the rug pull receives a larger portion of the slashed bond, with the remaining amount distributed among the users who supported the claim.
+
+2.
+\textbf{Claim Found to Be Fraudulent}: If the claim is found to be fraudulent, the claim bond is slashed by a parameterized percentage, \(\gamma\%\), and distributed to those who voted against the claim:
+
+\[
+\beta_{\text{slashed}_{\text{claim}}} = \gamma\% \times \beta_{\text{claim}}
+\]
+
+This process discourages false claims and encourages honest participation in the challenge process.
+
+\subsubsection{Incentives and Protection}
+
+This mechanism incentivizes users to carefully consider their actions when minting new assets and making claims.
+The initial bond posted by the issuer serves as a deterrent against rug pulls, while the challenge process allows the community to actively monitor and vote on the integrity of the project.
+By requiring bonds for claims and votes, the protocol ensures that participants have a stake in the outcome, reducing the likelihood of frivolous claims or votes.
+
+By implementing this mechanism, the Rugsafe chain offers a robust, community-driven solution to protect users from potential rug pulls before they occur.
+This not only enhances the security of the ecosystem but also empowers users to take an active role in maintaining the integrity of the projects they support.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%% rugproof mechanism
 

### 2024-08-31 hello_world/rugsafe/paper/images/py4.py

@@ -1,0 +1,23 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Define a common style for all plots
+plt.style.use('dark_background')
+
+# Plot 1: Supply Regulation Plot
+rugged_token_values = np.linspace(1, 1000, 500)
+rugsafe_price = 1 / np.log(rugged_token_values)
+rugsafe_supply = 1 / rugsafe_price
+
+plt.figure(figsize=(10, 6))
+plt.plot(rugged_token_values, rugsafe_supply, color='cyan', label=r'Theoretical Supply of Rugsafe Tokens $R$')
+plt.xlabel(r'Sum of Rugged Token Values $\sum R_{C_v}$', color='white')
+plt.ylabel('Theoretical Supply of Rugsafe Tokens $R$', color='white')
+plt.title('Theoretical Supply of Rugsafe Tokens vs. Total Rugged Tokens', color='white')
+plt.grid(True, color='gray')
+plt.legend()
+plt.tick_params(axis='x', colors='white')
+plt.tick_params(axis='y', colors='white')
+plt.legend(facecolor='black', edgecolor='white')
+plt.show()
+

### 2024-08-31 hello_world/rugsafe/paper/images/py6.py

@@ -1,0 +1,38 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Define time and parameters for emission and burn rates
+time = np.linspace(1, 100, 500)  # Start from 1 to avoid log(0)
+emission_rate = 10
+burn_rate = 2
+
+# Calculate the emission and burn values separately
+emission = emission_rate * time
+burn = burn_rate * np.log(time)
+
+# Plotting the emission component
+plt.figure(figsize=(10, 6))
+plt.plot(time, emission, color='cyan', label='Emission')
+plt.xlabel('Time', color='white')
+plt.ylabel('Emission', color='white')
+plt.title('Rugsafe Token Emission Over Time', color='white')
+plt.grid(True, color='gray')
+plt.legend()
+plt.tick_params(axis='x', colors='white')
+plt.tick_params(axis='y', colors='white')
+plt.legend(facecolor='black', edgecolor='white')
+plt.show()
+
+# Plotting the burn component
+plt.figure(figsize=(10, 6))
+plt.plot(time, burn, color='red', label='Burn')
+plt.xlabel('Time', color='white')
+plt.ylabel('Burn', color='white')
+plt.title('Rugsafe Token Burn Over Time', color='white')
+plt.grid(True, color='gray')
+plt.legend()
+plt.tick_params(axis='x', colors='white')
+plt.tick_params(axis='y', colors='white')
+plt.legend(facecolor='black', edgecolor='white')
+plt.show()
+

### 2024-08-31 hello_world/src/processor.rs

@@ -732,11 +732,16 @@ impl Processor {
         let account_info_iter = &mut accounts.iter();
 
         let payer_account = next_account_info(account_info_iter)?;
+
         let user_token_account = next_account_info(account_info_iter)?;
         let mint_account = next_account_info(account_info_iter)?;
+        // let user_token_account = get_associated_token_address(&payer_account.key, &mint_account.key);
         let spl_account = next_account_info(account_info_iter)?;
         let rent_account = next_account_info(account_info_iter)?;
         let system_program = next_account_info(account_info_iter)?;
+
+        let expected_user_token_pubkey =
+            get_associated_token_address(payer_account.key, mint_account.key);
 
         // Derive the PDA for the mint account
         let (expected_mint_pubkey, bump_seed) =
@@ -745,10 +750,10 @@ impl Processor {
         msg!("expected_mint_pubkey: {}", expected_mint_pubkey);
         msg!("comparing it to: {}", mint_account.key);
         // Ensure the derived mint address matches the passed mint account
-        if *mint_account.key != expected_mint_pubkey {
-            msg!("Error: Invalid mint account passed");
-            return Err(ProgramError::InvalidArgument);
-        }
+        // if *mint_account.key != expected_mint_pubkey {
+        //     msg!("Error: Invalid mint account passed");
+        //     return Err(ProgramError::InvalidArgument);
+        // }
 
         // Ensure the payer is a signer
         msg!("payer_account.is_signer: {}", payer_account.is_signer);
@@ -797,44 +802,29 @@ impl Processor {
             )?;
         }
 
-        // Check if the user token account needs to be created and initialized
+        // Ensure the user token account is created and initialized
         if user_token_account.data_is_empty() {
-            let rent = Rent::get()?;
-            let required_lamports = rent.minimum_balance(TokenAccount::LEN);
-
-            msg!("3");
-
-            // Create the user token account
             invoke(
-                &solana_program::system_instruction::create_account(
+                &spl_associated_token_account::instruction::create_associated_token_account(
                     payer_account.key,
-                    user_token_account.key,
-                    required_lamports,
-                    TokenAccount::LEN as u64,
+                    payer_account.key,
+                    mint_account.key,
                     spl_account.key,
                 ),
                 &[
                     payer_account.clone(),
                     user_token_account.clone(),
-                    system_program.clone(),
-                ],
-            )?;
-
-            msg!("4");
-
-            invoke(
-                &spl_token::instruction::initialize_account(
[…]

### 2024-08-31 hello_world/tests/test.rs

@@ -914,7 +914,8 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
 
     //////////////////////////////
     // Create user token account keypair
-    let user_token_keypair: Keypair = Keypair::new();
+    // let user_token_keypair: Keypair = Keypair::new();
+    let user_token_account = get_associated_token_address(&payer.pubkey(), &mint_pubkey);
 
     // Prepare the faucet instruction
     let amount: u64 = 1000;
@@ -925,7 +926,10 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
         program_id,
         accounts: vec![
             AccountMeta::new(payer.pubkey(), true),
-            AccountMeta::new(user_token_keypair.pubkey(), true),
+            //
+            // AccountMeta::new(user_token_keypair.pubkey(), true),
+            AccountMeta::new(user_token_account, false),
+            //
             AccountMeta::new(mint_pubkey, false), // Use derived mint pubkey
             AccountMeta::new_readonly(spl_token::id(), false),
             AccountMeta::new_readonly(solana_program::sysvar::rent::ID, false),
@@ -938,10 +942,11 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
     let faucet_tx = Transaction::new_signed_with_payer(
         &[faucet_ix],
         Some(&payer.pubkey()),
-        &[&payer, &user_token_keypair], // No mint keypair, backend handles mint creation
         // &[&payer, &mint_keypair, &user_token_keypair],
         // &[&payer, mint_pubkey],
         // &[&payer],
+        // &[&payer, &user_token_keypair], // No mint keypair, backend handles mint creation
+        &[&payer],
         recent_blockhash,
     );
     banks_client.process_transaction(faucet_tx).await?;
@@ -949,7 +954,8 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
     // Verify the user token account balance
     println!("Verifying user token account balance...");
     let user_token_account = banks_client
-        .get_account(user_token_keypair.pubkey())
+        // .get_account(user_token_keypair.pubkey())
+        .get_account(user_token_account)
         .await?
         .expect("user_token_account not found");
 

### 2024-09-01 hello_world/rugsafe/paper/paper.tex
updated paper

@@
 
-\title{Rugsafe: A Protocol for Protecting Digital Assets from Rug Pulls}
+\title{Rugsafe: A Multichain Vault Protocol for Defending Against Rug Pulls}
 \author{info@rugsafe.org}
-\date{v0.0.1 August 1, 2024}
+\date{v0.0.1 September 1, 2024}
 
@@
 
-%\begin{abstract}
-%Rugsafe introduces a novel protocol designed to mitigate the risks associated with rug pulls in decentralized finance (DeFi).
-By leveraging cryptographic primitives and economic incentives, Rugsafe provides a framework that ensures the security and recoverability of assets when fraudulent activities are detected.
-The protocol is built around the concept of vaults for rugged tokens, issuance of anticoin tokens, and an incentive mechanism that penalizes and rewards users based on their interaction with the system.
-Rugsafe integrates seamlessly with existing DeFi platforms, offering an additional layer of security without compromising the decentralization principles.
-%\end{abstract}
-
 \begin{abstract}
-Rugsafe introduces a novel protocol designed to mitigate the risks associated with rug pulls in decentralized finance (DeFi).
-By leveraging cryptographic primitives and economic incentives, Rugsafe provides a framework that ensures the security and recoverability of assets when fraudulent activities are detected.
-The protocol revolves around the concept of vaults for rugged tokens, issuance of anticoin tokens as receipts, and a mechanism that regulates the supply of the native Rugsafe token in response to the volume of rugged tokens.
-Rugsafe integrates seamlessly with existing DeFi platforms, offering an additional layer of security without compromising the decentralization principles.
+Rugsafe introduces a comprehensive protocol aimed at mitigating the risks of rug pulls in the cryptocurrency ecosystem.
+By utilizing cryptographic security measures and economic incentives, the protocol provides a secure multichain system for recovering assets and transforming rugged tokens into opportunities and rewards.
+Foundational to Rugsafe are specialized vaults where rugged tokens can be securely deposited, and anticoin tokens are issued as receipts.
+Users can utilize these anticoins within the ecosystem or choose to burn them, further securing the protocol and earning additional rewards.
+The supply of the native Rugsafe token is dynamically adjusted based on the volume, value, and activity of rugged tokens, ensuring stability and resilience.
+By depositing rugged tokens into a vault on several chains, and by burning anticoins, users receive incentives on the RugSafe chain.
+This protocol's vaults are designed to work in heterogenous blockchain ecosystems, offering a practical and effective solution to one of the most significant challenges in the cryptocurrency market.
 \end{abstract}
@@
 \section{Closing Remarks}
-Rugsafe presents a robust mathematical framework designed to protect against rug pulls in the DeFi space.
-By combining vault mechanisms, anticoin issuance, and incentive structures, it ensures a secure environment for digital asset management.
-The protocol's design not only protects users but also opens up new avenues for development and innovation in the DeFi ecosystem.
+The prevalence of rug pulls represents one of the most pressing threats to the integrity and trust in the cryptocurrency ecosystem.
+Rugsafe is committed to addressing this challenge by leveraging advanced technology and innovative mechanisms to protect users from rug pulls.
+By providing a secure framework for asset recovery and offering tools that prevent malicious activity, Rugsafe seeks to eliminate one of the largest sources of financial loss in the industry.
+Rugsafe’s mission is to transform vulnerabilities into resilience, ensuring that digital assets are protected and confidence in the market is restored.
 

### 2024-09-01 hello_world/rugsafe/paper/paper.tex
faucet fixed

@@
 
-%\tableofcontents
+\tableofcontents
 
@@
 To prevent large holders (whales) from gaming the system, the penalty for withdrawing rugged tokens $C_r$ scales with the amount of $C_a$ held.
-This mechanism is inspired by quadratic voting schemes, where the penalty increases progressively as the holder's balance of $C_a$ tokens grows, ensuring fairness and preventing manipulation.
-
+this mechanism is inspired by quadratic voting schemes, where the penalty increases progressively as the holder's balance of $C_a$ tokens grows, ensuring fairness and preventing manipulation.
 The penalty $P(C_a)$ for withdrawing rugged tokens is mathematically represented as:
@@
 
-\subsubsection{Impact on Regular Users vs. Whales}
+\subsubsection{Impact on regular users vs. whales}
 
-For regular users, who typically hold smaller amounts of $C_a$, the penalty remains relatively low, as the function’s exponent $\lambda$ ensures that the penalty grows slowly with their holdings:
+for regular users, who typically hold smaller amounts of $C_a$, the penalty remains relatively low, as the function’s exponent $\lambda$ ensures that the penalty grows slowly with their holdings:
 
@@
 
-where $k$ is a proportionality constant.
-For these users, the impact of the penalty is minimal, allowing them to interact with the protocol without significant costs, thus promoting fairness and inclusivity.
+Where $k$ is a proportionality constant.
+for these users, the impact of the penalty is minimal, allowing them to interact with the protocol without significant costs, thus promoting fairness and inclusivity.
 
-For whales, however, the penalty increases significantly due to their large holdings of $C_a$. As the amount of $C_a$ held by a whale increases, the penalty grows more steeply:
+For whales, however, the penalty increases significantly due to their large holdings of $C_a$. as the amount of $C_a$ held by a whale increases, the penalty grows more steeply:
 
@@
 This non-linear increase in penalty serves two purposes.
-First, it deters whales from attempting to manipulate the system by accumulating and withdrawing large amounts of $C_r$.
-Second, it ensures that whales, who may also be regular users of the protocol, are subject to the same rules but with penalties that reflect their larger influence on the system.
+first, it deters whales from attempting to manipulate the system by accumulating and withdrawing large amounts of $C_r$.
+second, it ensures that whales, who may also be regular users of the protocol, are subject to the same rules but with penalties that reflect their larger influence on the system.
 
-\subsubsection{Equitable System Design}
-
-By scaling the penalty non-linearly with the amount of $C_a$ held, as in figure \ref{fig:whale_penalty}, the system remains equitable for all users, regardless of their holdings.
-Regular users are protected from disproportionate penalties, while whales, whose actions could have a more significant impact on the system, face penalties commensurate with their holdings.
-This design discourages potential manipulation by large holders and promotes a more balanced and fair ecosystem for all participants.
+\subsubsection{equitable system design}
 
@@
 \includegraphics[width=\textwidth]{images/6.png}
-\caption{The impact of the whale penalty mechanism based on varying scaling factors $\lambda$.
-As $\lambda$ increases, the penalty for holding larger amounts of $C_a$ grows exponentially, particularly affecting whales with significant holdings.}
+\caption{the impact of the whale penalty mechanism based on varying scaling factors $\lambda$.
+as $\lambda$ increases, the penalty for holding larger amounts of $C_a$ grows exponentially, particularly affecting whales with significant holdings.}
 \label{fig:whale_penalty}
 \end{figure}
+
+By scaling the penalty non-linearly with the amount of $C_a$ held, as in figure \ref{fig:whale_penalty}, the system remains equitable for all users, regardless of their holdings.
+regular users are protected from disproportionate penalties, while whales, whose actions could have a more significant impact on the system, face penalties commensurate with their holdings.
+this design discourages potential manipulation by large holders and promotes a more balanced and fair ecosystem for all participants.
+
+\subsubsection{cumulative penalty mechanism}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/9.png}
+\caption{the impact of the cumulative penalty mechanism on sybil attack attempts.
+the more accounts a whale creates to split their holdings, the higher the cumulative penalty becomes, discouraging such behavior.}
+\label{fig:cumulative_penalty}
+\end{figure}
+
+To further enhance the protocol's defense against potential sybil attacks, a cumulative penalty mechanism has been introduced.
+this mechanism accumulates penalties progressively with each withdrawal attempt, particularly when a whale attempts to split their holdings across multiple accounts to evade higher penalties.
+
+In this approach, the cumulative penalty is applied on a per-account basis but is aggregated across all related accounts.
+as illustrated in figure \ref{fig:cumulative_penalty}, the more accounts a whale creates to distribute their holdings, the more significant the overall penalty becomes.
+this cumulative effect discourages sybil attacks by ensuring that the total penalty incurred across all accounts exceeds what would have been paid if the whale had used a single account.
+
+This combined system of both the original non-linear penalty and the cumulative penalty ensures that whales are doubly incentivized to avoid manipulative behaviors.
+they face increasing penalties for holding large amounts of $C_a$ and additional cumulative penalties if they attempt to circumvent the system through sybil attacks.
 

### 2024-09-01 hello_world/src/processor.rs

@@ -740,6 +740,8 @@ impl Processor {
         let rent_account = next_account_info(account_info_iter)?;
         let system_program = next_account_info(account_info_iter)?;
 
+        let associated_token_program = next_account_info(account_info_iter)?; // System program account
+
         let expected_user_token_pubkey =
             get_associated_token_address(payer_account.key, mint_account.key);
 
@@ -783,7 +785,7 @@ impl Processor {
                 &[&[b"mint".as_ref(), &[bump_seed]]],
             )?;
 
-            // msg!("2");
+            msg!("2");
 
             // // Initialize the mint account
             invoke(
@@ -797,10 +799,12 @@ impl Processor {
                 &[
                     mint_account.clone(),
                     rent_account.clone(),
-                    // payer_account.clone(),
+                    payer_account.clone(),
                 ],
             )?;
         }
+
+        msg!("3");
 
         // Ensure the user token account is created and initialized
         if user_token_account.data_is_empty() {
@@ -825,6 +829,15 @@ impl Processor {
                     // mint_account_token_a.clone(), // Token mint address
                     // system_program.clone(),       // System program
                     // spl_account.clone(),
+                    /*
+                    payer_account.clone(),        // Funding account
+                    vault_account.clone(),        // Associated token account
+                    payer_account.clone(),        // Wallet address
+                    mint_account_token_a.clone(), // Token mint address
+                    system_program.clone(),       // System program
+                    // NOTE: spl or associated
+                    spl_account.clone(),
+                    */
                 ],
             )?;
         }

### 2024-09-01 hello_world/tests/test.rs

@@ -78,7 +78,7 @@ async fn test_create_vault() -> Result<(), TransportError> {
 
     let rent_key = solana_program::sysvar::rent::ID;
     let spl_key = spl_token::id();
-    let associated_token_program = spl_associated_token_account::id();
+    let associated_token_program: Pubkey = spl_associated_token_account::id();
 
     // let state_keypair = Keypair::new(); // State account
 
@@ -917,6 +917,8 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
     // let user_token_keypair: Keypair = Keypair::new();
     let user_token_account = get_associated_token_address(&payer.pubkey(), &mint_pubkey);
 
+    let associated_token_program: Pubkey = spl_associated_token_account::id();
+
     // Prepare the faucet instruction
     let amount: u64 = 1000;
     let mut data = vec![4]; // Instruction ID
@@ -934,6 +936,7 @@ async fn test_faucet() -> Result<(), Box<dyn std::error::Error>> {
             AccountMeta::new_readonly(spl_token::id(), false),
             AccountMeta::new_readonly(solana_program::sysvar::rent::ID, false),
             AccountMeta::new_readonly(solana_program::system_program::id(), false),
+            AccountMeta::new(spl_associated_token_account::id(), false),
         ],
         data, // Construct data manually here
     };

### 2024-09-02 hello_world/src/processor.rs
faucet, vault creation, and deposit works finally in ui

@@ -13,6 +13,7 @@ use solana_program::{
     sysvar::rent::Rent,
 };
 use spl_associated_token_account::get_associated_token_address;
+// use spl_associated_token_account::instruction::create_associated_token_account;
 use spl_associated_token_account::{self, instruction};
 
 // use solana_sdk::program::invoke_signed;
@@ -94,6 +95,8 @@ impl Processor {
         }
 
         let associated_token_program = next_account_info(account_info_iter)?;
+        let user_token_a_account = next_account_info(account_info_iter)?;
+        let program_id_account = next_account_info(account_info_iter)?;
 
         // msg!("Creating vault...");
         msg!("payer account key: {:?}", payer_account.key);
@@ -105,7 +108,8 @@ impl Processor {
         msg!("Vault account key: {:?}", vault_account.key);
         msg!("Rent account key: {:?}", rent_account.key);
         msg!("State account key: {:?}", state_account.key);
-        msg!("SPL: {}", spl_token::id());
+        msg!("SPL: {}", spl_account.key);
+        msg!("user_token_a_account: {}", user_token_a_account.key);
 
         // NOTE: two mint types
         // msg!("Mint account balance: {:?}", mint_account.lamports());
@@ -125,6 +129,10 @@ impl Processor {
         msg!(
             "associated token account balance: {:?}",
             associated_token_program.lamports()
+        );
+        msg!(
+            "user token a account: {:?}",
+            user_token_a_account.lamports()
         );
 
         msg!("state account balance: {:?}", state_account.lamports());
@@ -205,16 +213,16 @@ impl Processor {
         // let vault_required_lamports = rent.minimum_balance(spl_token::state::Account::LEN);
         if vault_account.data_is_empty() {
             // associated attempt
-            // msg!("Actually Creating Associated Token vault account");
+            msg!("Actually Creating Associated Token vault account");
 
             invoke(
                 &spl_associated_token_account::instruction::create_associated_token_account(
                     payer_account.key,
-                    payer_account.key,
+                    program_id_account.key,
                     mint_account_token_a.key, // the mint this associated account should be for is the token a mint
                     // NOTE:
-                    &spl_token::id(), // SPL Token program ID is needed here
-                                      // associated_token_program.key,
+                    spl_account.key, // SPL Token program ID is needed here
+                                     // associated_token_program.key,
                 ),
                 &[
                     payer_account.clone(),        // Funding account
@@ -224,6 +232,7 @@ impl Processor {
                     system_program.clone(),       // System program
[…]

### 2024-09-02 hello_world/tests/test.rs

@@ -120,7 +120,9 @@ async fn test_create_vault() -> Result<(), TransportError> {
     // NOTE vault key should be associated token account for token a's mint
     // let vault_keypair = Keypair::new(); // Vault account
     // let vault_key = vault_keypair.pubkey();
-    let vault_key: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key);
+    // let vault_key: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key);
+    let vault_key: Pubkey = get_associated_token_address(&program_id, &mint_tokena_key); //associated address for programid and tokenamint
+    let user_token_a_key: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key);
 
     // Call the function to create the vault instruction
     println!("Creating vault instruction...");
@@ -132,6 +134,7 @@ async fn test_create_vault() -> Result<(), TransportError> {
         &payer.pubkey(),
         &state_key,
         &associated_token_program,
+        &user_token_a_key,
         // &[&payer.pubkey(), &mint_key, &vault_key, &state_key],
     );
 
@@ -258,7 +261,8 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
     let mint_atokena_key1 = mint_atokena_keypair1.pubkey();
 
     // Derive the associated token account for the first vault
-    let vault_key1: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key1);
+    let vault_key1: Pubkey = get_associated_token_address(&program_id, &mint_tokena_key1);
+    let user_token_a: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key1);
 
     // Create the first vault instruction
     println!("Creating first vault instruction...");
@@ -270,6 +274,7 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
         &payer.pubkey(),
         &state_account_pda,
         &associated_token_program,
+        &user_token_a,
     );
 
     let mut transaction1 =
@@ -291,7 +296,7 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
     let mint_atokena_key2 = mint_atokena_keypair2.pubkey();
 
     // Derive the associated token account for the second vault
-    let vault_key2: Pubkey = get_associated_token_address(&payer.pubkey(), &mint_tokena_key2);
[…]

### 2024-09-04 hello_world/rugsafe/paper/paper.tex
paper update

--- 2024-09-01 hello_world/rugsafe/paper/paper.tex
@@
 This mechanism is inspired by quadratic voting schemes, where the penalty increases progressively as the holder's balance of $C_a$ tokens grows, ensuring fairness and preventing manipulation.
-
-The penalty $P(C_a)$ for withdrawing rugged tokens is mathematically represented as:
+the penalty $P(C_a)$ for withdrawing rugged tokens is mathematically represented as:
 
@@
 
-where $\lambda > 1$ is a scaling factor that ensures the penalty increases non-linearly with the amount of $C_a$ held.
+Where $\lambda > 1$ is a scaling factor that ensures the penalty increases non-linearly with the amount of $C_a$ held.
 
-\subsubsection{Impact on Regular Users vs. Whales}
+\subsubsection{Impact on regular users vs. whales}
 
@@
 This non-linear increase in penalty serves two purposes.
-First, it deters whales from attempting to manipulate the system by accumulating and withdrawing large amounts of $C_r$.
+first, it deters whales from attempting to manipulate the system by accumulating and withdrawing large amounts of $C_r$.
 Second, it ensures that whales, who may also be regular users of the protocol, are subject to the same rules but with penalties that reflect their larger influence on the system.
 
-\subsubsection{Equitable System Design}
+\subsubsection{equitable system design}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/6.png}
+\caption{the impact of the whale penalty mechanism based on varying scaling factors $\lambda$.
+as $\lambda$ increases, the penalty for holding larger amounts of $C_a$ grows exponentially, particularly affecting whales with significant holdings.}
+\label{fig:whale_penalty}
+\end{figure}
 
@@
 
+\subsubsection{cumulative penalty mechanism}
+
 \begin{figure}[h]
 \centering
-\includegraphics[width=\textwidth]{images/6.png}
-\caption{The impact of the whale penalty mechanism based on varying scaling factors $\lambda$.
-As $\lambda$ increases, the penalty for holding larger amounts of $C_a$ grows exponentially, particularly affecting whales with significant holdings.}
-\label{fig:whale_penalty}
+\includegraphics[width=\textwidth]{images/9.png}
+\caption{the impact of the cumulative penalty mechanism on sybil attack attempts.
+the more accounts a whale creates to split their holdings, the higher the cumulative penalty becomes, discouraging such behavior.}
+\label{fig:cumulative_penalty}
 \end{figure}
+
+To further enhance the protocol's defense against potential sybil attacks, a cumulative penalty mechanism has been introduced.
+This mechanism accumulates penalties progressively with each withdrawal attempt, particularly when a whale attempts to split their holdings across multiple accounts to evade higher penalties.
+
+In this approach, the cumulative penalty is applied on a per-account basis but is aggregated across all related accounts.
+As illustrated in figure \ref{fig:cumulative_penalty}, the more accounts a whale creates to distribute their holdings, the more significant the overall penalty becomes.
+This cumulative effect discourages sybil attacks by ensuring that the total penalty incurred across all accounts exceeds what would have been paid if the whale had used a single account.
+
+\[
+P_{\text{cumulative}}(C_a) = P(C_a) \times \text{number of withdrawals}
+\]
+
+This means that while the whale may try to avoid the higher penalties by splitting their holdings across multiple accounts, the total cumulative penalty across those accounts will still be greater than the penalty they would have faced had they withdrawn the entire amount in a single transaction.
+
+This can be seen in the plot below, where splitting across more accounts results in steeper cumulative penalties.
+the yellow and purple lines represent penalties for whales trying to split their holdings across 4 and 10 accounts, respectively.
+
+%%%%%%
+
+\subsubsection{Combining both mechanisms}
+
+By combining the original non-linear penalty mechanism (which targets large holdings) with the cumulative penalty mechanism (which penalizes sybil attack attempts), the protocol ensures that whales are doubly disincentivized from trying to game the system.
+
+Whales face increasing penalties for holding large amounts of $C_a$.
+They also face additional cumulative penalties if they attempt to circumvent the system through sybil attacks by distributing their holdings across multiple accounts.
+
+To formally prove that a whale attempting to split their holdings across multiple accounts incurs a higher penalty than withdrawing the entire amount in one transaction, consider the following:
+
+\subsubsection{One-time withdrawal}
+
+For a whale holding $H_{total}$ tokens, the penalty for a single withdrawal is:
+
+\[
+P_{\text{one-time}} = H_{total} \times \gamma
+\]
+
+Where $\gamma$ is the penalty rate (e.g., 10\%).
+
+\subsubsection{Sybil withdrawal}
+
+If the whale splits $H_{total}$ into $n$ accounts, the penalty for each account is given by:
+
+\[
+P_{\text{split}} = \left(\frac{H_{total}}{n}\right) \times \gamma
+\]
+
+The cumulative penalty is the sum of penalties across all $n$ accounts:
+
+\[
+P_{\text{cumulative}} = \sum_{i=1}^{n} \left( \frac{H_{total}}{n} \times \left( \gamma + \Delta \gamma \times i \right) \right)
+\]
+
+Where $\Delta \gamma$ is the incremental penalty applied to each subsequent withdrawal (i.e., cumulative penalty mechanism).
+
+Simplifying this expression:
+
+\[
+P_{\text{cumulative}} = H_{total} \times \gamma + \frac{H_{total} \times \Delta \gamma \times n}{2}
+\]
+
+This expression shows that the cumulative penalty grows with both the number of splits $n$ and the incremental penalty $\Delta \gamma$, resulting in a total penalty that is higher than the one-time withdrawal penalty:
+
+\[
+P_{\text{cumulative}} > P_{\text{one-time}}
+\]
+
+Therefore, attempting to game the system through sybil attacks (splitting tokens across multiple accounts) leads to a higher overall penalty, as the cumulative penalty mechanism introduces increasing costs with each additional withdrawal.
+
+This combined system ensures the integrity of the protocol by preventing manipulative behaviors and promoting fairness for all participants.
 

### 2024-09-04 hello_world/rugsafe/paper/paper.tex
saved

@@
 \[
-\text{Rug Creator's Swap} = \text{Large Supply of Rug Token} \rightarrow \text{Withdrawal of All Liquid Tokens}
+\text{Swap} = \text{Rug Token (Large Supply)} \rightarrow \text{Liquid Token (Full Withdrawal)}
 \]
@@
 
-Through mechanisms like bonding, claim processes, and community-driven challenge periods, the Rugsafe protocol provides a robust framework to protect users from potential rug pulls.
+Through mechanisms like bonding, claim processes, and community-driven challenge periods, the Rugsafe protocol provides a protocol to protect users from rug pulls.
 By requiring issuers to post a bond at token issuance and allowing the community to challenge suspected rug pulls, the protocol empowers users to take proactive steps in safeguarding their investments.

### 2024-09-28 hello_world/src/instructions/perpetuals/processor.rs
fix(test): open position test works, now using  single store for all positions

@@ -1,5 +1,5 @@
 use crate::instructions::perpetuals::PerpetualsInstruction;
-use crate::state::perpetuals::{Position, Side};
+use crate::state::perpetuals::{Position, Side, UserPositions};
 use borsh::{BorshDeserialize, BorshSerialize};
 use solana_program::{
     account_info::{next_account_info, AccountInfo},
@@ -42,6 +42,129 @@ impl Processor {
         }
     }
 
+    // fn process_open_position(
+    //     program_id: &Pubkey,
+    //     accounts: &[AccountInfo],
+    //     side: Side,
+    //     amount: u64,
+    // ) -> ProgramResult {
+    //     msg!("Processing OpenPosition instruction");
+
+    //     let account_info_iter = &mut accounts.iter();
+
+    //     let payer_account = next_account_info(account_info_iter)?; // User who opens the position
+    //     let position_account = next_account_info(account_info_iter)?; // PDA for the position
+    //     let user_collateral_account = next_account_info(account_info_iter)?; // User's collateral token account
+    //     let custody_account = next_account_info(account_info_iter)?; // Vault's custody account
+    //     let token_program = next_account_info(account_info_iter)?; // Token program
+    //     let system_program = next_account_info(account_info_iter)?; // System program
+    //     let rent_account = next_account_info(account_info_iter)?; // Rent sysvar
+
+    //     msg!("Payer account: {}", payer_account.key);
+    //     msg!("Position account: {}", position_account.key);
+    //     msg!("User collateral account: {}", user_collateral_account.key);
+    //     msg!("Custody account: {}", custody_account.key);
+
+    //     // Ensure the payer is a signer
+    //     if !payer_account.is_signer {
+    //         return Err(ProgramError::MissingRequiredSignature);
+    //     }
+
+    //     // Derive the expected position PDA
+    //     let (expected_position_pubkey, bump_seed) =
+    //         Pubkey::find_program_address(&[b"position", payer_account.key.as_ref()], program_id);
+
+    //     msg!("Expected position PDA: {}", expected_position_pubkey);
+
+    //     if position_account.key != &expected_position_pubkey {
+    //         msg!("Invalid position account");
+    //         return Err(ProgramError::InvalidArgument);
+    //     }
+
+    //     // Create the position account if it's empty
+    //     if position_account.data_is_empty() {
+    //         msg!("Position account is empty, creating account");
+
+    //         let rent = &solana_program::rent::Rent::from_account_info(rent_account)?;
[…]

### 2024-09-28 hello_world/tests/test_suite/perpetuals/test_perpetuals.rs

@@ -15,19 +15,16 @@ use spl_token::state::Account as TokenAccount;
 use borsh::{BorshDeserialize, BorshSerialize};
 use rugsafe::instructions::processor::Processor;
 
-use rugsafe::state::perpetuals::{Position, Side};
+use rugsafe::state::perpetuals::{Position, Side, UserPositions};
+// use solana_logger;
+
 #[tokio::test]
 async fn test_open_position() {
-    // solana_logger::setup_with_default("solana_runtime::message_processor=debug"); // Enable detailed logging
+    // solana_logger::setup();
 
     // Step 1: Initialize the program ID and set up the ProgramTest environment
     let program_id = Pubkey::new_unique();
-    let mut program_test = ProgramTest::new(
-        "rugsafe", // Replace with your program name if different
-        program_id,
-        processor!(Processor::process),
-        // processor!(process_instruction),
-    );
+    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(Processor::process));
 
     // Add the SPL Token program to the test environment
     program_test.add_program(
@@ -39,7 +36,7 @@ async fn test_open_position() {
     // Start the test context
     let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
 
-    // Step 2: Create the collateral token mint
+    // **Step 2: Create the collateral token mint**
     let collateral_mint = Keypair::new();
     let mint_rent = banks_client
         .get_rent()
@@ -73,7 +70,7 @@ async fn test_open_position() {
 
     banks_client.process_transaction(transaction).await.unwrap();
 
-    // Step 3: Create user's collateral token account and mint tokens to it
+    // **Step 3: Create user's collateral token account and mint tokens to it**
     let user_collateral_account = Keypair::new();
     let rent = banks_client
         .get_rent()
@@ -121,7 +118,7 @@ async fn test_open_position() {
 
     banks_client.process_transaction(transaction).await.unwrap();
 
-    // Step 4: Create the custody account (where collateral is stored)
+    // **Step 4: Create the custody account (where collateral is stored)**
     let custody_account = Keypair::new();
 
     let create_custody_account_ix = system_instruction::create_account(
@@ -149,11 +146,31 @@ async fn test_open_position() {
 
     banks_client.process_transaction(transaction).await.unwrap();
 
-    // Step 5: Derive the Position PDA
-    let (position_pda, bump_seed) =
-        Pubkey::find_program_address(&[b"position", payer.pubkey().as_ref()], &program_id);
[…]

### 2024-09-29 hello_world/src/instructions/perpetuals/processor.rs
fix(perp/processor.rs, perp/test_perpetuals.rs): perpetuals can now open positions, the custody account is now an ATA for the colateral mint, and the user_positions account is now a PDA)

@@ -6,10 +6,14 @@ use solana_program::{
     clock::Clock,
     entrypoint::ProgramResult,
     msg,
+    program::invoke,
+    program::invoke_signed,
     program_error::ProgramError,
     pubkey::Pubkey,
+    rent::Rent,
     sysvar::Sysvar,
 };
+use spl_associated_token_account::get_associated_token_address;
 
 pub struct Processor;
 
@@ -42,161 +46,144 @@ impl Processor {
         }
     }
 
-    // fn process_open_position(
-    //     program_id: &Pubkey,
-    //     accounts: &[AccountInfo],
-    //     side: Side,
-    //     amount: u64,
-    // ) -> ProgramResult {
-    //     msg!("Processing OpenPosition instruction");
-
-    //     let account_info_iter = &mut accounts.iter();
-
-    //     let payer_account = next_account_info(account_info_iter)?; // User who opens the position
-    //     let position_account = next_account_info(account_info_iter)?; // PDA for the position
-    //     let user_collateral_account = next_account_info(account_info_iter)?; // User's collateral token account
-    //     let custody_account = next_account_info(account_info_iter)?; // Vault's custody account
-    //     let token_program = next_account_info(account_info_iter)?; // Token program
-    //     let system_program = next_account_info(account_info_iter)?; // System program
-    //     let rent_account = next_account_info(account_info_iter)?; // Rent sysvar
-
-    //     msg!("Payer account: {}", payer_account.key);
-    //     msg!("Position account: {}", position_account.key);
-    //     msg!("User collateral account: {}", user_collateral_account.key);
-    //     msg!("Custody account: {}", custody_account.key);
-
-    //     // Ensure the payer is a signer
-    //     if !payer_account.is_signer {
-    //         return Err(ProgramError::MissingRequiredSignature);
-    //     }
-
-    //     // Derive the expected position PDA
-    //     let (expected_position_pubkey, bump_seed) =
-    //         Pubkey::find_program_address(&[b"position", payer_account.key.as_ref()], program_id);
-
-    //     msg!("Expected position PDA: {}", expected_position_pubkey);
-
-    //     if position_account.key != &expected_position_pubkey {
-    //         msg!("Invalid position account");
-    //         return Err(ProgramError::InvalidArgument);
-    //     }
-
-    //     // Create the position account if it's empty
-    //     if position_account.data_is_empty() {
-    //         msg!("Position account is empty, creating account");
-
[…]

### 2024-09-29 hello_world/src/instructions/vaults/processor.rs

@@ -537,9 +537,7 @@ impl Processor {
                     payer_account.clone(),         // Wallet address
                     mint_atoken_a_account.clone(), // Token mint address
                     system_program.clone(),        // System program
-                    // NOTE: spl or associated
-                    spl_account.clone(), // SPL Token program
-                    // associated_token_program.clone(), // associated_token_program.clone(),
+                    spl_account.clone(),           // SPL Token program
                     rent_account.clone(),
                 ],
             )?;

### 2024-09-29 hello_world/tests/test_suite/perpetuals/test_perpetuals.rs

@@ -16,17 +16,20 @@ use borsh::{BorshDeserialize, BorshSerialize};
 use rugsafe::instructions::processor::Processor;
 
 use rugsafe::state::perpetuals::{Position, Side, UserPositions};
-// use solana_logger;
+use spl_associated_token_account::get_associated_token_address;
 
 #[tokio::test]
 async fn test_open_position() {
+    // Initialize logger if needed
     // solana_logger::setup();
 
     // Step 1: Initialize the program ID and set up the ProgramTest environment
+    println!("Initializing ProgramTest environment...");
     let program_id = Pubkey::new_unique();
     let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(Processor::process));
 
     // Add the SPL Token program to the test environment
+    println!("Adding SPL Token program...");
     program_test.add_program(
         "spl_token",
         spl_token::id(),
@@ -34,9 +37,11 @@ async fn test_open_position() {
     );
 
     // Start the test context
+    println!("Starting test context...");
     let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
 
     // **Step 2: Create the collateral token mint**
+    println!("Creating collateral token mint...");
     let collateral_mint = Keypair::new();
     let mint_rent = banks_client
         .get_rent()
@@ -68,9 +73,11 @@ async fn test_open_position() {
         recent_blockhash,
     );
 
+    println!("Processing mint transaction...");
     banks_client.process_transaction(transaction).await.unwrap();
 
     // **Step 3: Create user's collateral token account and mint tokens to it**
+    println!("Creating user's collateral token account and minting tokens...");
     let user_collateral_account = Keypair::new();
     let rent = banks_client
         .get_rent()
@@ -116,61 +123,25 @@ async fn test_open_position() {
         recent_blockhash,
     );
 
+    println!("Processing user token minting transaction...");
     banks_client.process_transaction(transaction).await.unwrap();
 
-    // **Step 4: Create the custody account (where collateral is stored)**
-    let custody_account = Keypair::new();
-
-    let create_custody_account_ix = system_instruction::create_account(
-        &payer.pubkey(),
-        &custody_account.pubkey(),
-        rent,
-        TokenAccount::LEN as u64,
-        &spl_token::id(),
+    // **Step 4: Derive the custody associated token account**
+    println!("Deriving custody associated token account...");
+    let custody_account = spl_associated_token_account::get_associated_token_address(
[…]

### 2024-09-29 hello_world/tests/test_suite/vaults/test_vaults.rs

@@ -596,6 +596,7 @@ fn create_vault_instruction(
         AccountMeta::new(*user_token_a, false),
         AccountMeta::new(*program_id, false),
     ];
+    println!("Create Vault program_id: {:?}", program_id);
 
     Instruction {
         program_id: *program_id,

### 2024-09-29 hello_world/src/instructions/perpetuals/processor.rs
before altering state to make an account per position

@@ -117,7 +117,6 @@ impl Processor {
 
         // Check that the provided user_positions_account matches the derived PDA
         if user_positions_account.key != &user_positions_pda {
-            msg!("User positions account key does not match the expected PDA");
             return Err(ProgramError::InvalidArgument);
         }
 
@@ -159,7 +158,6 @@ impl Processor {
 
         if custody_account.data_is_empty() {
             // Create the associated token account for custody
-            msg!("Custody Account is empty");
             invoke(
                 // &spl_associated_token_account::create_associated_token_account(
                 &spl_associated_token_account::instruction::create_associated_token_account(
@@ -196,7 +194,6 @@ impl Processor {
 
             // Check if the owner matches
             if user_positions.owner != *payer_account.key {
-                msg!("User positions account owner does not match payer");
                 return Err(ProgramError::InvalidAccountData);
             }
             user_positions
@@ -204,7 +201,6 @@ impl Processor {
 
         // Check if positions vector is not full
         if user_positions.positions.len() >= UserPositions::MAX_POSITIONS {
-            msg!("Maximum number of positions reached");
             return Err(ProgramError::AccountDataTooSmall);
         }
 
@@ -213,10 +209,7 @@ impl Processor {
 
         // Check that the provided custody account matches the derived associated token account
         if custody_account.key != &custody_ata {
-            msg!("Custody account key does not match the expected associated token account");
             return Err(ProgramError::InvalidArgument);
-        } else {
-            msg!("Custody Account matches expected Associated Token Account");
         }
 
         // Check that the provided custody account matches the derived associated token account
@@ -240,8 +233,6 @@ impl Processor {
                     rent_account.clone(),
                 ],
             )?;
-        } else {
-            msg!("Custody Account matches expected Associated Token Account");
         }
 
         // Create a new Position
@@ -272,8 +263,6 @@ impl Processor {
             &[],
             amount,
         )?;
-
-        msg!("Transferring collateral from user to custody account");
 
         invoke(
             &transfer_ix,

### 2024-09-29 hello_world/src/instructions/perpetuals/processor.rs
feat(state/perpetuals): just made it now where we can store infinite positions

@@ -64,6 +64,7 @@ impl Processor {
         let rent_account = next_account_info(account_info_iter)?; // Rent sysvar
         let associated_token_program = next_account_info(account_info_iter)?; // Associated token account program
         let program_account = next_account_info(account_info_iter)?; // Program's AccountInfo
+        let position_account = next_account_info(account_info_iter)?; // **Position account (PDA) should be last**
 
         msg!("OpenPosition Account: Program ID: {:?}", program_id);
         msg!(
@@ -104,6 +105,12 @@ impl Processor {
             "OpenPosition Account: Program Accout: {:?}",
             program_account.key
         );
+
+        msg!(
+            "OpenPosition Account: Position PDA: {:?}",
+            position_account.key
+        );
+
         // Ensure the payer is a signer
         if !payer_account.is_signer {
             return Err(ProgramError::MissingRequiredSignature);
@@ -159,7 +166,6 @@ impl Processor {
         if custody_account.data_is_empty() {
             // Create the associated token account for custody
             invoke(
-                // &spl_associated_token_account::create_associated_token_account(
                 &spl_associated_token_account::instruction::create_associated_token_account(
                     payer_account.key,
                     program_id, // Owner is the program
@@ -177,16 +183,15 @@ impl Processor {
                 ],
             )?;
         }
-
         // Deserialize the UserPositions account data
-        let mut user_positions_data = user_positions_account.try_borrow_mut_data()?;
+        let mut user_positions_data = user_positions_account.try_borrow_mut_data()?; // Access data via AccountInfo
         let mut data_slice: &[u8] = &user_positions_data;
 
         let mut user_positions = if data_slice.iter().all(|&x| x == 0) {
             // Account data is uninitialized, initialize UserPositions
             UserPositions {
                 owner: *payer_account.key,
-                positions: Vec::new(),
+                next_position_idx: 0, // Initialize index to 0
             }
         } else {
             // Account data is initialized, deserialize
@@ -199,39 +204,43 @@ impl Processor {
             user_positions
         };
 
-        // Check if positions vector is not full
-        if user_positions.positions.len() >= UserPositions::MAX_POSITIONS {
-            return Err(ProgramError::AccountDataTooSmall);
-        }
+        // Derive the PDA for the new position based on the user and the position index
+        let (position_pda, position_bump) = Pubkey::find_program_address(
+            &[
+                b"position",
+                payer_account.key.as_ref(),
+                &user_positions.next_position_idx.to_le_bytes(),
+            ],
+            program_id,
+        );
 
[…]

### 2024-09-29 hello_world/src/state/perpetuals.rs

@@ -42,11 +42,10 @@ impl Position {
 
 #[derive(Default, Debug, BorshSerialize, BorshDeserialize)]
 pub struct UserPositions {
-    pub owner: Pubkey,
-    pub positions: Vec<Position>, // Max length MAX_POSITIONS
+    pub owner: Pubkey,          // Owner's public key, no change
+    pub next_position_idx: u64, // Pointer to the next position index
 }
 
 impl UserPositions {
-    pub const MAX_POSITIONS: usize = MAX_POSITIONS; // Max number of positions per user
-    pub const LEN: usize = 32 + 4 + Position::LEN * Self::MAX_POSITIONS; // 32 bytes for owner, 4 bytes for vector length, rest for positions
+    pub const LEN: usize = 32 + 8; // 32 bytes for owner, 8 bytes for position index
 }

### 2024-09-29 hello_world/tests/test_suite/perpetuals/test_perpetuals.rs

@@ -161,7 +161,18 @@ async fn test_open_position() {
     instruction_data.extend_from_slice(&amount.to_le_bytes()); // Amount as u64 in little-endian
     println!("Instruction data: {:?}", instruction_data);
 
-    // Create the instruction
+    // **Derive the position PDA based on the next position index, assuming it's 0 for now**
+    let (position_pda, _position_bump) = Pubkey::find_program_address(
+        &[
+            b"position",
+            payer.pubkey().as_ref(),
+            &0u64.to_le_bytes(), // Assuming next position index is 0 initially
+        ],
+        &program_id,
+    );
+    println!("Position PDA: {:?}", position_pda);
+
+    // **Step 7: Send the OpenPosition transaction**
     let open_position_ix = Instruction {
         program_id,
         accounts: vec![
@@ -174,15 +185,12 @@ async fn test_open_position() {
             AccountMeta::new_readonly(solana_program::system_program::id(), false), // System program
             AccountMeta::new_readonly(solana_program::sysvar::rent::id(), false),   // Rent sysvar
             AccountMeta::new_readonly(spl_associated_token_account::id(), false), // Associated token program
-            AccountMeta::new_readonly(program_id, false), // Program account (newly added)
+            AccountMeta::new_readonly(program_id, false),                         // Program account
+            AccountMeta::new(position_pda, false), // Add the position PDA here (writable)
         ],
         data: instruction_data,
     };
 
-    // Log the instruction details
-    println!("OpenPosition instruction: {:?}", open_position_ix);
-
-    // **Step 7: Send the transaction**
     let transaction = Transaction::new_signed_with_payer(
         &[open_position_ix],
         Some(&payer.pubkey()),
@@ -193,7 +201,7 @@ async fn test_open_position() {
     println!("Processing open position transaction...");
     banks_client.process_transaction(transaction).await.unwrap();
 
-    // **Step 8: Verify the results**
+    // **Step 8: Fetch and verify user position details**
     println!("Fetching UserPositions account data...");
     let user_positions_account_data = banks_client
         .get_account(user_positions_pda)
@@ -205,13 +213,36 @@ async fn test_open_position() {
     let mut data_slice: &[u8] = &user_positions_account_data.data;
     let user_positions = UserPositions::deserialize(&mut data_slice).unwrap();
 
-    // Log and assert that a position was added
-    println!("User positions: {:?}", user_positions.positions);
-    assert_eq!(user_positions.positions.len(), 1);
[…]

### 2024-09-30 rugsafe-perps/src/instructions.rs
updated folder structure with broken out contracts

@@ -1,0 +1,5 @@
+pub mod perpetuals;
+pub mod processor;
+
+// pub use {perpetuals::*, vaults::*};
+pub use perpetuals::instruction::PerpetualsInstruction;

### 2024-09-30 rugsafe-perps/src/instructions/perpetuals/mod.rs

@@ -1,0 +1,5 @@
+pub mod instruction;
+// pub mod perpetuals;
+pub mod processor;
+// pub use {instruction::*, perpetuals::*};
+pub use {instruction::*, processor::*};

### 2024-09-30 rugsafe-perps/src/instructions/perpetuals/processor.rs

@@ -1,0 +1,332 @@
+use crate::instructions::perpetuals::PerpetualsInstruction;
+use crate::state::perpetuals::{Position, Side, UserPositions};
+use borsh::{BorshDeserialize, BorshSerialize};
+use solana_program::{
+    account_info::{next_account_info, AccountInfo},
+    clock::Clock,
+    entrypoint::ProgramResult,
+    msg,
+    program::invoke,
+    program::invoke_signed,
+    program_error::ProgramError,
+    pubkey::Pubkey,
+    rent::Rent,
+    sysvar::Sysvar,
+};
+use spl_associated_token_account::get_associated_token_address;
+
+pub struct Processor;
+
+impl Processor {
+    pub fn process(
+        program_id: &Pubkey,
+        accounts: &[AccountInfo],
+        instruction_data: &[u8],
+    ) -> ProgramResult {
+        let instruction = PerpetualsInstruction::unpack(instruction_data)?;
+
+        match instruction {
+            PerpetualsInstruction::OpenPosition { side, amount } => {
+                Self::process_open_position(program_id, accounts, side, amount)
+            }
+            PerpetualsInstruction::ClosePosition { position_id } => {
+                Self::process_close_position(program_id, accounts, position_id)
+            }
+            PerpetualsInstruction::AddCollateral {
+                position_id,
+                amount,
+            } => Self::process_add_collateral(program_id, accounts, position_id, amount),
+            PerpetualsInstruction::RemoveCollateral {
+                position_id,
+                amount,
+            } => Self::process_remove_collateral(program_id, accounts, position_id, amount),
+            PerpetualsInstruction::LiquidatePosition { position_id } => {
+                Self::process_liquidate_position(program_id, accounts, position_id)
+            }
+        }
+    }
+
+    fn process_open_position(
+        program_id: &Pubkey,
+        accounts: &[AccountInfo],
+        side: Side,
+        amount: u64,
+    ) -> ProgramResult {
+        let account_info_iter = &mut accounts.iter();
+
+        let payer_account = next_account_info(account_info_iter)?; // User who opens the position
+        let user_positions_account = next_account_info(account_info_iter)?; // User's positions account (PDA)
+        let user_collateral_account = next_account_info(account_info_iter)?; // User's collateral token account
+        let collateral_mint_account = next_account_info(account_info_iter)?; // Collateral mint account
+        let custody_account = next_account_info(account_info_iter)?; // Custody account (associated token account)
[…]

### 2024-09-30 rugsafe-perps/src/state.rs

@@ -1,0 +1,1 @@
+pub mod perpetuals;

### 2024-09-30 rugsafe-perps/src/state/perpetuals.rs

@@ -1,0 +1,66 @@
+use borsh::{BorshDeserialize, BorshSerialize};
+use solana_program::pubkey::Pubkey;
+
+pub const MAX_POSITIONS: usize = 10; // Max number of positions per user
+
+#[derive(Copy, Clone, PartialEq, Debug, BorshSerialize, BorshDeserialize)]
+pub enum Side {
+    None,
+    Long,
+    Short,
+}
+
+impl Default for Side {
+    fn default() -> Self {
+        Self::None
+    }
+}
+
+#[derive(Debug, Clone, BorshSerialize, BorshDeserialize, Default)]
+pub struct Position {
+    pub owner: Pubkey, // The public key of the user who owns this position. It uniquely identifies the user.
+
+    pub pool: Pubkey, // Represents the liquidity pool in which this position operates. It's used to link the position to a specific market or trading pool.
+
+    pub custody: Pubkey, // The public key of the custody account holding the assets for this position. Custody ensures that assets are stored securely.
+
+    pub collateral_custody: Pubkey, // The public key of the collateral custody account. This holds the collateral deposited to secure the position, protecting against liquidation.
+
+    pub open_time: i64, // Timestamp indicating when the position was first opened. It records the exact moment the position was initiated.
+
+    pub update_time: i64, // Timestamp of the most recent update to the position. It changes whenever new collateral is added, or a partial close happens.
+
+    pub side: Side, // Indicates whether the position is long (betting on price going up) or short (betting on price going down).
+
+    pub price: u64, // The price at which the position was opened. This is the reference price used to calculate profit and loss.
+
+    pub size_usd: u64, // The total size of the position in USD. Represents the notional value of the position.
+
+    pub borrow_size_usd: u64, // The amount borrowed in USD to leverage the position. Borrowing increases potential returns but also risk.
+
+    pub collateral_usd: u64, // The USD value of the collateral held for this position. This collateral is used to maintain the position and mitigate liquidation risk.
+
+    pub unrealized_profit_usd: u64, // The potential profit on the position if it were to be closed at the current market price. It is 'unrealized' because the position is still open.
+
+    pub unrealized_loss_usd: u64, // The potential loss on the position if it were to be closed at the current market price. This is the risk side, also 'unrealized' because the position is still open.
+
[…]

### 2024-09-30 rugsafe-perps/tests/test_suite/mod.rs

@@ -1,0 +1,3 @@
+pub mod perpetuals;
+
+pub use perpetuals::*;

### 2024-09-30 rugsafe-perps/tests/test_suite/perpetuals/test_perpetuals.rs

@@ -1,0 +1,275 @@
+// Import necessary dependencies
+use solana_program::instruction::{AccountMeta, Instruction};
+use solana_program::{system_instruction, sysvar};
+use solana_program_test::*;
+
+use solana_sdk::{
+    program_pack::Pack,
+    pubkey::Pubkey,
+    signature::{Keypair, Signer},
+    transaction::Transaction,
+};
+
+use spl_token::state::Account as TokenAccount;
+
+use borsh::{BorshDeserialize, BorshSerialize};
+use rugsafe::instructions::processor::Processor;
+
+use rugsafe::state::perpetuals::{Position, Side, UserPositions};
+use spl_associated_token_account::get_associated_token_address;
+
+#[tokio::test]
+async fn test_open_position() {
+    // Initialize logger if needed
+    // solana_logger::setup();
+
+    // Step 1: Initialize the program ID and set up the ProgramTest environment
+    println!("Initializing ProgramTest environment...");
+    let program_id = Pubkey::new_unique();
+    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(Processor::process));
+
+    // Add the SPL Token program to the test environment
+    println!("Adding SPL Token program...");
+    program_test.add_program(
+        "spl_token",
+        spl_token::id(),
+        processor!(spl_token::processor::Processor::process),
+    );
+
+    // Start the test context
+    println!("Starting test context...");
+    let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
+
+    // **Step 2: Create the collateral token mint**
+    println!("Creating collateral token mint...");
+    let collateral_mint = Keypair::new();
+    let mint_rent = banks_client
+        .get_rent()
+        .await
+        .unwrap()
+        .minimum_balance(spl_token::state::Mint::LEN);
+
+    let create_mint_ix = system_instruction::create_account(
+        &payer.pubkey(),
+        &collateral_mint.pubkey(),
+        mint_rent,
+        spl_token::state::Mint::LEN as u64,
+        &spl_token::id(),
+    );
+
+    let initialize_mint_ix = spl_token::instruction::initialize_mint(
+        &spl_token::id(),
+        &collateral_mint.pubkey(),
+        &payer.pubkey(),
+        None,
+        6, // Decimals
+    )
+    .unwrap();
+
+    let transaction = Transaction::new_signed_with_payer(
+        &[create_mint_ix, initialize_mint_ix],
+        Some(&payer.pubkey()),
[…]

### 2024-09-30 rugsafe-vaults/src/instructions/vaults/mod.rs

@@ -1,0 +1,7 @@
+pub mod instruction;
+pub mod processor;
+// pub mod vaults;
+
+pub use {instruction::*, processor::*};
+
+// pub use {instruction::*, vaults::*};

### 2024-09-30 rugsafe-vaults/src/lib.rs

@@ -1,0 +1,23 @@
+// pub mod instruction;
+pub mod instructions;
+// pub mod processor;
+// pub mod instructions::
+pub mod state;
+
+// deterministically designate program ID
+// declare_id!("FobNvbQsK5BAniZC2oJhXakjcPiArpsthTGDnX9eHDVY");
+
+use solana_program::{
+    account_info::AccountInfo, entrypoint, entrypoint::ProgramResult, pubkey::Pubkey,
+};
+
+entrypoint!(process_instruction);
+
+pub fn process_instruction(
+    program_id: &Pubkey,
+    accounts: &[AccountInfo],
+    instruction_data: &[u8],
+) -> ProgramResult {
+    // instructions::processor::Processor::process(program_id, accounts, instruction_data)
+    crate::instructions::processor::Processor::process(program_id, accounts, instruction_data)
+}

### 2024-09-30 rugsafe-vaults/src/state/vaults.rs

@@ -1,0 +1,122 @@
+use solana_program::pubkey::Pubkey;
+
+#[derive(Debug, PartialEq)]
+pub struct Vault {
+    pub vault_account: Pubkey,
+    pub mint_token_a: Pubkey,
+    pub mint_a_token_a: Pubkey,
+    pub owner: Pubkey,
+}
+
+#[derive(Debug, PartialEq)]
+pub struct VaultRegistry {
+    pub vaults: Vec<Vault>,
+    pub capacity: usize,
+}
+
+impl Vault {
+    pub const LEN: usize = 32 * 4; // 4 Pubkeys, each 32 bytes
+
+    pub fn serialize(&self) -> Vec<u8> {
+        let mut data = Vec::with_capacity(Self::LEN);
+        data.extend_from_slice(self.vault_account.as_ref());
+        data.extend_from_slice(self.mint_token_a.as_ref());
+        data.extend_from_slice(self.mint_a_token_a.as_ref());
+        data.extend_from_slice(self.owner.as_ref());
+        data
+    }
+
+    pub fn deserialize(input: &[u8]) -> Self {
+        let vault_account = Pubkey::new_from_array(input[0..32].try_into().unwrap());
+        let mint_token_a = Pubkey::new_from_array(input[32..64].try_into().unwrap());
+        let mint_a_token_a = Pubkey::new_from_array(input[64..96].try_into().unwrap());
+        let owner = Pubkey::new_from_array(input[96..128].try_into().unwrap());
+
+        Vault {
+            vault_account,
+            mint_token_a,
+            mint_a_token_a,
+            owner,
+        }
+    }
+}
+
+impl VaultRegistry {
+    pub const INITIAL_CAPACITY: usize = 10;
+
+    pub fn new() -> Self {
+        VaultRegistry {
+            vaults: Vec::new(),
+            capacity: Self::INITIAL_CAPACITY,
+        }
+    }
+
+    pub fn len(&self) -> usize {
+        8 + 8 + (Vault::LEN * self.capacity) // 8 bytes for vec length, 8 bytes for capacity
+    }
+
+    pub fn serialize(&self) -> Vec<u8> {
+        let mut data = Vec::with_capacity(self.len());
+        let vaults_len = self.vaults.len() as u64;
+        data.extend_from_slice(&vaults_len.to_le_bytes());
+        data.extend_from_slice(&(self.capacity as u64).to_le_bytes());
+
+        for vault in &self.vaults {
+            data.extend_from_slice(&vault.serialize());
+        }
+
[…]

### 2024-09-30 rugsafe-vaults/tests/test_suite/vaults/mod.rs

@@ -1,0 +1,3 @@
+pub mod test_vaults;
+
+pub use {test_vaults::*};

### 2024-09-30 rugsafe_original_old_merged/rugsafe/paper/images/py1.py

@@ -1,0 +1,49 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Define the range of the sum of rugged token values
+rugged_token_values = np.linspace(1, 100, 500)
+
+# Calculate the Rugsafe token price based on the equation
+rugsafe_price = 1 / np.log(rugged_token_values)
+rugsafe_price[0] = 0  # Avoid infinite value at the start
+
+# Calculate the price after burning
+burn_percentage = 0.5  # Example of burning 50% of the tokens
+burned_rugsafe_price = 1 / np.log(rugged_token_values * (1 - burn_percentage))
+burned_rugsafe_price[0] = 0  # Avoid infinite value at the start
+
+# Set up the plot with a black background and white text
+plt.style.use('dark_background')
+
+# Plot the results
+fig, axs = plt.subplots(1, 2, figsize=(14, 6))
+
+# Plot for minting
+axs[0].plot(rugged_token_values, rugsafe_price, color='orange', label='Rugsafe Token Price')
+axs[0].set_xlabel('Sum of Rugged Token Values', color='white')
+axs[0].set_ylabel('Rugsafe Token Price', color='white')
+axs[0].set_title('Rugsafe Token Price vs. Sum of Rugged Token Values', color='white')
+axs[0].grid(True, color='gray')
+axs[0].legend()
+
+# Plot for burning
+axs[1].plot(rugged_token_values, burned_rugsafe_price, color='red', label='Burned Rugsafe Token Price')
+axs[1].set_xlabel('Sum of Rugged Token Values', color='white')
+axs[1].set_ylabel('Burned Rugsafe Token Price', color='white')
+axs[1].set_title('Burned Rugsafe Token Price vs. Sum of Rugged Token Values', color='white')
+axs[1].grid(True, color='gray')
+axs[1].legend()
+
+# Adjusting the colors of the ticks and labels
+for ax in axs:
+    ax.tick_params(axis='x', colors='white')
+    ax.tick_params(axis='y', colors='white')
+    ax.legend(facecolor='black', edgecolor='white')
+
+# Save the plot as an image file
+plt.savefig('rugsafe_price_vs_burned_black_background.png')
+
+# Display the plot
+plt.show()
+

### 2024-09-30 rugsafe_original_old_merged/rugsafe/paper/images/py2.py

@@ -1,0 +1,35 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Define the range of the sum of rugged token values (total rugged tokens in the world)
+rugged_token_values = np.linspace(1, 1000, 500)
+
+# Calculate the Rugsafe token price based on the equation
+rugsafe_price = 1 / np.log(rugged_token_values)
+
+# Ensure the first value doesn't approach infinity (avoiding division by log(0))
+rugsafe_price[0] = 0
+
+# Calculate the corresponding theoretical supply of Rugsafe tokens
+# Assuming the supply is inversely proportional to the price
+rugsafe_supply = 1 / rugsafe_price
+
+# Set up the plot with a black background and white text
+plt.style.use('dark_background')
+
+# Plot the results
+plt.figure(figsize=(10, 6))
+plt.plot(rugged_token_values, rugsafe_supply, color='cyan', label=r'Theoretical Supply of Rugsafe Tokens $R$')
+plt.xlabel(r'Sum of Rugged Token Values $\sum R_{C_v}$', color='white')
+plt.ylabel('Theoretical Supply of Rugsafe Tokens $R$', color='white')
+plt.title('Theoretical Supply of Rugsafe Tokens vs. Total Rugged Tokens', color='white')
+plt.grid(True, color='gray')
+plt.legend(facecolor='black', edgecolor='white')
+
+# Adjusting the colors of the ticks and labels
+plt.tick_params(axis='x', colors='white')
+plt.tick_params(axis='y', colors='white')
+
+# Display the plot
+plt.show()
+

### 2024-09-30 rugsafe_original_old_merged/rugsafe/paper/images/py5.py

@@ -1,0 +1,101 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Define a common style for all plots
+plt.style.use('dark_background')
+
+# Plot 1: Supply Regulation Plot
+rugged_token_values = np.linspace(1, 1000, 500)
+rugsafe_price = 1 / np.log(rugged_token_values)
+rugsafe_supply = 1 / rugsafe_price
+
+plt.figure(figsize=(10, 6))
+plt.plot(rugged_token_values, rugsafe_supply, color='cyan', label=r'Theoretical Supply of Rugsafe Tokens $R$')
+plt.xlabel(r'Sum of Rugged Token Values $\sum R_{C_v}$', color='white')
+plt.ylabel('Theoretical Supply of Rugsafe Tokens $R$', color='white')
+plt.title('Theoretical Supply of Rugsafe Tokens vs. Total Rugged Tokens', color='white')
+plt.grid(True, color='gray')
+plt.legend()
+plt.tick_params(axis='x', colors='white')
+plt.tick_params(axis='y', colors='white')
+plt.legend(facecolor='black', edgecolor='white')
+plt.show()
+
+
+
+
+
+holdings_Ca = np.linspace(1, 1000, 500)
+lambda_values = [1.5, 2.0, 2.5]
+for lambd in lambda_values:
+    penalty = holdings_Ca**lambd
+    plt.plot(holdings_Ca, penalty, label=f'λ = {lambd}')
+
+plt.xlabel('Holdings of $C_a$', color='white')
+plt.ylabel('Penalty $P(C_a)$', color='white')
+plt.title('Whale Penalty Impact Based on Holdings of $C_a$', color='white')
+plt.grid(True, color='gray')
+plt.legend()
+plt.tick_params(axis='x', colors='white')
+plt.tick_params(axis='y', colors='white')
+plt.legend(facecolor='black', edgecolor='white')
+plt.show()
+
+
+
+
+
+expected_value_Cr = np.linspace(1, 100, 500)
+market_value_Ca = expected_value_Cr**1.1
+plt.figure(figsize=(10, 6))
+plt.plot(expected_value_Cr, market_value_Ca, color='green', label=r'Market Potential of $C_a$ Tokens')
+plt.xlabel('Expected Value of Rugged Tokens $E(P_{C_r})$', color='white')
+plt.ylabel('Market Value of $C_a$', color='white')
[…]

### 2024-09-30 rugsafe_original_old_merged/rugsafe/paper/images/py7.py

@@ -1,0 +1,43 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Define cumulative penalty function
+def cumulative_penalty(amount, factor):
+    return amount * factor
+
+# Initial values
+original_amount = 1000
+splits = [1, 4, 10]  # 1 for no sybil, 4 for sybil with 4 accounts, 10 for sybil with 10 accounts
+penalty_factor = 0.1  # penalty rate
+
+# Plot cumulative penalties for different splits
+plt.figure(figsize=(10, 6))
+
+# Set the black background and white font
+plt.style.use('dark_background')
+
+for split in splits:
+    total_withdrawn = original_amount / split
+    cumulative_penalties = [cumulative_penalty(total_withdrawn * i, penalty_factor) for i in range(1, split + 1)]
+    plt.plot(range(1, split + 1), cumulative_penalties, label=f'Splits = {split}')
+
+plt.xlabel('Number of Withdrawals (Accounts)', color='white')
+plt.ylabel('Cumulative Penalty', color='white')
+plt.title('Cumulative Penalty Impact with Sybil Attack Attempts', color='white')
+plt.legend()
+plt.grid(True, color='gray')
+
+# Set the axis color to white
+plt.gca().spines['bottom'].set_color('white')
+plt.gca().spines['top'].set_color('white') 
+plt.gca().spines['right'].set_color('white')
+plt.gca().spines['left'].set_color('white')
+
+plt.gca().xaxis.label.set_color('white')
+plt.gca().yaxis.label.set_color('white')
+
+plt.gca().tick_params(axis='x', colors='white')
+plt.gca().tick_params(axis='y', colors='white')
+
+plt.show()
+

### 2024-09-30 rugsafe_original_old_merged/rugsafe/paper/images/py8.py

@@ -1,0 +1,42 @@
+# I'll now display the image in this environment directly.
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Define cumulative penalty function
+def cumulative_penalty(amount, factor):
+    return amount * factor
+
+# Initial values
+original_amount = 1000
+splits = [1, 4, 10]  # 1 for no sybil, 4 for sybil with 4 accounts, 10 for sybil with 10 accounts
+penalty_factor = 0.1  # penalty rate
+
+# Plot cumulative penalties for different splits
+plt.figure(figsize=(10, 6))
+
+for split in splits:
+    total_withdrawn = original_amount / split
+    cumulative_penalties = [cumulative_penalty(total_withdrawn * i, penalty_factor) for i in range(1, split + 1)]
+    plt.plot(range(1, split + 1), cumulative_penalties, label=f'Splits = {split}')
+
+plt.xlabel('Number of Withdrawals (Accounts)', color='white')
+plt.ylabel('Cumulative Penalty', color='white')
+plt.title('Cumulative Penalty Impact with Sybil Attack Attempts', color='white')
+plt.legend()
+plt.grid(True)
+
+# Set the plot background to black
+plt.gca().set_facecolor('black')
+plt.gcf().set_facecolor('black')
+
+# Set the color of the labels and title
+plt.gca().spines['bottom'].set_color('white')
+plt.gca().spines['top'].set_color('white') 
+plt.gca().spines['right'].set_color('white')
+plt.gca().spines['left'].set_color('white')
+plt.gca().tick_params(axis='x', colors='white')
+plt.gca().tick_params(axis='y', colors='white')
+
+plt.legend(facecolor='black', edgecolor='white')
+plt.show()
+

### 2024-09-30 rugsafe_original_old_merged/src/instructions/perpetuals/instruction.rs

@@ -1,0 +1,72 @@
+use crate::state::perpetuals::Side;
+use borsh::{BorshDeserialize, BorshSerialize};
+use solana_program::program_error::ProgramError;
+
+#[derive(Clone, Debug, PartialEq, BorshSerialize, BorshDeserialize)]
+pub enum PerpetualsInstruction {
+    OpenPosition { side: Side, amount: u64 },
+    ClosePosition { position_id: u64 },
+    AddCollateral { position_id: u64, amount: u64 },
+    RemoveCollateral { position_id: u64, amount: u64 },
+    LiquidatePosition { position_id: u64 },
+}
+
+impl PerpetualsInstruction {
+    pub fn unpack(input: &[u8]) -> Result<Self, ProgramError> {
+        let (&tag, rest) = input
+            .split_first()
+            .ok_or(ProgramError::InvalidInstructionData)?;
+
+        Ok(match tag {
+            0 => {
+                let (side_byte, rest) = rest
+                    .split_first()
+                    .ok_or(ProgramError::InvalidInstructionData)?;
+                let side = match side_byte {
+                    1 => Side::Long,
+                    2 => Side::Short,
+                    _ => return Err(ProgramError::InvalidInstructionData),
+                };
+                let amount = Self::unpack_amount(rest)?;
+                Self::OpenPosition { side, amount }
+            }
+            1 => {
+                let position_id = Self::unpack_u64(rest)?;
+                Self::ClosePosition { position_id }
+            }
+            2 => {
+                let position_id = Self::unpack_u64(rest)?;
+                let amount = Self::unpack_amount(&rest[8..])?;
+                Self::AddCollateral {
+                    position_id,
+                    amount,
+                }
+            }
+            3 => {
+                let position_id = Self::unpack_u64(rest)?;
+                let amount = Self::unpack_amount(&rest[8..])?;
+                Self::RemoveCollateral {
+                    position_id,
+                    amount,
+                }
+            }
+            4 => {
+                let position_id = Self::unpack_u64(rest)?;
+                Self::LiquidatePosition { position_id }
+            }
+            _ => return Err(ProgramError::InvalidInstructionData),
+        })
+    }
+
+    fn unpack_u64(input: &[u8]) -> Result<u64, ProgramError> {
+        input
+            .get(..8)
+            .and_then(|slice| slice.try_into().ok())
+            .map(u64::from_le_bytes)
[…]

### 2024-09-30 rugsafe_original_old_merged/src/instructions/vaults/instruction.rs

@@ -1,0 +1,57 @@
+use borsh::{BorshDeserialize, BorshSerialize};
+use solana_program::msg;
+use solana_program::program_error::ProgramError;
+#[repr(C)]
+#[derive(Clone, Debug, PartialEq, BorshSerialize, BorshDeserialize)]
+pub enum VaultInstruction {
+    CreateVault,
+    Deposit { amount: u64 },
+    Withdraw { amount: u64 },
+    BurnRToken { amount: u64 },
+    Faucet { amount: u64 },
+}
+
+impl VaultInstruction {
+    pub fn unpack(input: &[u8]) -> Result<Self, ProgramError> {
+        msg!("input: {:?}", hex::encode(input));
+
+        let (&tag, rest) = input
+            .split_first()
+            .ok_or(ProgramError::InvalidInstructionData)?;
+        msg!("tag: {}", tag);
+        msg!("Rest: {:?}", hex::encode(rest));
+
+        Ok(match tag {
+            0 => Self::CreateVault,
+            1 => {
+                let amount = Self::unpack_amount(rest)?;
+                msg!("amount from inside unpack 1: {}", &amount.to_string());
+                Self::Deposit { amount }
+            }
+            2 => {
+                let amount = Self::unpack_amount(rest)?;
+                Self::Withdraw { amount }
+            }
+            3 => {
+                let amount = Self::unpack_amount(rest)?;
+                Self::BurnRToken { amount }
+            }
+            4 => {
+                let amount = Self::unpack_amount(rest)?;
+                msg!("amount from inside unpack 2: {}", &amount.to_string());
+                Self::Faucet { amount }
+            }
+            _ => return Err(ProgramError::InvalidInstructionData),
+        })
+    }
+
+    fn unpack_amount(input: &[u8]) -> Result<u64, ProgramError> {
+        let amount = input
+            .get(..8)
+            .and_then(|slice| slice.try_into().ok())
+            .map(u64::from_le_bytes)
+            .ok_or(ProgramError::InvalidInstructionData)?;
+        msg!("amount from inside unpack_amount: {}", amount);
+        Ok(amount)
+    }
+}

### 2024-09-30 rugsafe_original_old_merged/src/state.rs

@@ -1,0 +1,2 @@
+pub mod perpetuals;
+pub mod vaults;

### 2024-09-30 rugsafe_original_old_merged/tests/test_suite/perpetuals/mod.rs

@@ -1,0 +1,3 @@
+pub mod test_perpetuals;
+
+pub use test_perpetuals::*;

### 2024-09-30 rugsafe_original_old_merged/tests/test_suite/perpetuals/test_perpetuals.rs

@@ -1,0 +1,275 @@
+// Import necessary dependencies
+use solana_program::instruction::{AccountMeta, Instruction};
+use solana_program::{system_instruction, sysvar};
+use solana_program_test::*;
+
+use solana_sdk::{
+    program_pack::Pack,
+    pubkey::Pubkey,
+    signature::{Keypair, Signer},
+    transaction::Transaction,
+};
+
+use spl_token::state::Account as TokenAccount;
+
+use borsh::{BorshDeserialize, BorshSerialize};
+use rugsafe::instructions::processor::Processor;
+
+use rugsafe::state::perpetuals::{Position, Side, UserPositions};
+use spl_associated_token_account::get_associated_token_address;
+
+#[tokio::test]
+async fn test_open_position() {
+    // Initialize logger if needed
+    // solana_logger::setup();
+
+    // Step 1: Initialize the program ID and set up the ProgramTest environment
+    println!("Initializing ProgramTest environment...");
+    let program_id = Pubkey::new_unique();
+    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(Processor::process));
+
+    // Add the SPL Token program to the test environment
+    println!("Adding SPL Token program...");
+    program_test.add_program(
+        "spl_token",
+        spl_token::id(),
+        processor!(spl_token::processor::Processor::process),
+    );
+
+    // Start the test context
+    println!("Starting test context...");
+    let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
+
+    // **Step 2: Create the collateral token mint**
+    println!("Creating collateral token mint...");
+    let collateral_mint = Keypair::new();
+    let mint_rent = banks_client
+        .get_rent()
+        .await
+        .unwrap()
+        .minimum_balance(spl_token::state::Mint::LEN);
+
+    let create_mint_ix = system_instruction::create_account(
+        &payer.pubkey(),
+        &collateral_mint.pubkey(),
+        mint_rent,
+        spl_token::state::Mint::LEN as u64,
+        &spl_token::id(),
+    );
+
+    let initialize_mint_ix = spl_token::instruction::initialize_mint(
+        &spl_token::id(),
+        &collateral_mint.pubkey(),
+        &payer.pubkey(),
+        None,
+        6, // Decimals
+    )
+    .unwrap();
+
+    let transaction = Transaction::new_signed_with_payer(
+        &[create_mint_ix, initialize_mint_ix],
+        Some(&payer.pubkey()),
[…]

### 2024-09-30 rugsafe_original_old_merged/tests/test_suite/vaults/test_vaults.rs

@@ -1,0 +1,991 @@
+// use borsh::de::BorshDeserialize;
+// use borsh::{BorshDeserialize, BorshSerialize};
+use hex;
+use rugsafe::instructions::vaults::VaultInstruction;
+use rugsafe::process_instruction;
+// use rugsafe::processor::Processor;
+use rugsafe::instructions::processor::Processor;
+use rugsafe::state::vaults::{Vault, VaultRegistry};
+use solana_program::hash::Hash;
+use solana_program::program_pack::Pack;
+use solana_program::rent::Rent;
+use solana_program::system_instruction;
+use solana_program::{
+    instruction::{AccountMeta, Instruction},
+    msg,
+    program_error::ProgramError,
+    sysvar,
+    sysvar::rent::ID as RentSysvarId,
+};
+use solana_program_test::*;
+use solana_sdk::{
+    account::Account,
+    pubkey::Pubkey,
+    signature::{Keypair, Signer},
+    transaction::Transaction,
+    transport::TransportError,
+};
+use spl_associated_token_account::get_associated_token_address;
+use spl_token::instruction::initialize_mint;
+use spl_token::state::Account as TokenAccount;
+use spl_token::state::Mint;
+use std::iter;
+
+fn program_error_to_banks_client_error(e: ProgramError) -> BanksClientError {
+    BanksClientError::ClientError(Box::leak(Box::new(e.to_string())))
+    // return Err(BanksClientError::ClientError(Box::new(e.to_string())));
+    // return Err(BanksClientError::ClientError(
+    //     Box::leak(Box::new(e.to_string())).as_str(),
+    // ));
+}
+
+#[tokio::test]
+async fn test_process_instruction() -> Result<(), TransportError> {
+    // Start the test environment
+    let program_id = Pubkey::new_unique();
+    let program_test = ProgramTest::new("hello_world", program_id, processor!(process_instruction));
+
+    // Add accounts to the test environment
+    let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
+
+    // Create a new Keypair for the account
+    let new_account = Keypair::new();
+
+    // Create a transaction to invoke the program
+    let mut transaction = Transaction::new_with_payer(
+        &[system_instruction::create_account(
+            &payer.pubkey(),
+            &new_account.pubkey(),
+            1_000_000,
+            0,
+            &program_id,
+        )],
+        Some(&payer.pubkey()),
+    );
+
+    // Sign the transaction with both the payer and the new account keypair
[…]

### 2024-09-30 rugsafe-vaults/tests/test_suite/vaults/test_vaults.rs
fixing tests for parent integration

@@ -1,11 +1,11 @@
 // use borsh::de::BorshDeserialize;
 // use borsh::{BorshDeserialize, BorshSerialize};
 use hex;
-use rugsafe::instructions::vaults::VaultInstruction;
-use rugsafe::process_instruction;
+use rugsafe_vaults::instructions::vaults::VaultInstruction;
+use rugsafe_vaults::process_instruction;
 // use rugsafe::processor::Processor;
-use rugsafe::instructions::processor::Processor;
-use rugsafe::state::vaults::{Vault, VaultRegistry};
+use rugsafe_vaults::instructions::processor::Processor;
+use rugsafe_vaults::state::vaults::{Vault, VaultRegistry};
 use solana_program::hash::Hash;
 use solana_program::program_pack::Pack;
 use solana_program::rent::Rent;

### 2024-09-30 tests/integration.rs

@@ -1,0 +1,230 @@
+use rugsafe_perps::instructions::processor::Processor as PerpsProcessor;
+use rugsafe_vaults::instructions::processor::Processor as VaultProcessor;
+use solana_program::instruction::{AccountMeta, Instruction};
+use solana_program::program_error::ProgramError;
+use solana_program::program_pack::Pack;
+use solana_program::{system_instruction, sysvar};
+use solana_program_test::*;
+use solana_sdk::{
+    pubkey::Pubkey,
+    signature::{Keypair, Signer},
+    transaction::Transaction,
+    transport::TransportError,
+};
+use spl_associated_token_account::get_associated_token_address;
+use spl_token::state::Account as TokenAccount;
+
+#[tokio::test]
+async fn test_integration_perps_vaults() -> Result<(), TransportError> {
+    // Initialize the test environment
+    let vaults_program_id = Pubkey::new_unique();
+    let perps_program_id = Pubkey::new_unique();
+    let mut program_test = ProgramTest::new(
+        "rugsafe_vaults",
+        vaults_program_id,
+        processor!(VaultProcessor::process),
+    );
+
+    program_test.add_program(
+        "rugsafe_perps",
+        perps_program_id,
+        processor!(PerpsProcessor::process),
+    );
+
+    program_test.add_program(
+        "spl_token",
+        spl_token::id(),
+        processor!(spl_token::processor::Processor::process),
+    );
+
+    let mut context = program_test.start_with_context().await;
+    let banks_client = &mut context.banks_client;
+    let payer = &context.payer;
+    let recent_blockhash = banks_client.get_latest_blockhash().await?;
+
+    // Step 1: Create token mint for vault
+    let mint_keypair = Keypair::new();
+    let mint_rent = banks_client
+        .get_rent()
+        .await?
+        .minimum_balance(TokenAccount::LEN);
+    let create_mint_ix = system_instruction::create_account(
+        &payer.pubkey(),
+        &mint_keypair.pubkey(),
+        mint_rent,
+        spl_token::state::Mint::LEN as u64,
+        &spl_token::id(),
+    );
+    let initialize_mint_ix = spl_token::instruction::initialize_mint(
+        &spl_token::id(),
+        &mint_keypair.pubkey(),
+        &payer.pubkey(),
+        None,
+        6, // 6 decimals
+    )
+    .unwrap();
+
+    let transaction = Transaction::new_signed_with_payer(
[…]

### 2024-09-30 hello_world/rugsafe/paper/images/py3.py
cleaned repo

@@ -1,23 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-# Define a common style for all plots
-plt.style.use('dark_background')
-
-# Plot 1: Supply Regulation Plot
-rugged_token_values = np.linspace(1, 1000, 500)
-rugsafe_price = 1 / np.log(rugged_token_values)
-rugsafe_supply = 1 / rugsafe_price
-
-plt.figure(figsize=(10, 6))
-plt.plot(rugged_token_values, rugsafe_supply, color='cyan', label=r'Theoretical Supply of Rugsafe Tokens $R$')
-plt.xlabel(r'Sum of Rugged Token Values $\sum R_{C_v}$', color='white')
-plt.ylabel('Theoretical Supply of Rugsafe Tokens $R$', color='white')
-plt.title('Theoretical Supply of Rugsafe Tokens vs. Total Rugged Tokens', color='white')
-plt.grid(True, color='gray')
-plt.legend()
-plt.tick_params(axis='x', colors='white')
-plt.tick_params(axis='y', colors='white')
-plt.legend(facecolor='black', edgecolor='white')
-plt.show()
-

### 2024-09-30 hello_world/rugsafe/paper/images/py7.py

@@ -1,43 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Define cumulative penalty function
-def cumulative_penalty(amount, factor):
-    return amount * factor
-
-# Initial values
-original_amount = 1000
-splits = [1, 4, 10]  # 1 for no sybil, 4 for sybil with 4 accounts, 10 for sybil with 10 accounts
-penalty_factor = 0.1  # penalty rate
-
-# Plot cumulative penalties for different splits
-plt.figure(figsize=(10, 6))
-
-# Set the black background and white font
-plt.style.use('dark_background')
-
-for split in splits:
-    total_withdrawn = original_amount / split
-    cumulative_penalties = [cumulative_penalty(total_withdrawn * i, penalty_factor) for i in range(1, split + 1)]
-    plt.plot(range(1, split + 1), cumulative_penalties, label=f'Splits = {split}')
-
-plt.xlabel('Number of Withdrawals (Accounts)', color='white')
-plt.ylabel('Cumulative Penalty', color='white')
-plt.title('Cumulative Penalty Impact with Sybil Attack Attempts', color='white')
-plt.legend()
-plt.grid(True, color='gray')
-
-# Set the axis color to white
-plt.gca().spines['bottom'].set_color('white')
-plt.gca().spines['top'].set_color('white') 
-plt.gca().spines['right'].set_color('white')
-plt.gca().spines['left'].set_color('white')
-
-plt.gca().xaxis.label.set_color('white')
-plt.gca().yaxis.label.set_color('white')
-
-plt.gca().tick_params(axis='x', colors='white')
-plt.gca().tick_params(axis='y', colors='white')
-
-plt.show()
-

### 2024-09-30 hello_world/rugsafe/paper/images/py8.py

@@ -1,42 +1,0 @@
-# I'll now display the image in this environment directly.
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Define cumulative penalty function
-def cumulative_penalty(amount, factor):
-    return amount * factor
-
-# Initial values
-original_amount = 1000
-splits = [1, 4, 10]  # 1 for no sybil, 4 for sybil with 4 accounts, 10 for sybil with 10 accounts
-penalty_factor = 0.1  # penalty rate
-
-# Plot cumulative penalties for different splits
-plt.figure(figsize=(10, 6))
-
-for split in splits:
-    total_withdrawn = original_amount / split
-    cumulative_penalties = [cumulative_penalty(total_withdrawn * i, penalty_factor) for i in range(1, split + 1)]
-    plt.plot(range(1, split + 1), cumulative_penalties, label=f'Splits = {split}')
-
-plt.xlabel('Number of Withdrawals (Accounts)', color='white')
-plt.ylabel('Cumulative Penalty', color='white')
-plt.title('Cumulative Penalty Impact with Sybil Attack Attempts', color='white')
-plt.legend()
-plt.grid(True)
-
-# Set the plot background to black
-plt.gca().set_facecolor('black')
-plt.gcf().set_facecolor('black')
-
-# Set the color of the labels and title
-plt.gca().spines['bottom'].set_color('white')
-plt.gca().spines['top'].set_color('white') 
-plt.gca().spines['right'].set_color('white')
-plt.gca().spines['left'].set_color('white')
-plt.gca().tick_params(axis='x', colors='white')
-plt.gca().tick_params(axis='y', colors='white')
-
-plt.legend(facecolor='black', edgecolor='white')
-plt.show()
-

### 2024-09-30 hello_world/src/instructions.rs

@@ -1,7 +1,0 @@
-pub mod perpetuals;
-pub mod processor;
-pub mod vaults;
-
-// pub use {perpetuals::*, vaults::*};
-pub use perpetuals::instruction::PerpetualsInstruction;
-pub use vaults::instruction::VaultInstruction;

### 2024-09-30 hello_world/src/instructions/perpetuals/instruction.rs

@@ -1,72 +1,0 @@
-use crate::state::perpetuals::Side;
-use borsh::{BorshDeserialize, BorshSerialize};
-use solana_program::program_error::ProgramError;
-
-#[derive(Clone, Debug, PartialEq, BorshSerialize, BorshDeserialize)]
-pub enum PerpetualsInstruction {
-    OpenPosition { side: Side, amount: u64 },
-    ClosePosition { position_id: u64 },
-    AddCollateral { position_id: u64, amount: u64 },
-    RemoveCollateral { position_id: u64, amount: u64 },
-    LiquidatePosition { position_id: u64 },
-}
-
-impl PerpetualsInstruction {
-    pub fn unpack(input: &[u8]) -> Result<Self, ProgramError> {
-        let (&tag, rest) = input
-            .split_first()
-            .ok_or(ProgramError::InvalidInstructionData)?;
-
-        Ok(match tag {
-            0 => {
-                let (side_byte, rest) = rest
-                    .split_first()
-                    .ok_or(ProgramError::InvalidInstructionData)?;
-                let side = match side_byte {
-                    1 => Side::Long,
-                    2 => Side::Short,
-                    _ => return Err(ProgramError::InvalidInstructionData),
-                };
-                let amount = Self::unpack_amount(rest)?;
-                Self::OpenPosition { side, amount }
-            }
-            1 => {
-                let position_id = Self::unpack_u64(rest)?;
-                Self::ClosePosition { position_id }
-            }
-            2 => {
-                let position_id = Self::unpack_u64(rest)?;
-                let amount = Self::unpack_amount(&rest[8..])?;
-                Self::AddCollateral {
-                    position_id,
-                    amount,
-                }
-            }
-            3 => {
-                let position_id = Self::unpack_u64(rest)?;
-                let amount = Self::unpack_amount(&rest[8..])?;
-                Self::RemoveCollateral {
-                    position_id,
-                    amount,
-                }
-            }
-            4 => {
-                let position_id = Self::unpack_u64(rest)?;
-                Self::LiquidatePosition { position_id }
-            }
-            _ => return Err(ProgramError::InvalidInstructionData),
-        })
-    }
-
-    fn unpack_u64(input: &[u8]) -> Result<u64, ProgramError> {
-        input
-            .get(..8)
-            .and_then(|slice| slice.try_into().ok())
-            .map(u64::from_le_bytes)
[…]

### 2024-09-30 hello_world/src/instructions/perpetuals/mod.rs

@@ -1,5 +1,0 @@
-pub mod instruction;
-// pub mod perpetuals;
-pub mod processor;
-// pub use {instruction::*, perpetuals::*};
-pub use {instruction::*, processor::*};

### 2024-09-30 hello_world/src/lib.rs

@@ -1,23 +1,0 @@
-// pub mod instruction;
-pub mod instructions;
-// pub mod processor;
-// pub mod instructions::
-pub mod state;
-
-// deterministically designate program ID
-// declare_id!("FobNvbQsK5BAniZC2oJhXakjcPiArpsthTGDnX9eHDVY");
-
-use solana_program::{
-    account_info::AccountInfo, entrypoint, entrypoint::ProgramResult, pubkey::Pubkey,
-};
-
-entrypoint!(process_instruction);
-
-pub fn process_instruction(
-    program_id: &Pubkey,
-    accounts: &[AccountInfo],
-    instruction_data: &[u8],
-) -> ProgramResult {
-    // instructions::processor::Processor::process(program_id, accounts, instruction_data)
-    crate::instructions::processor::Processor::process(program_id, accounts, instruction_data)
-}

### 2024-09-30 hello_world/src/state.rs

@@ -1,2 +1,0 @@
-pub mod perpetuals;
-pub mod vaults;

### 2024-09-30 hello_world/src/state/perpetuals.rs

@@ -1,51 +1,0 @@
-use borsh::{BorshDeserialize, BorshSerialize};
-use solana_program::pubkey::Pubkey;
-
-pub const MAX_POSITIONS: usize = 10; // Max number of positions per user
-
-#[derive(Copy, Clone, PartialEq, Debug, BorshSerialize, BorshDeserialize)]
-pub enum Side {
-    None,
-    Long,
-    Short,
-}
-
-impl Default for Side {
-    fn default() -> Self {
-        Self::None
-    }
-}
-
-#[derive(Default, Debug, Clone, BorshSerialize, BorshDeserialize)]
-pub struct Position {
-    pub owner: Pubkey,
-    pub pool: Pubkey,
-    pub custody: Pubkey,
-    pub collateral_custody: Pubkey,
-    pub open_time: i64,
-    pub update_time: i64,
-    pub side: Side,
-    pub price: u64,
-    pub size_usd: u64,
-    pub borrow_size_usd: u64,
-    pub collateral_usd: u64,
-    pub unrealized_profit_usd: u64,
-    pub unrealized_loss_usd: u64,
-    pub cumulative_interest_snapshot: u128,
-    pub locked_amount: u64,
-    pub collateral_amount: u64,
-}
-
-impl Position {
-    pub const LEN: usize = 32 * 4 + 8 * 11 + 16 + 1; // Adjusted size calculation
-}
-
-#[derive(Default, Debug, BorshSerialize, BorshDeserialize)]
-pub struct UserPositions {
-    pub owner: Pubkey,          // Owner's public key, no change
-    pub next_position_idx: u64, // Pointer to the next position index
-}
-
-impl UserPositions {
-    pub const LEN: usize = 32 + 8; // 32 bytes for owner, 8 bytes for position index
-}

### 2024-09-30 hello_world/src/state/vaults.rs

@@ -1,122 +1,0 @@
-use solana_program::pubkey::Pubkey;
-
-#[derive(Debug, PartialEq)]
-pub struct Vault {
-    pub vault_account: Pubkey,
-    pub mint_token_a: Pubkey,
-    pub mint_a_token_a: Pubkey,
-    pub owner: Pubkey,
-}
-
-#[derive(Debug, PartialEq)]
-pub struct VaultRegistry {
-    pub vaults: Vec<Vault>,
-    pub capacity: usize,
-}
-
-impl Vault {
-    pub const LEN: usize = 32 * 4; // 4 Pubkeys, each 32 bytes
-
-    pub fn serialize(&self) -> Vec<u8> {
-        let mut data = Vec::with_capacity(Self::LEN);
-        data.extend_from_slice(self.vault_account.as_ref());
-        data.extend_from_slice(self.mint_token_a.as_ref());
-        data.extend_from_slice(self.mint_a_token_a.as_ref());
-        data.extend_from_slice(self.owner.as_ref());
-        data
-    }
-
-    pub fn deserialize(input: &[u8]) -> Self {
-        let vault_account = Pubkey::new_from_array(input[0..32].try_into().unwrap());
-        let mint_token_a = Pubkey::new_from_array(input[32..64].try_into().unwrap());
-        let mint_a_token_a = Pubkey::new_from_array(input[64..96].try_into().unwrap());
-        let owner = Pubkey::new_from_array(input[96..128].try_into().unwrap());
-
-        Vault {
-            vault_account,
-            mint_token_a,
-            mint_a_token_a,
-            owner,
-        }
-    }
-}
-
-impl VaultRegistry {
-    pub const INITIAL_CAPACITY: usize = 10;
-
-    pub fn new() -> Self {
-        VaultRegistry {
-            vaults: Vec::new(),
-            capacity: Self::INITIAL_CAPACITY,
-        }
-    }
-
-    pub fn len(&self) -> usize {
-        8 + 8 + (Vault::LEN * self.capacity) // 8 bytes for vec length, 8 bytes for capacity
-    }
-
-    pub fn serialize(&self) -> Vec<u8> {
-        let mut data = Vec::with_capacity(self.len());
-        let vaults_len = self.vaults.len() as u64;
-        data.extend_from_slice(&vaults_len.to_le_bytes());
-        data.extend_from_slice(&(self.capacity as u64).to_le_bytes());
-
-        for vault in &self.vaults {
-            data.extend_from_slice(&vault.serialize());
-        }
-
[…]

### 2024-09-30 hello_world/tests/test_suite/mod.rs

@@ -1,4 +1,0 @@
-pub mod perpetuals;
-pub mod vaults;
-
-pub use {perpetuals::*, vaults::*};

### 2024-09-30 hello_world/tests/test_suite/perpetuals/test_perpetuals.rs

@@ -1,275 +1,0 @@
-// Import necessary dependencies
-use solana_program::instruction::{AccountMeta, Instruction};
-use solana_program::{system_instruction, sysvar};
-use solana_program_test::*;
-
-use solana_sdk::{
-    program_pack::Pack,
-    pubkey::Pubkey,
-    signature::{Keypair, Signer},
-    transaction::Transaction,
-};
-
-use spl_token::state::Account as TokenAccount;
-
-use borsh::{BorshDeserialize, BorshSerialize};
-use rugsafe::instructions::processor::Processor;
-
-use rugsafe::state::perpetuals::{Position, Side, UserPositions};
-use spl_associated_token_account::get_associated_token_address;
-
-#[tokio::test]
-async fn test_open_position() {
-    // Initialize logger if needed
-    // solana_logger::setup();
-
-    // Step 1: Initialize the program ID and set up the ProgramTest environment
-    println!("Initializing ProgramTest environment...");
-    let program_id = Pubkey::new_unique();
-    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(Processor::process));
-
-    // Add the SPL Token program to the test environment
-    println!("Adding SPL Token program...");
-    program_test.add_program(
-        "spl_token",
-        spl_token::id(),
-        processor!(spl_token::processor::Processor::process),
-    );
-
-    // Start the test context
-    println!("Starting test context...");
-    let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
-
-    // **Step 2: Create the collateral token mint**
-    println!("Creating collateral token mint...");
-    let collateral_mint = Keypair::new();
-    let mint_rent = banks_client
-        .get_rent()
-        .await
-        .unwrap()
-        .minimum_balance(spl_token::state::Mint::LEN);
-
-    let create_mint_ix = system_instruction::create_account(
-        &payer.pubkey(),
-        &collateral_mint.pubkey(),
-        mint_rent,
-        spl_token::state::Mint::LEN as u64,
-        &spl_token::id(),
-    );
-
-    let initialize_mint_ix = spl_token::instruction::initialize_mint(
-        &spl_token::id(),
-        &collateral_mint.pubkey(),
-        &payer.pubkey(),
-        None,
-        6, // Decimals
-    )
-    .unwrap();
-
-    let transaction = Transaction::new_signed_with_payer(
-        &[create_mint_ix, initialize_mint_ix],
-        Some(&payer.pubkey()),
[…]

### 2024-09-30 hello_world/tests/test_suite/vaults/mod.rs

@@ -1,3 +1,0 @@
-pub mod test_vaults;
-
-pub use {test_vaults::*};

### 2024-09-30 hello_world/tests/test_suite/vaults/test_vaults.rs

@@ -1,991 +1,0 @@
-// use borsh::de::BorshDeserialize;
-// use borsh::{BorshDeserialize, BorshSerialize};
-use hex;
-use rugsafe::instructions::vaults::VaultInstruction;
-use rugsafe::process_instruction;
-// use rugsafe::processor::Processor;
-use rugsafe::instructions::processor::Processor;
-use rugsafe::state::vaults::{Vault, VaultRegistry};
-use solana_program::hash::Hash;
-use solana_program::program_pack::Pack;
-use solana_program::rent::Rent;
-use solana_program::system_instruction;
-use solana_program::{
-    instruction::{AccountMeta, Instruction},
-    msg,
-    program_error::ProgramError,
-    sysvar,
-    sysvar::rent::ID as RentSysvarId,
-};
-use solana_program_test::*;
-use solana_sdk::{
-    account::Account,
-    pubkey::Pubkey,
-    signature::{Keypair, Signer},
-    transaction::Transaction,
-    transport::TransportError,
-};
-use spl_associated_token_account::get_associated_token_address;
-use spl_token::instruction::initialize_mint;
-use spl_token::state::Account as TokenAccount;
-use spl_token::state::Mint;
-use std::iter;
-
-fn program_error_to_banks_client_error(e: ProgramError) -> BanksClientError {
-    BanksClientError::ClientError(Box::leak(Box::new(e.to_string())))
-    // return Err(BanksClientError::ClientError(Box::new(e.to_string())));
-    // return Err(BanksClientError::ClientError(
-    //     Box::leak(Box::new(e.to_string())).as_str(),
-    // ));
-}
-
-#[tokio::test]
-async fn test_process_instruction() -> Result<(), TransportError> {
-    // Start the test environment
-    let program_id = Pubkey::new_unique();
-    let program_test = ProgramTest::new("hello_world", program_id, processor!(process_instruction));
-
-    // Add accounts to the test environment
-    let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
-
-    // Create a new Keypair for the account
-    let new_account = Keypair::new();
-
-    // Create a transaction to invoke the program
-    let mut transaction = Transaction::new_with_payer(
-        &[system_instruction::create_account(
-            &payer.pubkey(),
-            &new_account.pubkey(),
-            1_000_000,
-            0,
-            &program_id,
-        )],
-        Some(&payer.pubkey()),
-    );
-
-    // Sign the transaction with both the payer and the new account keypair
[…]

### 2024-09-30 site2/src/script.js

@@ -1,37 +1,0 @@
-// init
-const camera = new THREE.PerspectiveCamera(70, window.innerWidth / window.innerHeight, 0.01, 10);
-camera.position.z = 3;
-
-const scene = new THREE.Scene();
-
-// lighting
-const light = new THREE.DirectionalLight(0xffffff, 1);
-light.position.set(1, 1, 1).normalize();
-scene.add(light);
-
-// load fbx model
-const loader = new THREE.FBXLoader();
-// loader.load('https://threejs.org/examples/models/fbx/Samba%20Dancing.fbx', function (object) {
-loader.load('http://localhost:4000/src/1.fbx', function (object) {
-  // scale the model if necessary
-  object.scale.set(0.01, 0.01, 0.01); // Adjust the scale based on your model's size
-
-  scene.add(object);
-}, undefined, function (error) {
-  console.error('An error happened while loading the FBX model:', error);
-});
-
-// renderer
-const renderer = new THREE.WebGLRenderer({ antialias: true });
-renderer.setSize(window.innerWidth, window.innerHeight);
-document.body.appendChild(renderer.domElement);
-
-// animation loop
-function animation(time) {
-  // Optional: rotate the scene or specific objects
-  scene.rotation.y += 0.01;
-
-  renderer.render(scene, camera);
-}
-
-renderer.setAnimationLoop(animation);

### 2024-09-30 rugsafe-perps/tests/test_suite/perpetuals/test_perpetuals.rs
update checkpoint

@@ -13,9 +13,9 @@ use solana_sdk::{
 use spl_token::state::Account as TokenAccount;
 
 use borsh::{BorshDeserialize, BorshSerialize};
-use rugsafe::instructions::processor::Processor;
+use rugsafe_perps::instructions::processor::Processor;
 
-use rugsafe::state::perpetuals::{Position, Side, UserPositions};
+use rugsafe_perps::state::perpetuals::{Position, Side, UserPositions};
 use spl_associated_token_account::get_associated_token_address;
 
 #[tokio::test]
@@ -24,12 +24,13 @@ async fn test_open_position() {
     // solana_logger::setup();
 
     // Step 1: Initialize the program ID and set up the ProgramTest environment
-    println!("Initializing ProgramTest environment...");
+    // println!("Initializing ProgramTest environment...");
     let program_id = Pubkey::new_unique();
-    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(Processor::process));
+    let mut program_test =
+        ProgramTest::new("rugsafe_perps", program_id, processor!(Processor::process));
 
     // Add the SPL Token program to the test environment
-    println!("Adding SPL Token program...");
+    // println!("Adding SPL Token program...");
     program_test.add_program(
         "spl_token",
         spl_token::id(),
@@ -37,11 +38,11 @@ async fn test_open_position() {
     );
 
     // Start the test context
-    println!("Starting test context...");
+    // println!("Starting test context...");
     let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
 
     // **Step 2: Create the collateral token mint**
-    println!("Creating collateral token mint...");
+    // println!("Creating collateral token mint...");
     let collateral_mint = Keypair::new();
     let mint_rent = banks_client
         .get_rent()
@@ -73,11 +74,11 @@ async fn test_open_position() {
         recent_blockhash,
     );
 
-    println!("Processing mint transaction...");
+    // println!("Processing mint transaction...");
     banks_client.process_transaction(transaction).await.unwrap();
 
     // **Step 3: Create user's collateral token account and mint tokens to it**
-    println!("Creating user's collateral token account and minting tokens...");
+    // println!("Creating user's collateral token account and minting tokens...");
     let user_collateral_account = Keypair::new();
     let rent = banks_client
         .get_rent()
@@ -123,25 +124,25 @@ async fn test_open_position() {
         recent_blockhash,
     );
 
-    println!("Processing user token minting transaction...");
[…]

### 2024-09-30 rugsafe-vaults/tests/test_suite/vaults/test_vaults.rs

@@ -43,7 +43,11 @@ fn program_error_to_banks_client_error(e: ProgramError) -> BanksClientError {
 async fn test_process_instruction() -> Result<(), TransportError> {
     // Start the test environment
     let program_id = Pubkey::new_unique();
-    let program_test = ProgramTest::new("hello_world", program_id, processor!(process_instruction));
+    let program_test = ProgramTest::new(
+        "rugsafe_vaults",
+        program_id,
+        processor!(process_instruction),
+    );
 
     // Add accounts to the test environment
     let (mut banks_client, payer, recent_blockhash) = program_test.start().await;
@@ -86,7 +90,11 @@ async fn test_create_vault() -> Result<(), TransportError> {
     // let state_key = state_keypair.pubkey();
     let (state_key, _bump_seed) = Pubkey::find_program_address(&[b"vault_registry"], &program_id);
 
-    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(process_instruction));
+    let mut program_test = ProgramTest::new(
+        "rugsafe_vaults",
+        program_id,
+        processor!(process_instruction),
+    );
 
     // Add SPL Token program
     program_test.add_program(
@@ -228,7 +236,11 @@ async fn test_create_two_vaults() -> Result<(), TransportError> {
     let spl_key = spl_token::id();
     let associated_token_program = spl_associated_token_account::id();
 
-    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(process_instruction));
+    let mut program_test = ProgramTest::new(
+        "rugsafe_vaults",
+        program_id,
+        processor!(process_instruction),
+    );
 
     // Derive the state account PDA
     let (state_account_pda, _bump_seed) =
@@ -392,7 +404,11 @@ async fn test_deposit() -> Result<(), BanksClientError> {
     let spl_key = spl_token::id();
     let associated_token_program = spl_associated_token_account::id();
 
-    let mut program_test = ProgramTest::new("rugsafe", program_id, processor!(process_instruction));
+    let mut program_test = ProgramTest::new(
+        "rugsafe_vaults",
+        program_id,
+        processor!(process_instruction),
+    );
 
     program_test.add_program(
         "spl_token",
@@ -722,7 +738,11 @@ async fn test_fetch_vault_from_registry() -> Result<(), TransportError> {
 
     let (state_key, _bump_seed) = Pubkey::find_program_address(&[b"vault_registry"], &program_id);
 
[…]

### 2024-09-30 tests/integration.rs

@@ -1,7 +1,7 @@
 use rugsafe_perps::instructions::processor::Processor as PerpsProcessor;
 use rugsafe_vaults::instructions::processor::Processor as VaultProcessor;
 use solana_program::instruction::{AccountMeta, Instruction};
-use solana_program::program_error::ProgramError;
+// use solana_program::program_error::ProgramError;
 use solana_program::program_pack::Pack;
 use solana_program::{system_instruction, sysvar};
 use solana_program_test::*;
@@ -16,6 +16,7 @@ use spl_token::state::Account as TokenAccount;
 
 #[tokio::test]
 async fn test_integration_perps_vaults() -> Result<(), TransportError> {
+    // Initialize the test environment
     // Initialize the test environment
     let vaults_program_id = Pubkey::new_unique();
     let perps_program_id = Pubkey::new_unique();
@@ -42,57 +43,88 @@ async fn test_integration_perps_vaults() -> Result<(), TransportError> {
     let payer = &context.payer;
     let recent_blockhash = banks_client.get_latest_blockhash().await?;
 
-    // Step 1: Create token mint for vault
-    let mint_keypair = Keypair::new();
+    // Step 1: Create Token A mint for the vault
+    let mint_tokena_keypair = Keypair::new();
     let mint_rent = banks_client
         .get_rent()
         .await?
         .minimum_balance(TokenAccount::LEN);
-    let create_mint_ix = system_instruction::create_account(
+    let create_mint_tokena_ix = system_instruction::create_account(
         &payer.pubkey(),
-        &mint_keypair.pubkey(),
+        &mint_tokena_keypair.pubkey(),
         mint_rent,
         spl_token::state::Mint::LEN as u64,
         &spl_token::id(),
     );
-    let initialize_mint_ix = spl_token::instruction::initialize_mint(
+    let initialize_mint_tokena_ix = spl_token::instruction::initialize_mint(
         &spl_token::id(),
-        &mint_keypair.pubkey(),
+        &mint_tokena_keypair.pubkey(),
         &payer.pubkey(),
         None,
-        6, // 6 decimals
+        6,
     )
     .unwrap();
 
+    // Step 2: Create AToken A mint for the vault
+    let mint_atokena_keypair = Keypair::new();
+    let create_mint_atokena_ix = system_instruction::create_account(
+        &payer.pubkey(),
+        &mint_atokena_keypair.pubkey(),
+        mint_rent,
[…]

### 2024-10-03 rugsafe_original_old_merged/rugsafe/paper/paper.tex
updated folder structure with broken out contracts
updated paper

--- 2024-09-04 hello_world/rugsafe/paper/paper.tex
@@
 
-\title{Rugsafe: A Multichain Vault Protocol for Defending Against Rug Pulls}
+\title{Rugsafe: A Multichain Vault Protocol for Recovering from \& Defending Against Rug Pulls}
 \author{info@rugsafe.org}
@@
 Foundational to Rugsafe are specialized vaults where rugged tokens can be securely deposited, and anticoin tokens are issued as receipts.
+These anticoins are designed to be inversely pegged to the price movement of the underlying rugged token.
 Users can utilize these anticoins within the ecosystem or choose to burn them, further securing the protocol and earning additional rewards.
@@
 
-The Rugsafe protocol enables users who hold rugged tokens, denoted as $C_r$, to deposit these tokens into a specialized vault $V_c$ and receive anticoin tokens, $C_a$,  which serve as receipts, \(\mathcal{R} \).
+The Rugsafe protocol enables users who hold rugged tokens, denoted as $C_r$, to deposit these tokens into a specialized vault $V_c$ and receive anticoin tokens, $C_a$,  which serve as receipts, \(\mathcal{R} \), and are inversely pegged to the value of the underlying rugged token.
 The supply of Rugsafe's native token, $R$, is regulated based on the total value of rugged tokens in existence.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ANTICOINS
 
@@
 Upon deposit, the protocol mints an equal amount of $C_a$ tokens, which are credited to the user's balance.
-These $C_a$ tokens serve as a new, clean fungible token for the rugged victim, issued 1:1 with the underlying rugged token.
+These $C_a$ tokens serve as a new, clean fungible token for the rugged victim, issued 1:1 with the underlying rugged token and are inversely pegged to its value.
 
@@
 
-In addition to the 1:1 $C_a$ tokens, the user may also receive a receipt, \(\mathcal{R} \) , in the form of a non-fungible token (NFT) or a refungible token (RFT).
+In addition to the 1:1 $C_a$ tokens, the user may also receive a receipt, \(\mathcal{R} \), in the form of a non-fungible token (NFT) or a refungible token (RFT).
 The 1:1 $C_a$ token acts as a standard fungible token, fully transferable and tradable.
@@
 
-where $\text{type}$ determines whether the receipt is a fungible token, an NFT, or an RFT.
-This provides flexibility depending on the specific use case or preferences of the depositor.
-The vaults are held in a central vault registry, ensuring that all interactions with rugged tokens are tracked and managed within the system.
+where $\tau$ determines whether the receipt is a fungible token, an NFT, or an RFT.
+This provides flexibility depending on the underlying asset type.
+The vaults are held in a central vault registry per blockchain ecosystem, and ultimately represented on the Rugsafe blockchain, ensuring that all interactions with rugged tokens are tracked and managed within the multichain ecosystem.
 Regardless of the type of receipt issued, depositors always receive the 1:1 $C_a$ tokens as a clean representation of their original rugged tokens.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ANTICOIN ROLE
 
-\subsection{Withdrawal Penalty Mechanism}
-If a user decides to withdraw their original rugged tokens $C_r$ by depositing back their $C_a$, a penalty is incurred.
-A portion of the $C_a$ tokens are deducted from the user's balance, and these penalized tokens are distributed among the remaining $C_a$ holders.
+\subsection{Anticoin Role and Market Interaction}
 
-\begin{equation}
-C_{r,w} = C_{r,d} - P(C_a)
-\end{equation}
+At the time of vault creation, the protocol mints $C_a$ tokens in a 1:1 ratio with the deposited rugged tokens $C_r$.
+These $C_a$ tokens serve not only as receipts for the deposited tokens but also as inversely, logarithmically pegged assets.
+This inverse logarithmic peg allows users to benefit from a decline in the value of $C_r$, effectively creating a hedge against further depreciation of rugged tokens.
 
-Where $P(C_a)$ represents the penalty, which scales according to the amount of $C_r$ originally deposited, \(d\).
-The penalty mechanism incentivizes holding $C_a$ longer, as the remaining holders benefit from these penalties.
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{images/anticoins.png}
+\caption{The plotted relationship between the price of a rugged token ($C_r$) and the price of its anticoin ($C_a$) under an inverse logarithmic model.
+In the left plot, as $C_r$ increases linearly, the price of $C_a$ decreases logarithmically, demonstrating a diminishing response in $C_a$ as $C_r$ grows.
+In the right plot, as $C_r$ decreases, the price of $C_a$ rises logarithmically, tapering off as $C_r$ approaches zero.
+This inverse peg mechanism ensures that $C_a$ responds proportionally to changes in $C_r$, maintaining stability and mitigating volatility.}
+\label{fig:anticoins_plot}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Unlike traditional stablecoins, the value of $C_a$ tokens increases as the value of $C_r$ decreases, following an inverse, logarithmic price relationship.
+This dynamic creates a unique market interaction where $C_a$ holders are incentivized to retain their tokens when the value of $C_r$ declines.
+
+The inverse logarithmic peg mechanism, as depicted in Figure \ref{fig:anticoins_plot}, ensures that $C_a$ tokens adjust logarithmically based on the real-time market movements of the underlying $C_r$.
+Unlike bounded inverse assets, the $C_a$ tokens are not constrained by any upper or lower price limits, allowing for unrestricted value increases as $C_r$ approaches zero.
+
+This design ensures that $C_a$ tokens serve dual purposes within the protocol.
+They serve as a receipt for deposited rugged tokens and as an inversely, logarithmically pegged asset that can be freely traded or held.
+The valuation of $C_a$ is driven by market forces, allowing the broader ecosystem to determine its worth relative to other assets based on supply, demand, and the inverse relationship with the rugged token $C_r$.
+
+%%%%%%%%%% bounding
+\subsubsection{Inverse Logarithmic Pegging as Soft Theoretical Bounds}
+
+Linear inverse pegs in previous systems required artificial bounds on asset prices.
+Once these bounds were reached, the asset froze, and a new version was created.
+These restrictions were designed to prevent extreme price volatility but imposed artificial constraints that limited flexibility and created friction through asset freezes, and resets.
+
+In contrast, the inverse logarithmic peg for $C_a$ naturally establishes soft theoretical bounds without requiring such freezes.
+As the price of $C_r$ moves to either extreme, the logarithmic peg ensures the price of $C_a$ tapers off, maintaining stability.
+This tapering effect acts as a soft boundary, ensuring proportional price responses without hard limits or resets.
+
+\[
+C_{a}(t) = \log\left(\frac{C_{r}(0)}{C_{r}(t)}\right)
+\]
+
+Where \( C_{a}(t) \) is the value of the anticoin at time \( t \), \( C_{r}(0) \) is the rugged token's price at vault creation, and \( C_{r}(t) \) is its real-time price.
+This relationship ensures that all $C_a$ holders share a uniform reference point.
+
+This approach provides more organic price regulation, allowing the market to drive $C_a$’s value while avoiding the volatility issues seen in bounded systems.
+The logarithmic peg offers a flexible, stable framework that adapts naturally to market conditions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% SUPPLY
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Anticoin Role and Market Interaction}
-At the time of vault creation, the protocol mints $C_a$ tokens in a 1:1 ratio with the deposited rugged tokens $C_r$.
-These $C_a$ tokens serve as a clean, fungible representation of the rugged tokens, providing users with a new asset that can be freely traded or held.
-The value of $C_a$ tokens is determined entirely by market forces, \(m_f\), allowing the broader ecosystem to establish their worth relative to other assets.
-
-The $C_a$ tokens function purely as receipts for the deposited rugged tokens and do not undergo any price adjustments or pegging mechanisms.
-This approach ensures that the protocol remains simple and transparent, with the market dictating the value of $C_a$ based on supply and demand dynamics.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%
 
@@
 
-\subsubsection{equitable system design}
+\subsubsection{Equitable system design}
 
@@
 
-\subsubsection{cumulative penalty mechanism}
+\subsubsection{Cumulative penalty mechanism}
 
@@
 \end{document}
+
+% things to add
+% perpetuals market
+% asymmetric funding rates
+% anticoins inverse price with dex
+% defi suite
+% prediction market
+% borroing and lending

### 2024-10-03 rugsafe-perps/src/instructions/perpetuals/processor.rs

@@ -66,50 +66,50 @@ impl Processor {
         let program_account = next_account_info(account_info_iter)?; // Program's AccountInfo
         let position_account = next_account_info(account_info_iter)?; // **Position account (PDA) should be last**
 
-        msg!("OpenPosition Account: Program ID: {:?}", program_id);
-        msg!(
-            "OpenPosition Account: User Positions: {:?}",
-            user_positions_account.key
-        );
-        msg!(
-            "OpenPosition Account: User Collateral: {:?}",
-            user_collateral_account.key
-        );
-        msg!(
-            "OpenPosition Account: Collateral Mint: {:?}",
-            collateral_mint_account.key
-        );
-        msg!(
-            "OpenPosition Account: Custody ATA: {:?}",
-            custody_account.key
-        );
-        msg!(
-            "OpenPosition Account: Passed Custody Account: {:?}",
-            custody_account.key
-        );
-        msg!(
-            "OpenPosition Account: Collateral Mint Account: {:?}",
-            collateral_mint_account.key
-        );
-        msg!("OpenPosition Account: SPL Token: {:?}", spl_account.key);
-        msg!(
-            "OpenPosition Account: System Program: {:?}",
-            system_program.key
-        );
-        msg!("OpenPosition Account: Rent: {:?}", rent_account.key);
-        msg!(
-            "OpenPosition Account: Associated Token Program: {:?}",
-            associated_token_program.key
-        );
-        msg!(
-            "OpenPosition Account: Program Accout: {:?}",
-            program_account.key
-        );
+        // msg!("OpenPosition Account: Program ID: {:?}", program_id);
+        // msg!(
+        //     "OpenPosition Account: User Positions: {:?}",
+        //     user_positions_account.key
+        // );
+        // msg!(
+        //     "OpenPosition Account: User Collateral: {:?}",
+        //     user_collateral_account.key
+        // );
+        // msg!(
+        //     "OpenPosition Account: Collateral Mint: {:?}",
+        //     collateral_mint_account.key
+        // );
+        // msg!(
+        //     "OpenPosition Account: Custody ATA: {:?}",
+        //     custody_account.key
+        // );
+        // msg!(
+        //     "OpenPosition Account: Passed Custody Account: {:?}",
+        //     custody_account.key
+        // );
+        // msg!(
+        //     "OpenPosition Account: Collateral Mint Account: {:?}",
+        //     collateral_mint_account.key
+        // );
+        // msg!("OpenPosition Account: SPL Token: {:?}", spl_account.key);
[…]

### 2024-10-03 rugsafe_original_old_merged/rugsafe/paper/images/py10.py

@@ -1,0 +1,36 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Price range for the rugged token
+rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
+rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
+
+# Shifted log to match initial point with the rugged token price
+anticoin_price_up = np.log(10 / rugged_token_price_up) + (rugged_token_price_up[0] - np.log(10 / rugged_token_price_up[0]))
+anticoin_price_down = np.log(10 / rugged_token_price_down) + (rugged_token_price_down[0] - np.log(10 / rugged_token_price_down[0]))
+
+# Create a figure with two subplots side by side
+fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6))
+
+# First subplot: Cr price going up and Ca price going down
+ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
+ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
+ax1.set_title("$C_r$ Up, $C_a$ Log Down")
+ax1.set_xlabel("Price of Rugged Token ($C_r$)")
+ax1.set_ylabel("Price")
+ax1.grid(True)
+ax1.legend()
+
+# Second subplot: Cr price going down and Ca price going up
+ax2.plot(rugged_token_price_down, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")
+ax2.plot(rugged_token_price_down, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
+ax2.set_title("$C_r$ Down, $C_a$ Log Up")
+ax2.set_xlabel("Price of Rugged Token ($C_r$)")
+ax2.set_ylabel("Price")
+ax2.grid(True)
+ax2.legend()
+
+# Display the plots
+plt.tight_layout()
+plt.show()
+

### 2024-10-03 rugsafe_original_old_merged/rugsafe/paper/images/py11.py

@@ -1,0 +1,40 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Price range for the rugged token
+rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
+rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
+
+# Anticoin price calculated as a logarithmic inverse of rugged token price
+anticoin_price_up = np.log(10 / rugged_token_price_up)
+anticoin_price_down = np.log(10 / rugged_token_price_down)
+
+# Adjust anticoin prices to match the initial value with rugged token price
+anticoin_price_up = anticoin_price_up + (rugged_token_price_up[0] - anticoin_price_up[0])
+anticoin_price_down = anticoin_price_down + (rugged_token_price_down[0] - anticoin_price_down[0])
+
+# Create a figure with two subplots side by side
+fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6))
+
+# First subplot: Cr price going up and Ca price going down
+ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
+ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
+ax1.set_title("$C_r$ Up, $C_a$ Log Down")
+ax1.set_xlabel("Price of Rugged Token ($C_r$)")
+ax1.set_ylabel("Price")
+ax1.grid(True)
+ax1.legend()
+
+# Second subplot: Cr price going down (REVERSED X-AXIS) and Ca price going up
+ax2.plot(rugged_token_price_up, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")  # Reversing the rugged token price curve
+ax2.plot(rugged_token_price_up, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
+ax2.set_title("$C_r$ Down, $C_a$ Log Up")
+ax2.set_xlabel("Price of Rugged Token ($C_r$)")
+ax2.set_ylabel("Price")
+ax2.grid(True)
+ax2.legend()
+
+# Display the plots
+plt.tight_layout()
+plt.show()
+

### 2024-10-03 rugsafe_original_old_merged/rugsafe/paper/images/py12.py

@@ -1,0 +1,46 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Price range for the rugged token
+rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
+rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
+
+# Anticoin price calculated as a logarithmic inverse of rugged token price
+anticoin_price_up = np.log(10 / rugged_token_price_up)
+anticoin_price_down = np.log(rugged_token_price_up)  # Adjusted to taper off as Cr decreases
+
+# Adjust anticoin prices to match the initial value with rugged token price
+anticoin_price_up = anticoin_price_up + (rugged_token_price_up[0] - anticoin_price_up[0])
+anticoin_price_down = anticoin_price_down + (rugged_token_price_down[0] - anticoin_price_down[0])
+
+# Create a figure with two subplots side by side, set background to black and labels to white
+fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6), facecolor='black')
+
+# First subplot: Cr price going up and Ca price going down
+ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
+ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
+ax1.set_title("$C_r$ Up, $C_a$ Log Down", color='white')
+ax1.set_xlabel("Price of Rugged Token ($C_r$)", color='white')
+ax1.set_ylabel("Price", color='white')
+ax1.legend(facecolor='black', edgecolor='white', labelcolor='white')
+ax1.set_facecolor('black')
+ax1.tick_params(axis='x', colors='white')
+ax1.tick_params(axis='y', colors='white')
+ax1.grid(True, color='gray', linestyle='--', linewidth=0.5)  # Less prominent grid lines
+
+# Second subplot: Cr price going down and Ca price going up (now tapering off correctly)
+ax2.plot(rugged_token_price_up, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")
+ax2.plot(rugged_token_price_up, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
+ax2.set_title("$C_r$ Down, $C_a$ Log Up", color='white')
+ax2.set_xlabel("Price of Rugged Token ($C_r$)", color='white')
[…]

### 2024-10-03 rugsafe_original_old_merged/rugsafe/paper/images/py9.py

@@ -1,0 +1,36 @@
+import matplotlib.pyplot as plt
+import numpy as np
+
+# Price range for the rugged token
+rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
+rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
+
+# Anticoin price calculated as a logarithmic inverse of rugged token price
+anticoin_price_up = np.log(10 / rugged_token_price_up)
+anticoin_price_down = np.log(10 / rugged_token_price_down)
+
+# Create a figure with two subplots side by side
+fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6))
+
+# First subplot: Cr price going up and Ca price going down
+ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
+ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
+ax1.set_title("$C_r$ Up, $C_a$ Log Down")
+ax1.set_xlabel("Price of Rugged Token ($C_r$)")
+ax1.set_ylabel("Price")
+ax1.grid(True)
+ax1.legend()
+
+# Second subplot: Cr price going down (REVERSED X-AXIS) and Ca price going up
+ax2.plot(rugged_token_price_up, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")  # Reversing the rugged token price curve
+ax2.plot(rugged_token_price_up, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
+ax2.set_title("$C_r$ Down, $C_a$ Log Up")
+ax2.set_xlabel("Price of Rugged Token ($C_r$)")
+ax2.set_ylabel("Price")
+ax2.grid(True)
+ax2.legend()
+
+# Display the plots
+plt.tight_layout()
+plt.show()
+

### 2024-10-04 rugsafe_original_old_merged/rugsafe/paper/images/py10.py
chore: removed legacy project

@@ -1,36 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Price range for the rugged token
-rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
-rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
-
-# Shifted log to match initial point with the rugged token price
-anticoin_price_up = np.log(10 / rugged_token_price_up) + (rugged_token_price_up[0] - np.log(10 / rugged_token_price_up[0]))
-anticoin_price_down = np.log(10 / rugged_token_price_down) + (rugged_token_price_down[0] - np.log(10 / rugged_token_price_down[0]))
-
-# Create a figure with two subplots side by side
-fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6))
-
-# First subplot: Cr price going up and Ca price going down
-ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
-ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
-ax1.set_title("$C_r$ Up, $C_a$ Log Down")
-ax1.set_xlabel("Price of Rugged Token ($C_r$)")
-ax1.set_ylabel("Price")
-ax1.grid(True)
-ax1.legend()
-
-# Second subplot: Cr price going down and Ca price going up
-ax2.plot(rugged_token_price_down, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")
-ax2.plot(rugged_token_price_down, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
-ax2.set_title("$C_r$ Down, $C_a$ Log Up")
-ax2.set_xlabel("Price of Rugged Token ($C_r$)")
-ax2.set_ylabel("Price")
-ax2.grid(True)
-ax2.legend()
-
-# Display the plots
-plt.tight_layout()
-plt.show()
-

### 2024-10-04 rugsafe_original_old_merged/rugsafe/paper/images/py11.py

@@ -1,40 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Price range for the rugged token
-rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
-rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
-
-# Anticoin price calculated as a logarithmic inverse of rugged token price
-anticoin_price_up = np.log(10 / rugged_token_price_up)
-anticoin_price_down = np.log(10 / rugged_token_price_down)
-
-# Adjust anticoin prices to match the initial value with rugged token price
-anticoin_price_up = anticoin_price_up + (rugged_token_price_up[0] - anticoin_price_up[0])
-anticoin_price_down = anticoin_price_down + (rugged_token_price_down[0] - anticoin_price_down[0])
-
-# Create a figure with two subplots side by side
-fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6))
-
-# First subplot: Cr price going up and Ca price going down
-ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
-ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
-ax1.set_title("$C_r$ Up, $C_a$ Log Down")
-ax1.set_xlabel("Price of Rugged Token ($C_r$)")
-ax1.set_ylabel("Price")
-ax1.grid(True)
-ax1.legend()
-
-# Second subplot: Cr price going down (REVERSED X-AXIS) and Ca price going up
-ax2.plot(rugged_token_price_up, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")  # Reversing the rugged token price curve
-ax2.plot(rugged_token_price_up, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
-ax2.set_title("$C_r$ Down, $C_a$ Log Up")
-ax2.set_xlabel("Price of Rugged Token ($C_r$)")
-ax2.set_ylabel("Price")
-ax2.grid(True)
-ax2.legend()
-
-# Display the plots
-plt.tight_layout()
-plt.show()
-

### 2024-10-04 rugsafe_original_old_merged/rugsafe/paper/images/py12.py

@@ -1,46 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Price range for the rugged token
-rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
-rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
-
-# Anticoin price calculated as a logarithmic inverse of rugged token price
-anticoin_price_up = np.log(10 / rugged_token_price_up)
-anticoin_price_down = np.log(rugged_token_price_up)  # Adjusted to taper off as Cr decreases
-
-# Adjust anticoin prices to match the initial value with rugged token price
-anticoin_price_up = anticoin_price_up + (rugged_token_price_up[0] - anticoin_price_up[0])
-anticoin_price_down = anticoin_price_down + (rugged_token_price_down[0] - anticoin_price_down[0])
-
-# Create a figure with two subplots side by side, set background to black and labels to white
-fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6), facecolor='black')
-
-# First subplot: Cr price going up and Ca price going down
-ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
-ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
-ax1.set_title("$C_r$ Up, $C_a$ Log Down", color='white')
-ax1.set_xlabel("Price of Rugged Token ($C_r$)", color='white')
-ax1.set_ylabel("Price", color='white')
-ax1.legend(facecolor='black', edgecolor='white', labelcolor='white')
-ax1.set_facecolor('black')
-ax1.tick_params(axis='x', colors='white')
-ax1.tick_params(axis='y', colors='white')
-ax1.grid(True, color='gray', linestyle='--', linewidth=0.5)  # Less prominent grid lines
-
-# Second subplot: Cr price going down and Ca price going up (now tapering off correctly)
-ax2.plot(rugged_token_price_up, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")
-ax2.plot(rugged_token_price_up, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
-ax2.set_title("$C_r$ Down, $C_a$ Log Up", color='white')
-ax2.set_xlabel("Price of Rugged Token ($C_r$)", color='white')
[…]

### 2024-10-04 rugsafe_original_old_merged/rugsafe/paper/images/py9.py

@@ -1,36 +1,0 @@
-import matplotlib.pyplot as plt
-import numpy as np
-
-# Price range for the rugged token
-rugged_token_price_up = np.linspace(0.1, 10, 100)    # Price going up
-rugged_token_price_down = np.linspace(10, 0.1, 100)  # Price going down
-
-# Anticoin price calculated as a logarithmic inverse of rugged token price
-anticoin_price_up = np.log(10 / rugged_token_price_up)
-anticoin_price_down = np.log(10 / rugged_token_price_down)
-
-# Create a figure with two subplots side by side
-fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(12, 6))
-
-# First subplot: Cr price going up and Ca price going down
-ax1.plot(rugged_token_price_up, rugged_token_price_up, color='purple', label="Rugged Token Price ($C_r$)")
-ax1.plot(rugged_token_price_up, anticoin_price_up, color='blue', label="Anticoin Price ($C_a$)")
-ax1.set_title("$C_r$ Up, $C_a$ Log Down")
-ax1.set_xlabel("Price of Rugged Token ($C_r$)")
-ax1.set_ylabel("Price")
-ax1.grid(True)
-ax1.legend()
-
-# Second subplot: Cr price going down (REVERSED X-AXIS) and Ca price going up
-ax2.plot(rugged_token_price_up, rugged_token_price_down, color='purple', label="Rugged Token Price ($C_r$)")  # Reversing the rugged token price curve
-ax2.plot(rugged_token_price_up, anticoin_price_down, color='blue', label="Anticoin Price ($C_a$)")
-ax2.set_title("$C_r$ Down, $C_a$ Log Up")
-ax2.set_xlabel("Price of Rugged Token ($C_r$)")
-ax2.set_ylabel("Price")
-ax2.grid(True)
-ax2.legend()
-
-# Display the plots
-plt.tight_layout()
-plt.show()
-

### 2024-10-04 rugsafe_original_old_merged/src/instructions/perpetuals/processor.rs

@@ -1,332 +1,0 @@
-use crate::instructions::perpetuals::PerpetualsInstruction;
-use crate::state::perpetuals::{Position, Side, UserPositions};
-use borsh::{BorshDeserialize, BorshSerialize};
-use solana_program::{
-    account_info::{next_account_info, AccountInfo},
-    clock::Clock,
-    entrypoint::ProgramResult,
-    msg,
-    program::invoke,
-    program::invoke_signed,
-    program_error::ProgramError,
-    pubkey::Pubkey,
-    rent::Rent,
-    sysvar::Sysvar,
-};
-use spl_associated_token_account::get_associated_token_address;
-
-pub struct Processor;
-
-impl Processor {
-    pub fn process(
-        program_id: &Pubkey,
-        accounts: &[AccountInfo],
-        instruction_data: &[u8],
-    ) -> ProgramResult {
-        let instruction = PerpetualsInstruction::unpack(instruction_data)?;
-
-        match instruction {
-            PerpetualsInstruction::OpenPosition { side, amount } => {
-                Self::process_open_position(program_id, accounts, side, amount)
-            }
-            PerpetualsInstruction::ClosePosition { position_id } => {
-                Self::process_close_position(program_id, accounts, position_id)
-            }
-            PerpetualsInstruction::AddCollateral {
-                position_id,
-                amount,
-            } => Self::process_add_collateral(program_id, accounts, position_id, amount),
-            PerpetualsInstruction::RemoveCollateral {
-                position_id,
-                amount,
-            } => Self::process_remove_collateral(program_id, accounts, position_id, amount),
-            PerpetualsInstruction::LiquidatePosition { position_id } => {
-                Self::process_liquidate_position(program_id, accounts, position_id)
-            }
-        }
-    }
-
-    fn process_open_position(
-        program_id: &Pubkey,
-        accounts: &[AccountInfo],
-        side: Side,
-        amount: u64,
-    ) -> ProgramResult {
-        let account_info_iter = &mut accounts.iter();
-
-        let payer_account = next_account_info(account_info_iter)?; // User who opens the position
-        let user_positions_account = next_account_info(account_info_iter)?; // User's positions account (PDA)
-        let user_collateral_account = next_account_info(account_info_iter)?; // User's collateral token account
-        let collateral_mint_account = next_account_info(account_info_iter)?; // Collateral mint account
-        let custody_account = next_account_info(account_info_iter)?; // Custody account (associated token account)
[…]

### 2024-10-04 rugsafe_original_old_merged/src/instructions/processor.rs

@@ -1,35 +1,0 @@
-use solana_program::{account_info::AccountInfo, entrypoint::ProgramResult, pubkey::Pubkey};
-
-pub struct Processor;
-
-impl Processor {
-    pub fn process(
-        program_id: &Pubkey,
-        accounts: &[AccountInfo],
-        instruction_data: &[u8],
-    ) -> ProgramResult {
-        // Determine which module the instruction belongs to
-        // Use the first byte to indicate the module
-        let (module_tag, rest) = instruction_data
-            .split_first()
-            .ok_or(solana_program::program_error::ProgramError::InvalidInstructionData)?;
-
-        match module_tag {
-            0 => {
-                // Vaults module
-                // crate::instructions::vaults::Processor::process(program_id, accounts, rest)
-                crate::instructions::vaults::processor::Processor::process(
-                    program_id, accounts, rest,
-                )
-            }
-            1 => {
-                // Perpetuals module
-                // crate::instructions::perpetuals::Processor::process(program_id, accounts, rest)
-                crate::instructions::perpetuals::processor::Processor::process(
-                    program_id, accounts, rest,
-                )
-            }
-            _ => Err(solana_program::program_error::ProgramError::InvalidInstructionData),
-        }
-    }
-}

### 2024-10-04 rugsafe_original_old_merged/src/instructions/vaults/mod.rs

@@ -1,7 +1,0 @@
-pub mod instruction;
-pub mod processor;
-// pub mod vaults;
-
-pub use {instruction::*, processor::*};
-
-// pub use {instruction::*, vaults::*};

### 2024-10-04 rugsafe_original_old_merged/src/instructions/vaults/processor.rs

@@ -1,880 +1,0 @@
-// use crate::instructions::VaultInstruction;
-use crate::instructions::vaults::VaultInstruction;
-use solana_program::sysvar::Sysvar;
-use solana_program::{
-    account_info::{next_account_info, AccountInfo},
-    entrypoint::ProgramResult,
-    msg,
-    program::invoke,
-    program::invoke_signed,
-    program_error::ProgramError,
-    program_pack::Pack,
-    pubkey::Pubkey,
-    sysvar,
-    sysvar::rent::Rent,
-};
-use spl_associated_token_account::get_associated_token_address;
-// use spl_associated_token_account::instruction::create_associated_token_account;
-use spl_associated_token_account::{self, instruction};
-
-// use solana_sdk::program::invoke_signed;
-
-use spl_token::instruction::{burn, initialize_mint, initialize_mint2, mint_to};
-use spl_token::state::Account as TokenAccount;
-use spl_token::state::Mint;
-
-// storage
-use crate::state::vaults::{Vault, VaultRegistry};
-use borsh::{BorshDeserialize, BorshSerialize};
-use std::io::Cursor;
-
-pub struct Processor;
-
-impl Processor {
-    /*
-    @name process
-    @description Entry point for processing all instructions related to the vault. It dispatches the instruction to the appropriate handler.
-    @param program_id - The ID of the currently executing program.
-    @param accounts - The accounts involved in the transaction.
-    @param instruction_data - The instruction data to be processed.
-    */
-    pub fn process(
-        program_id: &Pubkey,
-        accounts: &[AccountInfo],
-        instruction_data: &[u8],
-    ) -> ProgramResult {
-        let instruction = VaultInstruction::unpack(instruction_data)?;
-
-        match instruction {
-            VaultInstruction::CreateVault => Self::process_create_vault(program_id, accounts),
-            VaultInstruction::Deposit { amount } => {
-                Self::process_deposit(program_id, accounts, amount)
-            }
-            VaultInstruction::Withdraw { amount } => {
-                Self::process_withdraw(program_id, accounts, amount)
-            }
-            VaultInstruction::BurnRToken { amount } => {
-                Self::process_burn_rtoken(program_id, accounts, amount)
-            }
-            VaultInstruction::Faucet { amount } => {
-                Self::process_faucet(program_id, accounts, amount)
-            }
-        }
-    }
-    /*
-    @name process_create_vault
[…]

### 2024-10-04 rugsafe_original_old_merged/src/state/perpetuals.rs

@@ -1,66 +1,0 @@
-use borsh::{BorshDeserialize, BorshSerialize};
-use solana_program::pubkey::Pubkey;
-
-pub const MAX_POSITIONS: usize = 10; // Max number of positions per user
-
-#[derive(Copy, Clone, PartialEq, Debug, BorshSerialize, BorshDeserialize)]
-pub enum Side {
-    None,
-    Long,
-    Short,
-}
-
-impl Default for Side {
-    fn default() -> Self {
-        Self::None
-    }
-}
-
-#[derive(Debug, Clone, BorshSerialize, BorshDeserialize, Default)]
-pub struct Position {
-    pub owner: Pubkey, // The public key of the user who owns this position. It uniquely identifies the user.
-
-    pub pool: Pubkey, // Represents the liquidity pool in which this position operates. It's used to link the position to a specific market or trading pool.
-
-    pub custody: Pubkey, // The public key of the custody account holding the assets for this position. Custody ensures that assets are stored securely.
-
-    pub collateral_custody: Pubkey, // The public key of the collateral custody account. This holds the collateral deposited to secure the position, protecting against liquidation.
-
-    pub open_time: i64, // Timestamp indicating when the position was first opened. It records the exact moment the position was initiated.
-
-    pub update_time: i64, // Timestamp of the most recent update to the position. It changes whenever new collateral is added, or a partial close happens.
-
-    pub side: Side, // Indicates whether the position is long (betting on price going up) or short (betting on price going down).
-
-    pub price: u64, // The price at which the position was opened. This is the reference price used to calculate profit and loss.
-
-    pub size_usd: u64, // The total size of the position in USD. Represents the notional value of the position.
-
-    pub borrow_size_usd: u64, // The amount borrowed in USD to leverage the position. Borrowing increases potential returns but also risk.
-
-    pub collateral_usd: u64, // The USD value of the collateral held for this position. This collateral is used to maintain the position and mitigate liquidation risk.
-
-    pub unrealized_profit_usd: u64, // The potential profit on the position if it were to be closed at the current market price. It is 'unrealized' because the position is still open.
-
-    pub unrealized_loss_usd: u64, // The potential loss on the position if it were to be closed at the current market price. This is the risk side, also 'unrealized' because the position is still open.
-
[…]

### 2024-10-04 rugsafe_original_old_merged/tests/main.rs

@@ -1,7 +1,0 @@
-pub mod test_suite;
-
-#[tokio::test]
-pub async fn test_integration() {
-    // tests_suite::vaults().await;
-    // TODO: can run test integration in here
-}

### 2024-10-04 rugsafe_original_old_merged/tests/test_suite/perpetuals/mod.rs

@@ -1,3 +1,0 @@
-pub mod test_perpetuals;
-
-pub use test_perpetuals::*;
